---
title: "honours"
output: html_document
date: "2025-05-07"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r eval=FALSE}
pak::pak("christelinda-laureijs/patchclampplotteR")

# work around for when ^ wasn't working
install.packages("remotes")  
remotes::install_github("christelinda-laureijs/patchclampplotteR")
```
## Libraries
libraries I might need
```{r}
library(patchclampplotteR)
library(dplyr)
library(ggplot2)
library(ggsignif)
library(ggtext)
library(ggforce)
library(ggpubr)
library(here)
library(car)
library(ez)
library(lme4)
library(lmerTest)
library(tidyr)
```

## Importing Data
Importing Cell Characteristics
```{r}
cell_characteristics <- import_cell_characteristics_df("Data/Cell-Characteristics.csv")

cell_characteristics
```

Importing Sheet with Raw Evoked Current Data
```{r}
eEPSC_data <- read.csv("Data/new_raw_eEPSC.csv")

eEPSC_data
```

### Raw eEPSC
To Append New Data onto the EXISTING SHEET (raw_eEPSC_df.csv) after first time
```{r eval=FALSE}
# will not run if there is nothing new in "new_raw_eEPSC.csv" so if you put new data directly into "raw_eEPSC_df.csv", it won't run
add_new_cells(
  new_raw_data_csv = "Data/new_raw_eEPSC.csv", # should ONLY have the new data you want
  cell_characteristics_csv = "Data/Cell-Characteristics.csv",
  old_raw_data_csv = "Data/raw_eEPSC_df.csv",
  data_type = "eEPSC",
  write_new_csv = "yes",
  new_file_name = "Data/raw_eEPSC_df.csv", # will overwrite the current version of this file
  decimal_places = 2
)

# once successful, go delete the data from "new_raw_eEPSC.csv" so that you don't get a duplication error the next time you are adding data to the raw_eEPSC_df.
```

Look at the data frame
```{r}
raw_eEPSC_df <- read.csv(here("Data/raw_eEPSC_df.csv")) # puts it in the environment
```

### AP Count
Importing NEW Action Potential Count Data
```{r eval=FALSE}
add_new_cells(
  new_raw_data_csv = "Data/new_AP_count.csv", # should ONLY have the new data you want
  cell_characteristics_csv = "Data/Cell-Characteristics.csv",
  old_raw_data_csv = "Data/AP_count_data.csv", # current data
  data_type = "AP_count",
  write_new_csv = "yes",
  new_file_name = "Data/AP_count_data.csv", # will add to this and overwrite the current version of this file
  decimal_places = 2,
  injection_start_time = 265.4,
  length_of_current_injection = 0.5
)
```
```{r}
AP_count_data <- read.csv(here("Data/AP_count_data.csv"))
```

### AP Parameters
Importing NEW Action Potential Parameter Data
```{r eval=FALSE}
add_new_cells(
  new_raw_data_csv = "Data/new_AP_parameters.csv", # should ONLY have the new data you want,
  cell_characteristics_csv = "Data/Cell-Characteristics.csv",
  old_raw_data_csv = "Data/AP_parameters.csv", # current data
  data_type = "AP_parameter",
  write_new_csv = "yes",
  new_file_name = "Data/AP_parameters.csv", # will add to this and overwrite the current version of this file (same as current data)
  decimal_places = 2,
  injection_start_time = 265.4,
  length_of_current_injection = 0.5
)
```
```{r}
AP_data <- read.csv(here("Data/AP_parameters.csv"))
```

```{r}
# adding group column
AP_data <- AP_data %>%
  mutate(group = case_when(
    category == 1 & treatment == "Control" ~ "naive",
    category == 2 & treatment == "Control" ~ "acute",
    category == 2 & treatment == "AM251" ~ "AM251",
    category == 3 & treatment == "Control" ~ "repeated",
    category == 1 & treatment == "Cort" ~ "cort",
  )) %>%
  mutate(group = factor(group, levels = c("naive", "acute", "AM251", "repeated", "cort")))
```


## Theme and Colour Options
defining my colour theme
```{r}
my_theme_colours <- data.frame(
  category = c(1, 2, 3, 2, 1),
    treatment = c("Control", "Control", "Control", "AM251", "Cort"),
  display_names = c("Naive", "Acute", "Repeated", "Acute with AM251", "Naive with Corticosterone"),
  colours = c("#ecc479", "#eb647e", "#005b96", "#C11C84", "#6aa84f"),
  very_pale_colours = c("#f5e0b3", "#f19cac", "#6497b1", "#FFADFF","#93c47d")
)
```

editing my theme options
```{r}
library(tibble)

my_theme_options <- read.csv("Data/my_custom_theme_options.csv") %>%
  remove_rownames() %>%
  column_to_rownames(var = "option")
```

## How many cells, and how long are they?
```{r}
# acute
raw_eEPSC_df %>%
  filter(category == 2) %>%
  filter(time == 0) %>%
  group_by(treatment) %>%
  count(sex) %>%
  arrange(treatment, sex)
```
```{r}
# naive
raw_eEPSC_df %>%
  filter(category == 1) %>%
  filter(time == 0) %>%
  group_by(treatment) %>%
  count(sex) %>%
  arrange(treatment, sex)
```
```{r}
# repeated
raw_eEPSC_df %>%
  filter(category == 3) %>%
  filter(time == 0) %>%
  group_by(treatment) %>%
  count(sex) %>%
  arrange(treatment, sex)
```

Length of Cells
```{r}
raw_eEPSC_df %>%
  group_by(letter) %>%
  summarize(max_time = max(time))
```

## Raw Plots per Cell
Normalizing Data:
```{r}
normalized_raw_eEPSC_df <- make_normalized_EPSC_data(
  filename = "Data/raw_eEPSC_df.csv",
  current_type = "eEPSC",
  min_time_value = 0,
  max_time_value = 30,
  interval_length = 5,
  baseline_length = 5,
  negative_transform_currents = "yes" # because the raw amplitudes are negative
)
```

Raw ACUTE Plots for each cell:
```{r eval=FALSE}
raw_eEPSC_acute_plots <- plot_raw_current_data(
 data = normalized_raw_eEPSC_df, # why are RMA3 and RMA4 not showing up (May 2025)
 # no longer filtering bad cells RMA5 and RMA7 (2025/6/16)
  plot_treatment = "Control", # RMA3 and RMA4 were not showing up because they had "control" instead of "Control" and "female" instead of "Female" (May 2025)
  plot_category = 2, # 2 is acute restraint, 1 is naive
  current_type = "eEPSC",
  y_variable = "P1",
  pruned = "no",
  hormone_added = "HFS",
  hormone_or_HFS_start_time = 5,
  theme_options = my_theme_options,
  treatment_colour_theme = my_theme_colours
)

 raw_eEPSC_acute_plots
 
# ggsave(raw_eEPSC_acute_plots$RMA1, path = here("Figures"), file = "raw_eEPSC_acute_plots_RMA1.png", width = 7, height = 5, units = "in", dpi = 300)

# remove the title and subtitle 
RMA1_plot <- raw_eEPSC_acute_plots$RMA1 + theme(plot.subtitle = element_blank(), plot.title = element_blank())

RMA1_plot

# saving as png to figure folder
# ggsave(RMA1_plot, path = here("Figures"), file = "RMA1_plot.png", width = 7, height = 5, units = "in", dpi = 300)
```
Raw ACUTE Plots for each cell with AM251:
```{r eval=FALSE}
raw_eEPSC_acute_plots_AM251 <- plot_raw_current_data(
 data = normalized_raw_eEPSC_df,
  plot_treatment = "AM251",
  plot_category = 2, # 2 is acute restraint, 1 is naive
  current_type = "eEPSC",
  y_variable = "P1",
  pruned = "no",
  hormone_added = "HFS",
  hormone_or_HFS_start_time = 5,
  theme_options = my_theme_options,
  treatment_colour_theme = my_theme_colours
)

 raw_eEPSC_acute_plots_AM251

# remove the title and subtitle 
RMA2A_plot <- raw_eEPSC_acute_plots_AM251$RMA2A + theme(plot.subtitle = element_blank(), plot.title = element_blank())

RMA2A_plot

# saving as png to figure folder
# ggsave(RMA2A_plot, path = here("Figures"), file = "RMA2A_plot.png", width = 7, height = 5, units = "in", dpi = 300)
```

Raw Naive Plots for each cell:
```{r eval=FALSE}
raw_eEPSC_naive_plots <- plot_raw_current_data(
 data = normalized_raw_eEPSC_df,
  plot_treatment = "Control",
  plot_category = 1,
  current_type = "eEPSC",
  y_variable = "P1",
  pruned = "no",
  hormone_added = "HFS",
  hormone_or_HFS_start_time = 5,
  theme_options = my_theme_options,
  treatment_colour_theme = my_theme_colours
)

 raw_eEPSC_naive_plots

# remove the title ("Recording LS10") and subtitle ("Treatment: Control Sex: Female")
LS2_plot <- raw_eEPSC_naive_plots$LS2 + theme(plot.subtitle = element_blank(), plot.title = element_blank())

LS2_plot

#fixing the y-axis
# LS10_final_plot <- LS10_plot + ylim(0,550)

# LS10_final_plot

# saving as png to figure folder
# ggsave(LS2_plot, path = here("Figures"), file = "LS2_plot.png", width = 7, height = 5, units = "in", dpi = 300)
```

Raw REPEATED Plots for each cell:
```{r}
raw_eEPSC_repeated_plots <- plot_raw_current_data(
 data = normalized_raw_eEPSC_df, # why are RMA3 and RMA4 not showing up (May 2025)
 # no longer filtering bad cells RMA5 and RMA7 (2025/6/16)
  plot_treatment = "Control", # RMA3 and RMA4 were not showing up because they had "control" instead of "Control" and "female" instead of "Female" (May 2025)
  plot_category = 3, # 3 is repeated, 2 is acute restraint, 1 is naive
  current_type = "eEPSC",
  y_variable = "P1",
  pruned = "no",
  hormone_added = "HFS",
  hormone_or_HFS_start_time = 5,
  theme_options = my_theme_options,
  treatment_colour_theme = my_theme_colours
)

 raw_eEPSC_repeated_plots
 
# ggsave(raw_eEPSC_repeated_plots$RMR5, path = here("Figures"), file = "raw_eEPSC_repeated_plots_RMR5.png", width = 7, height = 5, units = "in", dpi = 300)
 
 # remove the title and subtitle 
RMR5_plot <- raw_eEPSC_repeated_plots$RMR5 + theme(plot.subtitle = element_blank(), plot.title = element_blank())

RMR5_plot

# saving as png to figure folder
# ggsave(RMR5_plot, path = here("Figures"), file = "RMR5_plot.png", width = 7, height = 5, units = "in", dpi = 300)
```

```{r eval=FALSE}
raw_eEPSC_cort_plots <- plot_raw_current_data(
 data = normalized_raw_eEPSC_df, 
  plot_treatment = "Cort", 
  plot_category = 1, 
  current_type = "eEPSC",
  y_variable = "P1",
  pruned = "no",
  hormone_added = "HFS",
  hormone_or_HFS_start_time = 5,
  theme_options = my_theme_options,
  treatment_colour_theme = my_theme_colours
)

 raw_eEPSC_cort_plots
```


## Pruned Plots per Cell
Prune full cells from the normalized raw data: FOR FULL CELLS ONLY
```{r}
# pruning averages data per minute

pruned_eEPSC_df <- make_pruned_EPSC_data(
  data = normalized_raw_eEPSC_df,
  current_type = "eEPSC",
  min_time_value = 0, 
  max_time_value = 30,
  baseline_length = 5, 
  interval_length = 1
)

pruned_eEPSC_df$individual_cells
```

```{r}
# all cells
all_pruned_eEPSC_df <- make_pruned_EPSC_data(
  data = normalized_raw_eEPSC_df,
  current_type = "eEPSC",
  min_time_value = 0,
  max_time_value = 30,
  baseline_length = 5,
  interval_length = 1
)

all_pruned_eEPSC_df$individual_cells
```


Plot Pruned NAIVE Data
```{r eval=FALSE}
pruned_eEPSC_naive_plots <- plot_raw_current_data(
  data = pruned_eEPSC_df$individual_cells,
  plot_treatment = "Control",
  plot_category = 1,
  current_type = "eEPSC",
  y_variable = "mean_P1",
  pruned = "yes",
  hormone_added = "HFS",
  hormone_or_HFS_start_time = 5,
  theme_options = my_theme_options,
  treatment_colour_theme = my_theme_colours
)

pruned_eEPSC_naive_plots
```
Plot Pruned ACUTE Data
```{r eval=FALSE}
pruned_eEPSC_acute_plots <- plot_raw_current_data(
  data = pruned_eEPSC_df$individual_cells,
  plot_treatment = "Control",
  plot_category = 2,
  current_type = "eEPSC",
  y_variable = "mean_P1",
  pruned = "yes",
  hormone_added = "HFS",
  hormone_or_HFS_start_time = 5,
  theme_options = my_theme_options,
  treatment_colour_theme = my_theme_colours
)

pruned_eEPSC_acute_plots

RMA1_pruned_plot <- pruned_eEPSC_acute_plots$RMA1 + theme(plot.subtitle = element_blank(), plot.title = element_blank())

RMA1_pruned_plot

# saving as png to figure folder
# ggsave(RMA1_pruned_plot, path = here("Figures"), file = "RMA1_pruned_plot.png", width = 7, height = 5, units = "in", dpi = 300)
```


Plot Pruned ACUTE Data with AM251
```{r eval=FALSE}
pruned_eEPSC_acute_plots_AM251 <- plot_raw_current_data(
  data = pruned_eEPSC_df$individual_cells,
  plot_treatment = "AM251",
  plot_category = 2,
  current_type = "eEPSC",
  y_variable = "mean_P1",
  pruned = "yes",
  hormone_added = "HFS",
  hormone_or_HFS_start_time = 5,
  theme_options = my_theme_options,
  treatment_colour_theme = my_theme_colours
)

pruned_eEPSC_acute_plots_AM251
```
Plot Pruned REPEATED Data
```{r eval=FALSE}
pruned_eEPSC_repeated_plots <- plot_raw_current_data(
  data = pruned_eEPSC_df$individual_cells,
  plot_treatment = "Control",
  plot_category = 3,
  current_type = "eEPSC",
  y_variable = "mean_P1",
  pruned = "yes",
  hormone_added = "HFS",
  hormone_or_HFS_start_time = 5,
  theme_options = my_theme_options,
  treatment_colour_theme = my_theme_colours
)

pruned_eEPSC_repeated_plots

# MR11, MR12, maybe MR7 baselines might be questionable
```

```{r eval=FALSE}
pruned_eEPSC_cort_plots <- plot_raw_current_data(
  data = pruned_eEPSC_df$individual_cells,
  plot_treatment = "Cort",
  plot_category = 1,
  current_type = "eEPSC",
  y_variable = "mean_P1",
  pruned = "yes",
  hormone_added = "HFS",
  hormone_or_HFS_start_time = 5,
  theme_options = my_theme_options,
  treatment_colour_theme = my_theme_colours
)

pruned_eEPSC_cort_plots
```


## Summary Plots
Summary DATA
```{r}
summary_eEPSC_df <- make_summary_EPSC_data(
  data = normalized_raw_eEPSC_df, # not pruned
  current_type = "eEPSC",
  save_output_as_RDS = "no",
  baseline_interval = "t0to5",
  ending_interval = "t25to30"
)
summary_eEPSC_df # what I will use in my summary data stuff and plots from now on

# gives percent change, mean, and SE

# Summary Plots (use PRUNED data, for visual ease, but t-tests are done with the SUMMARY data)

# Category 1 is naive, 2 is acute
```


Summary Plots (use PRUNED data, for visual ease)
### summary plots
Naive FEMALE Summary: (only FULL)
```{r}
naive_summary_plot <- plot_summary_current_data(
  data = pruned_eEPSC_df$all_cells,
  plot_category = 1,
  plot_treatment = "Control",
  current_type = "eEPSC",
  y_variable = "amplitude",
  hormone_added = "HFS",
  hormone_or_HFS_start_time = 5,
  included_sexes = "female",
  include_representative_trace = "no",
  representative_trace_filename = import_ext_data("Control-trace.png"),
  y_axis_limit = 230,
  # signif_stars = "yes",
  geom_signif_text_size = 8,
  t_test_df = NULL,
  large_axis_text = "no",
  legend_position = "inside",
  shade_intervals = "no",
  treatment_colour_theme = my_theme_colours,
  theme_options = my_theme_options,
  save_plot_png = "no"
) #+ theme(legend.position = "none")

naive_summary_plot

# saving as png to figure folder
# ggsave(naive_summary_plot, path = here("Figures"), file = "naive_summary_plot.png", width = 7, height = 5, units = "in", dpi = 300)
```

Naive MALE Summary:
```{r}
male_naive_summary_plot <- plot_summary_current_data(
  data = pruned_eEPSC_df$all_cells,
  plot_category = 1,
  plot_treatment = "Control",
  current_type = "eEPSC",
  y_variable = "amplitude",
  hormone_added = "HFS",
  hormone_or_HFS_start_time = 5,
  included_sexes = "male",
  include_representative_trace = "no",
  representative_trace_filename = import_ext_data("Control-trace.png"),
  y_axis_limit = 230,
  # signif_stars = "yes",
  geom_signif_text_size = 8,
  t_test_df = NULL,
  large_axis_text = "no",
  legend_position = "inside",
  shade_intervals = "no",
  treatment_colour_theme = my_theme_colours,
  theme_options = my_theme_options,
  save_plot_png = "no"
) #+ theme(legend.position = "none")

male_naive_summary_plot

# ggsave(male_naive_summary_plot, path = here("Figures"), file = "male_naive_summary_plot.png", width = 7, height = 5, units = "in", dpi = 300)
```

Acute FEMALE Summary: (only FULL)
```{r eval = FALSE}
# Christlinda's package
acute_summary_plot <- plot_summary_current_data(
  data = pruned_eEPSC_df$all_cells, 
  plot_category = 2,
  plot_treatment = "Control",
  current_type = "eEPSC",
  y_variable = "amplitude",
  hormone_added = "HFS",
  hormone_or_HFS_start_time = 5,
  included_sexes = "female",
  include_representative_trace = "no",
  representative_trace_filename = "Figures/Representative-Traces/acute_trace.png",
  y_axis_limit = 230,
  # signif_stars = "yes",
  geom_signif_text_size = 8,
  t_test_df = NULL, 
  large_axis_text = "no",
  legend_position = "inside",
  shade_intervals = "no",
  treatment_colour_theme = my_theme_colours,
  theme_options = my_theme_options,
  save_plot_png = "no"
) # + theme(legend.position = "none") # keeping this hashed out keeps the n = # label in

acute_summary_plot

# saving as png to figure folder
# ggsave(acute_summary_plot, path = here("Figures"), file = "acute_summary_plot.png", width = 7, height = 5, units = "in", dpi = 300)
```
```{r}
# from linear mixed model
female_acute_summary_sig_df <- tibble(
  time = c(22.5, 27.5), # where on the x-axis
  y = c(170, 170), # y-axis
  label = c("**", "**")
)

female_acute_summary_plot <- pruned_eEPSC_df$all_cells %>%
  filter(sex == "Female",
         category == 2,
         treatment == "Control") %>%
  ggplot(aes(x = time,
             y = mean_P1_all_cells,
             ymin = mean_P1_all_cells - se_P1_all_cells,
             ymax = mean_P1_all_cells + se_P1_all_cells,
             colour = "acute")) +
  
  geom_pointrange(size = 0.9, shape = 16) +
  ylim(0, 230) +
  labs(x = "Time (min)", y = "eEPSC Amplitude (% Baseline)", colour = NULL) +
  geom_hline(yintercept = 100, linetype = "dashed") +
  
  scale_colour_manual(
    values = c("acute" = "#f19cac"),
    labels = c("acute" = "Acute, n = 8")
  ) +
  
  # significance stars
  geom_text(
    data = female_acute_summary_sig_df,
    aes(x = time, y = y, label = label),
    inherit.aes = FALSE,
    colour = "black",
    size = 8
  ) +
  
  annotate(
    geom = "text",
    x = 5,
    y = 220,
    label = "HFS",
    size = 4,
    hjust = 0.5
  ) +
  
  annotate(
    geom = "segment",
    x = 5,
    y = 210,
    xend = 5,
    yend = 190,
    arrow = grid::arrow(type = "closed", length = grid::unit(0.02, "npc"))
  ) +
  
  patchclampplotteR_theme() +
  theme(
    legend.position = "inside",
    legend.position.inside = c(0.025, 0.05),
    legend.justification = c(0, 0)
  )

female_acute_summary_plot

# ggsave(female_acute_summary_plot, path = here("Figures"), file = "female_acute_summary_plot.png", width = 7, height = 5, units = "in", dpi = 300)
```


FEMALE TREATMENT 1 COMBINED (only FULL)
```{r}
female_acute_naive_summary_plot <- pruned_eEPSC_df$all_cells %>%
  filter(sex == "Female" & category %in% c(1,2) & treatment == "Control") %>%
  ggplot(aes(x = time, y = mean_P1_all_cells, ymin = mean_P1_all_cells - se_P1_all_cells, ymax = mean_P1_all_cells + se_P1_all_cells, colour = category)) +
  geom_pointrange(size = 0.9, shape = 16) +
  ylim(0,230) +
  labs(x = "Time (min)", y = "eEPSC Amplitude (% Baseline)", colour = NULL) + # NULL for legend heading
  geom_hline(yintercept = 100, linetype = "dashed") +
  scale_colour_manual(values = c("lightgrey", "#f19cac"), labels = c("Naive, n = 10", "Acute, n = 8")) + 
  
  # add HFS text
  annotate(
        geom = "text",
        x = 5,
        y = 220,
        label = "HFS",
        size = 4,
        hjust = 0.5
      ) +
  
  # add arrow
   annotate(
        geom = "segment",
        x = 5,
        y = 210,
        xend = 5,
        yend = 190,
        arrow = grid::arrow(type = "closed", length = grid::unit(0.02, "npc"))
      ) +
  
# significance stars
  geom_text(
    data = female_acute_summary_sig_df,
    aes(x = time, y = y, label = label),
    inherit.aes = FALSE,
    colour = "black",
    size = 8
  ) +
  
  patchclampplotteR_theme() +
  theme(
    legend.position = "inside",
    legend.position.inside = c(0.025, 0.05),
    legend.justification = c(0, 0)
  )

female_acute_naive_summary_plot

ggsave(female_acute_naive_summary_plot, path = here("Figures"), file = "female_acute_naive_summary_plot.png", width = 7, height = 5, units = "in", dpi = 300)
```

```{r}
female_naive_summary_plot <- pruned_eEPSC_df$all_cells %>%
  filter(sex == "Female",
         category == 1,
         treatment == "Control") %>%
  ggplot(aes(x = time,
             y = mean_P1_all_cells,
             ymin = mean_P1_all_cells - se_P1_all_cells,
             ymax = mean_P1_all_cells + se_P1_all_cells,
             colour = "Naive")) +
  
  geom_pointrange(size = 0.9, shape = 16) +
  ylim(0, 230) +
  labs(x = "Time (min)", y = "eEPSC Amplitude (% Baseline)", colour = NULL) +
  geom_hline(yintercept = 100, linetype = "dashed") +
  
  scale_colour_manual(
    values = c("Naive" = "#f5e0b3"),
    labels = c("Naive" = "Naive, n = 10")
  ) +
  
  annotate(
    geom = "text",
    x = 5,
    y = 220,
    label = "HFS",
    size = 4,
    hjust = 0.5
  ) +
  
  annotate(
    geom = "segment",
    x = 5,
    y = 210,
    xend = 5,
    yend = 190,
    arrow = grid::arrow(type = "closed", length = grid::unit(0.02, "npc"))
  ) +
  
  patchclampplotteR_theme() +
  theme(
    legend.position = "inside",
    legend.position.inside = c(0.025, 0.05),
    legend.justification = c(0, 0)
  )

female_naive_summary_plot

ggsave(female_naive_summary_plot, path = here("Figures"), file = "female_naive_summary_plot.png", width = 7, height = 5, units = "in", dpi = 300)
```

```{r}
female_stress_plot <- pruned_eEPSC_df$all_cells %>%
  filter(sex == "Female" & category %in% c(1,2,3) & treatment %in% c("Control","AM251")) %>%
  ggplot(aes(x = time, 
             y = mean_P1_all_cells, 
             ymin = mean_P1_all_cells - se_P1_all_cells, 
             ymax = mean_P1_all_cells + se_P1_all_cells, 
             colour = interaction(category, treatment))) +
  
  geom_pointrange(size = 0.9, shape = 16) +
  ylim(0,230) +
  labs(x = "Time (min)", y = "eEPSC Amplitude (% Baseline)", colour = NULL) + # NULL for legend heading
  geom_hline(yintercept = 100, linetype = "dashed") +
 
   scale_colour_manual(
    values = c(
      "1.Control" = "#f5e0b3",
      "2.Control" = "#f19cac",
      "2.AM251"   = "#FFADFF",
      "3.Control" = "#6497b1"
    ),
    breaks = c(
      "1.Control",
      "2.Control",
      "2.AM251",
      "3.Control"
    ),
    labels = c(
      "1.Control" = "Naive, n = 10",
      "2.Control" = "Acute, n = 8",
      "2.AM251"   = "Acute with AM251, n = 10",
      "3.Control" = "Repeated, n = 9"
    )
  ) +
  
  # add HFS text
  annotate(
        geom = "text",
        x = 5,
        y = 220,
        label = "HFS",
        size = 4,
        hjust = 0.5
      ) +
  
  # add arrow
   annotate(
        geom = "segment",
        x = 5,
        y = 210,
        xend = 5,
        yend = 190,
        arrow = grid::arrow(type = "closed", length = grid::unit(0.02, "npc"))
      ) +
  patchclampplotteR_theme() +
  
  theme(
    legend.position = "right",
    #legend.position.inside = c(0.025, 0.05),
    #legend.justification = c(0, 0)
  )

female_stress_plot

# ggsave(female_stress_plot, path = here("Figures"), file = "female_stress_plot.png", width = 9, height = 5, units = "in", dpi = 300)
```


MALE TREATMENT 1 COMBINED
```{r}
male_treatment1_plot <- pruned_eEPSC_df$all_cells %>%
  filter(sex == "Male" & category %in% c(1,2) & treatment == "Control") %>%
  
  ggplot(aes(x = time, y = mean_P1_all_cells, ymin = mean_P1_all_cells - se_P1_all_cells, ymax = mean_P1_all_cells + se_P1_all_cells, colour = category)) +
  geom_pointrange(size = 0.9, shape = 17) +
  ylim(0,230) +
  labs(x = "Time (min)", y = "eEPSC Amplitude (% Baseline)", colour = NULL) + # NULL for legend heading
  geom_hline(yintercept = 100, linetype = "dashed") +
  scale_colour_manual(values = c("lightgrey", "#f19cac"), labels = c("Naive, n = 13", "Acute, n = 8")) +
  
 # add HFS text
  annotate(
        geom = "text",
        x = 5,
        y = 220,
        label = "HFS",
        size = 4,
        hjust = 0.5
      ) +
  
  # add arrow  
  annotate(
        geom = "segment",
        x = 5,
        y = 210,
        xend = 5,
        yend = 190,
        arrow = grid::arrow(type = "closed", length = grid::unit(0.02, "npc"))
      ) +
  
  patchclampplotteR_theme() +
  theme(
    legend.position = "inside",
    legend.position.inside = c(0.025, 0.05),
    legend.justification = c(0, 0)
  )

male_treatment1_plot

# ggsave(male_treatment1_plot, path = here("Figures"), file = "male_treatment1_plot.png", width = 7, height = 5, units = "in", dpi = 300)
```


Acute FEMALE Summary with AM251: (only FULL)
```{r eval = FALSE}
# Christelinda's package
am251_acute_summary_plot <- plot_summary_current_data(
  data = pruned_eEPSC_df$all_cells, 
  plot_category = 2,
  plot_treatment = "AM251",
  current_type = "eEPSC",
  y_variable = "amplitude",
  hormone_added = "HFS",
  hormone_or_HFS_start_time = 5,
  included_sexes = "female",
  include_representative_trace = "no",
  representative_trace_filename = import_ext_data("Control-trace.png"),
  y_axis_limit = 230,
  # signif_stars = "yes",
  geom_signif_text_size = 8,
  t_test_df = NULL, 
  large_axis_text = "no",
  legend_position = "inside",
  shade_intervals = "no",
  treatment_colour_theme = my_theme_colours,
  theme_options = my_theme_options,
  save_plot_png = "no"
) #+ theme(legend.position = "none") keeping this hashed out keeps the n = # label in

am251_acute_summary_plot

# ggsave(am251_acute_summary_plot, path = here("Figures"), file = "am251_acute_summary_plot.png", width = 7, height = 5, units = "in", dpi = 300)
```

```{r}
female_am251_summary_plot <- pruned_eEPSC_df$all_cells %>%
  filter(sex == "Female",
         category == 2,
         treatment == "AM251") %>%
  ggplot(aes(x = time,
             y = mean_P1_all_cells,
             ymin = mean_P1_all_cells - se_P1_all_cells,
             ymax = mean_P1_all_cells + se_P1_all_cells,
             colour = "AM251")) +
  
  geom_pointrange(size = 0.9, shape = 16) +
  ylim(0, 230) +
  labs(x = "Time (min)", y = "eEPSC Amplitude (% Baseline)", colour = NULL) +
  geom_hline(yintercept = 100, linetype = "dashed") +
  
  scale_colour_manual(
    values = c("AM251" = "#FFADFF"),
    labels = c("AM251" = "Acute with AM251, n = 10")
  ) +
  
  annotate(
    geom = "text",
    x = 5,
    y = 220,
    label = "HFS",
    size = 4,
    hjust = 0.5
  ) +
  
  annotate(
    geom = "segment",
    x = 5,
    y = 210,
    xend = 5,
    yend = 190,
    arrow = grid::arrow(type = "closed", length = grid::unit(0.02, "npc"))
  ) +
  
  patchclampplotteR_theme() +
  theme(
    legend.position = "inside",
    legend.position.inside = c(0.025, 0.05),
    legend.justification = c(0, 0)
  )

female_am251_summary_plot

# ggsave(female_am251_summary_plot, path = here("Figures"), file = "female_am251_summary_plot.png", width = 7, height = 5, units = "in", dpi = 300)
```


REPEATED FEMALE Summary: (only FULL)
```{r eval = FALSE}
# Christelinda's package
repeated_summary_plot <- plot_summary_current_data(
  data = pruned_eEPSC_df$all_cells, 
  plot_category = 3,
  plot_treatment = "Control",
  current_type = "eEPSC",
  y_variable = "amplitude",
  hormone_added = "HFS",
  hormone_or_HFS_start_time = 5,
  included_sexes = "female",
  include_representative_trace = "no",
  representative_trace_filename = import_ext_data("Control-trace.png"),
  y_axis_limit = 230,
  # signif_stars = "yes",
  geom_signif_text_size = 8,
  t_test_df = NULL, 
  large_axis_text = "no",
  legend_position = "inside",
  shade_intervals = "no",
  treatment_colour_theme = my_theme_colours,
  theme_options = my_theme_options,
  save_plot_png = "no"
) #+ theme(legend.position = "none") keeping this hashed out keeps the n = # label in

repeated_summary_plot

# ggsave(repeated_summary_plot, path = here("Figures"), file = "repeated_summary_plot.png", width = 7, height = 5, units = "in", dpi = 300)
```
```{r}
female_repeated_summary_plot <- pruned_eEPSC_df$all_cells %>%
  filter(sex == "Female",
         category == 3,
         treatment == "Control") %>%
  ggplot(aes(x = time,
             y = mean_P1_all_cells,
             ymin = mean_P1_all_cells - se_P1_all_cells,
             ymax = mean_P1_all_cells + se_P1_all_cells,
             colour = "repeated")) +
  
  geom_pointrange(size = 0.9, shape = 16) +
  ylim(0, 230) +
  labs(x = "Time (min)", y = "eEPSC Amplitude (% Baseline)", colour = NULL) +
  geom_hline(yintercept = 100, linetype = "dashed") +
  
  scale_colour_manual(
    values = c("repeated" = "#6497b1"),
    labels = c("repeated" = "Repeated, n = 9")
  ) +
  
  annotate(
    geom = "text",
    x = 5,
    y = 220,
    label = "HFS",
    size = 4,
    hjust = 0.5
  ) +
  
  annotate(
    geom = "segment",
    x = 5,
    y = 210,
    xend = 5,
    yend = 190,
    arrow = grid::arrow(type = "closed", length = grid::unit(0.02, "npc"))
  ) +
  
  patchclampplotteR_theme() +
  theme(
    legend.position = "inside",
    legend.position.inside = c(0.025, 0.05),
    legend.justification = c(0, 0)
  )

female_repeated_summary_plot

# ggsave(female_repeated_summary_plot, path = here("Figures"), file = "female_repeated_summary_plot.png", width = 7, height = 5, units = "in", dpi = 300)
```


REPEATED MALE Summary:
```{r}
male_repeated_summary_plot <- plot_summary_current_data(
  data = pruned_eEPSC_df$all_cells, 
  plot_category = 3,
  plot_treatment = "Control",
  current_type = "eEPSC",
  y_variable = "amplitude",
  hormone_added = "HFS",
  hormone_or_HFS_start_time = 5,
  included_sexes = "male",
  include_representative_trace = "no",
  representative_trace_filename = import_ext_data("Control-trace.png"),
  y_axis_limit = 230,
  # signif_stars = "yes",
  geom_signif_text_size = 8,
  t_test_df = NULL, 
  large_axis_text = "no",
  legend_position = "inside",
  shade_intervals = "no",
  treatment_colour_theme = my_theme_colours,
  theme_options = my_theme_options,
  save_plot_png = "no"
) #+ theme(legend.position = "none") keeping this hashed out keeps the n = # label in

male_repeated_summary_plot

# ggsave(male_repeated_summary_plot, path = here("Figures"), file = "male_repeated_summary_plot.png", width = 7, height = 5, units = "in", dpi = 300)

```


Acute MALE Summary:
```{r}
male_acute_summary_plot <- plot_summary_current_data(
  data = pruned_eEPSC_df$all_cells, 
  plot_category = 2,
  plot_treatment = "Control",
  current_type = "eEPSC",
  y_variable = "amplitude",
  hormone_added = "HFS",
  hormone_or_HFS_start_time = 5,
  included_sexes = "male",
  include_representative_trace = "no",
  representative_trace_filename = import_ext_data("Control-trace.png"),
  y_axis_limit = 230,
  # signif_stars = "yes",
  geom_signif_text_size = 8,
  t_test_df = NULL, 
  large_axis_text = "no",
  legend_position = "inside",
  shade_intervals = "no",
  treatment_colour_theme = my_theme_colours,
  theme_options = my_theme_options,
  save_plot_png = "no"
) #+ theme(legend.position = "none") keeping this hashed out keeps the n = # label in

male_acute_summary_plot

# ggsave(male_acute_summary_plot, path = here("Figures"), file = "male_acute_summary_plot.png", width = 7, height = 5, units = "in", dpi = 300)
```

CORT FEMALE Summary:
```{r}
female_cort_summary_plot <- pruned_eEPSC_df$all_cells %>%
  filter(sex == "Female" & category %in% c(1) & treatment == "Cort") %>%
  ggplot(aes(x = time, y = mean_P1_all_cells, ymin = mean_P1_all_cells - se_P1_all_cells, ymax = mean_P1_all_cells + se_P1_all_cells, colour = category)) +
  geom_pointrange(size = 0.9, shape = 16) +
  ylim(0,230) +
  labs(x = "Time (min)", y = "eEPSC Amplitude (% Baseline)", colour = NULL) + # NULL for legend heading
  geom_hline(yintercept = 100, linetype = "dashed") +
  scale_colour_manual(values = c("#93c47d"), labels = c("Naive with Corticosterone, n = 7")) + 
  
  # add HFS text
  annotate(
        geom = "text",
        x = 5,
        y = 220,
        label = "HFS",
        size = 4,
        hjust = 0.5
      ) +
  
  # add arrow
   annotate(
        geom = "segment",
        x = 5,
        y = 210,
        xend = 5,
        yend = 190,
        arrow = grid::arrow(type = "closed", length = grid::unit(0.02, "npc"))
      ) +
  patchclampplotteR_theme() +
  theme(
    legend.position = "inside",
    legend.position.inside = c(0.025, 0.05),
    legend.justification = c(0, 0)
  )

female_cort_summary_plot

# ggsave(female_cort_summary_plot, path = here("Figures"), file = "female_cort_summary_plot.png", width = 7, height = 5, units = "in", dpi = 300)
```


### overall summary percent change mean and SE for eEPSC
summary data has both full and baseline only cells
```{r}
female_percentchange_eEPSC_summary <- summary_eEPSC_df$percent_change_data %>%
  filter(sex == "Female" & category %in% c(1, 2, 3) & treatment %in% c("Control", "AM251", "Cort")) %>%
  mutate(cat_treat = factor(
    interaction(category, treatment),
    levels = c("1.Control", "2.Control", "2.AM251", "3.Control", "1.Cort")
  )) %>%
  group_by(cat_treat) %>%  
  summarise(
    n = n(),
    mean_percentchange = mean(percent_change, na.rm = TRUE),
    sd_percentchange = sd(percent_change, na.rm = TRUE), 
    se_percentchange = sd_percentchange / sqrt(n), 
    .groups = "drop"  
  )
female_percentchange_eEPSC_summary
```

### eEPSC mean and SE 
```{r}
# baseline
female_baseline_eEPSC_summary <- summary_eEPSC_df$percent_change_data %>%
  filter(sex == "Female" & category %in% c(1, 2, 3) & treatment %in% c("Control", "AM251", "Cort")) %>%
  mutate(cat_treat = factor(
    interaction(category, treatment),
    levels = c("1.Control", "2.Control", "2.AM251", "3.Control", "1.Cort")
  )) %>%
  group_by(cat_treat) %>%  
  summarise(
    n = n(),
    mean_amplitude = mean(t0to5, na.rm = TRUE),
    sd_amplitude = sd(t0to5, na.rm = TRUE), 
    se_amplitude = sd_amplitude / sqrt(n), 
    .groups = "drop"  
  )
female_baseline_eEPSC_summary

# post HFS
female_HFS_eEPSC_summary <- summary_eEPSC_df$percent_change_data %>%
  filter(sex == "Female" & category %in% c(1, 2, 3) & treatment %in% c("Control", "AM251", "Cort") & !(letter %in% c("RMA100A", "RMR100", "RMR101", "RMR102", "RMR103", "RMR104", "RMR105", "RMR106", "RMR107"))) %>% # excluding baseline onlys
  mutate(cat_treat = factor(
    interaction(category, treatment),
    levels = c("1.Control", "2.Control", "2.AM251", "3.Control", "1.Cort")
  )) %>%
  group_by(cat_treat) %>%  
  summarise(
    n = n(),
    mean_amplitude = mean(t25to30, na.rm = TRUE),
    sd_amplitude = sd(t25to30, na.rm = TRUE), 
    se_amplitude = sd_amplitude / sqrt(n), 
    .groups = "drop"  
  )
female_HFS_eEPSC_summary
```



## Baseline eEPSC
### baseline naive and acute eEPSC only
```{r}
# data
female_acute_baseline_amp_plot <- summary_eEPSC_df$percent_change_data %>%
  filter(sex == "Female" & category %in% c(1,2) & treatment %in% c("Control")) %>% 
  mutate(cat_treat = factor(
    interaction(category, treatment),
    levels = c("1.Control", "2.Control")
  )) %>%
  
  ggplot(aes(x = cat_treat, y = t0to5)) +
  
  patchclampplotteR_theme() +
  
# axis labels
  labs(x = NULL, y = "Baseline eEPSC Amplitude (pA)") +
  patchclampplotteR_theme() +
  
# the boxes
  geom_boxplot(aes(fill = interaction(category, treatment), color = interaction(category, treatment)), 
               alpha = 0.6, 
               color = "black", # get rid of if want the dark colour to be the outline
# outlier.shape = NA stops the box plot from plotting outliers. BUT because the sina plot is a different layer, all outliers are still shown as dots from that.
               outlier.shape = NA, 
               width = 0.5, 
               show.legend = FALSE)  +
  
  # the dots/scatter plot
  geom_sina(aes(x = interaction(category, treatment), color = interaction(category, treatment)), 
            max_width = 0.2, 
            shape = 16, 
            size = 2, 
            show.legend = FALSE) +
  
   # significance bracket
  geom_signif(
    comparisons = list(c("1.Control", "2.Control")),
    map_signif_level = TRUE,
    annotations = "*", 
    y_position = 120,
    tip_length = 0.02,
    textsize = 7
  ) +

  # colours
  scale_fill_manual(values = c("1.Control" = "#f5e0b3",
                               "2.Control" = "#f19cac")) +
  
  scale_color_manual(values = c("1.Control" = "#ecc479", 
                                "2.Control" = "#eb647e")) +
  
  # x-axis labels  
scale_x_discrete(labels = c("Naive", "Acute")) +
  
# x-axis subtitles  
  #annotate("text", x = 1, y = -0.2, label = "n = 10", size = 4, hjust = 0.4) + 
  #annotate("text", x = 2, y = -0.2, label = "n = 8", size = 4, hjust = 0.5) + 
  #annotate("text", x = 3, y = -0.2, label = "n = 10", size = 4, hjust = 0.5) +
  
  scale_y_continuous(expand = expansion(mult = c(0.2, .2))) +

  guides(fill = "none", color = "none")

female_acute_baseline_amp_plot

# ggsave(female_acute_baseline_amp_plot, path = here("Figures"), file = "female_acute_baseline_amp_plot.png", width = 7, height = 5, units = "in", dpi = 300)
```

```{r}
# data
female_baseline_amp_plot <- summary_eEPSC_df$percent_change_data %>%
  filter(sex == "Female" & category %in% c(1,2, 3) & treatment %in% c("Control","AM251", "Cort")) %>% 
  mutate(cat_treat = factor(
    interaction(category, treatment),
    levels = c("1.Control", "2.Control", "2.AM251", "3.Control", "1.Cort")
  )) %>%
  
  ggplot(aes(x = cat_treat, y = t0to5)) +
  
  patchclampplotteR_theme() +
  
# axis labels
  labs(x = NULL, y = "Baseline eEPSC Amplitude (pA)") +
  patchclampplotteR_theme() +
  
# the boxes
  geom_boxplot(aes(fill = interaction(category, treatment), color = interaction(category, treatment)), 
               alpha = 0.6, 
               color = "black", # get rid of if want the dark colour to be the outline
# outlier.shape = NA stops the box plot from plotting outliers. BUT because the sina plot is a different layer, all outliers are still shown as dots from that.
               outlier.shape = NA, 
               width = 0.5, 
               show.legend = FALSE)  +
  
  # the dots/scatter plot
  geom_sina(aes(x = interaction(category, treatment), color = interaction(category, treatment)), 
            max_width = 0.2, 
            shape = 16, 
            size = 2, 
            show.legend = FALSE) +

  # colours
  scale_fill_manual(values = c("1.Control" = "#f5e0b3",
                               "2.Control" = "#f19cac",
                               "2.AM251" = "#ffadff",
                               "3.Control" = "#6497b1",
                               "1.Cort" = "#93c47d")) +
  
  scale_color_manual(values = c("1.Control" = "#ecc479", 
                                "2.Control" = "#eb647e", 
                                "2.AM251" = "#c11c84",
                                "3.Control" = "#005b96",
                                "1.Cort" = "#6aa84f")) +
  
  # x-axis labels  
scale_x_discrete(labels = c("Naive", "Acute", "Acute with AM251", "Repeated", "Naive with Corticosterone")) +
  
# x-axis subtitles  
  #annotate("text", x = 1, y = -0.2, label = "n = 10", size = 4, hjust = 0.4) + 
  #annotate("text", x = 2, y = -0.2, label = "n = 8", size = 4, hjust = 0.5) + 
  #annotate("text", x = 3, y = -0.2, label = "n = 10", size = 4, hjust = 0.5) +
  
  scale_y_continuous(expand = expansion(mult = c(0.2, .2))) +

  guides(fill = "none", color = "none")

female_baseline_amp_plot

# ggsave(female_baseline_amp_plot, path = here("Figures"), file = "female_baseline_amp_plot.png", width = 7, height = 5, units = "in", dpi = 300)
```
THESIS
```{r}
# data
thesis_female_baseline_amp_plot <- summary_eEPSC_df$percent_change_data %>%
  filter(sex == "Female" & category %in% c(1,2, 3) & treatment %in% c("Control","AM251")) %>% 
  mutate(cat_treat = factor(
    interaction(category, treatment),
    levels = c("1.Control", "2.Control", "2.AM251", "3.Control")
  )) %>%
  
  ggplot(aes(x = cat_treat, y = t0to5)) +
  
  patchclampplotteR_theme() +
  
# axis labels
  labs(x = NULL, y = "Baseline eEPSC Amplitude (pA)") +
  patchclampplotteR_theme() +
  
# the boxes
  geom_boxplot(aes(fill = interaction(category, treatment), color = interaction(category, treatment)), 
               alpha = 0.6, 
               color = "black", # get rid of if want the dark colour to be the outline
# outlier.shape = NA stops the box plot from plotting outliers. BUT because the sina plot is a different layer, all outliers are still shown as dots from that.
               outlier.shape = NA, 
               width = 0.5, 
               show.legend = FALSE)  +
  
  # the dots/scatter plot
  geom_sina(aes(x = interaction(category, treatment), color = interaction(category, treatment)), 
            max_width = 0.2, 
            shape = 16, 
            size = 2, 
            show.legend = FALSE) +

  # colours
  scale_fill_manual(values = c("1.Control" = "#f5e0b3",
                               "2.Control" = "#f19cac",
                               "2.AM251" = "#ffadff",
                               "3.Control" = "#6497b1")) +
  
  scale_color_manual(values = c("1.Control" = "#ecc479", 
                                "2.Control" = "#eb647e", 
                                "2.AM251" = "#c11c84",
                                "3.Control" = "#005b96")) +
  
  # x-axis labels  
scale_x_discrete(labels = c("Naive", "Acute", "Acute with AM251", "Repeated")) +
  
# x-axis subtitles  
  #annotate("text", x = 1, y = -0.2, label = "n = 10", size = 4, hjust = 0.4) + 
  #annotate("text", x = 2, y = -0.2, label = "n = 8", size = 4, hjust = 0.5) + 
  #annotate("text", x = 3, y = -0.2, label = "n = 10", size = 4, hjust = 0.5) +
  
  scale_y_continuous(expand = expansion(mult = c(0.2, .2))) +

  guides(fill = "none", color = "none")

thesis_female_baseline_amp_plot

ggsave(thesis_female_baseline_amp_plot, path = here("Figures"), file = "thesis_female_baseline_amp_plot.png", width = 7, height = 5, units = "in", dpi = 300)
```



eEPSC amplitude after the HFS (25-30 min)
## post HFS eEPSC (final)
```{r eval=FALSE}}
# data
female_HFS_amp_plot <- summary_eEPSC_df$percent_change_data %>%
  filter(sex == "Female" & category %in% c(1,2, 3) & treatment %in% c("Control","AM251", "Cort") & !(letter %in% c("RMA100A", "RMR100", "RMR101", "RMR102", "RMR103", "RMR104", "RMR105", "RMR106", "RMR107"))) %>% # excluding baseline onlys %>% 
  mutate(cat_treat = factor(
    interaction(category, treatment),
    levels = c("1.Control", "2.Control", "2.AM251", "3.Control", "1.Cort")
  )) %>%
  
  ggplot(aes(x = cat_treat, y = t25to30)) +
  
  patchclampplotteR_theme() +
  
# axis labels
  labs(x = NULL, y = "FINAL eEPSC Amplitude (pA)") +
  patchclampplotteR_theme() +
  
# the boxes
  geom_boxplot(aes(fill = interaction(category, treatment), color = interaction(category, treatment)), 
               alpha = 0.6, 
               color = "black", # get rid of if want the dark colour to be the outline
# outlier.shape = NA stops the box plot from plotting outliers. BUT because the sina plot is a different layer, all outliers are still shown as dots from that.
               outlier.shape = NA, 
               width = 0.5, 
               show.legend = FALSE)  +
  
  # the dots/scatter plot
  geom_sina(aes(x = interaction(category, treatment), color = interaction(category, treatment)), 
            max_width = 0.2, 
            shape = 16, 
            size = 2, 
            show.legend = FALSE) +
  
  # mean as a point
  #stat_summary(fun = mean, geom = "point", 
               #shape = 16, size = 4, color = "black") +
  
  # colours
  scale_fill_manual(values = c("1.Control" = "#f5e0b3",
                               "2.Control" = "#f19cac",
                               "2.AM251" = "#ffadff",
                               "3.Control" = "#6497b1",
                               "1.Cort" = "#93c47d")) +
  
  scale_color_manual(values = c("1.Control" = "#ecc479", 
                                "2.Control" = "#eb647e", 
                                "2.AM251" = "#c11c84",
                                "3.Control" = "#005b96",
                                "1.Cort" = "#6aa84f")) +
  
  # x-axis labels  
scale_x_discrete(labels = c("Naive", "Acute", "Acute with AM251", "Repeated", "Naive with Corticosterone")) +
  
# x-axis subtitles  
  #annotate("text", x = 1, y = -0.2, label = "n = 10", size = 4, hjust = 0.4) + 
  #annotate("text", x = 2, y = -0.2, label = "n = 8", size = 4, hjust = 0.5) + 
  #annotate("text", x = 3, y = -0.2, label = "n = 10", size = 4, hjust = 0.5) +

  
  scale_y_continuous(expand = expansion(mult = c(0.2, .2))) +

  guides(fill = "none", color = "none")

female_HFS_amp_plot
```

## PPR
Make PPR Dataset
includes full cells and baseline only
```{r}
PPR_df <- make_PPR_data(
  data = normalized_raw_eEPSC_df,
  include_all_treatments = "yes",
  list_of_treatments = "yes",
  PPR_min = 0,
  PPR_max = 5,
  baseline_interval = "t0to5",
  treatment_colour_theme = my_theme_colours
)
PPR_df

# adding group colulmn
PPR_df <- PPR_df %>%
  mutate(group = case_when(
    category == 1 & treatment == "Control" ~ "naive",
    category == 2 & treatment == "Control" ~ "acute",
    category == 2 & treatment == "AM251" ~ "AM251",
    category == 3 & treatment == "Control" ~ "repeated",
    category == 1 & treatment == "Cort" ~ "cort"
  )) 
```

```{r}
# cell means
PPR_cell_df <- PPR_df %>%
  group_by(letter, group, state, sex) %>%
  summarise(mean_PPR_cell = mean(PPR, na.rm = TRUE), .groups = "drop")


# BASELINE
# filtering sex and state
female_baseline_PPR_df <- PPR_cell_df %>%
  filter(sex == "Female", state == "Baseline") 

# getting the mean and se...
female_baseline_PPR_summary_df <- female_baseline_PPR_df %>%
  group_by(group) %>%
  summarise(
    n = n(),
    mean_PPR = mean(mean_PPR_cell, na.rm = TRUE),
    sd_PPR = sd(mean_PPR_cell, na.rm = TRUE),
    se_PPR = sd_PPR / sqrt(n),
    .groups = "drop"
  )
female_baseline_PPR_summary_df

# HFS
# filtering and adding group column
female_HFS_PPR_df <- PPR_cell_df %>%
  filter(sex == "Female", state == "Post-modification") 

# getting the mean and se...
female_HFS_PPR_summary_df <- female_HFS_PPR_df %>%
  group_by(group) %>%
  summarise(
    n = n(),
    mean_PPR = mean(mean_PPR_cell, na.rm = TRUE),
    sd_PPR = sd(mean_PPR_cell, na.rm = TRUE),
    se_PPR = sd_PPR / sqrt(n),
    .groups = "drop"
  )
female_HFS_PPR_summary_df


# only paired letters (for change over time)
female_paired_PPR_df <- PPR_cell_df %>%
  filter(sex == "Female", state %in% c("Baseline", "Post-modification")) %>%
  group_by(letter, group) %>%
  filter(n_distinct(state) == 2) %>%  # only keep letters with both states
  ungroup()
# rename to HFS
female_paired_PPR_df <- female_paired_PPR_df %>%
  mutate(state = ifelse(state == "Post-modification", "HFS", state))
```
### Thesis 
```{r}
# renaming to HFS
PPR_cell_df <- PPR_cell_df %>%
  mutate(state = recode_factor(state,
                        "Post-modification" = "HFS"))

# removing unpaired neurons (that are only baselines)
paired_PPR_cell_df <- PPR_cell_df %>%
  group_by(group, letter) %>%
  filter(n_distinct(state) == 2) %>%  
  ungroup()

# converting to wide format
wide_paired_PPR_cell_df <- paired_PPR_cell_df %>%
  select(group, sex, letter, state, mean_PPR_cell) %>%
  pivot_wider(names_from = state, values_from = mean_PPR_cell)


# adding difference column (for mean_PPR_cell) to test for normality
wide_paired_PPR_cell_df <- wide_paired_PPR_cell_df %>%
  mutate(diff = HFS - Baseline)

# filtering for only females
wide_female_paired_PPR_cell_df <- wide_paired_PPR_cell_df %>%
  filter(sex == "Female")



# testing for normality (all good)
shapiro.test(wide_female_paired_PPR_cell_df$diff[wide_female_paired_PPR_cell_df$group == "naive"])
qqnorm(wide_female_paired_PPR_cell_df$diff[wide_female_paired_PPR_cell_df$group == "naive"])
qqline(wide_female_paired_PPR_cell_df$diff[wide_female_paired_PPR_cell_df$group == "naive"])

shapiro.test(wide_female_paired_PPR_cell_df$diff[wide_female_paired_PPR_cell_df$group == "acute"])
qqnorm(wide_female_paired_PPR_cell_df$diff[wide_female_paired_PPR_cell_df$group == "acute"])
qqline(wide_female_paired_PPR_cell_df$diff[wide_female_paired_PPR_cell_df$group == "acute"])

shapiro.test(wide_female_paired_PPR_cell_df$diff[wide_female_paired_PPR_cell_df$group == "AM251"])
qqnorm(wide_female_paired_PPR_cell_df$diff[wide_female_paired_PPR_cell_df$group == "AM251"])
qqline(wide_female_paired_PPR_cell_df$diff[wide_female_paired_PPR_cell_df$group == "AM251"])

shapiro.test(wide_female_paired_PPR_cell_df$diff[wide_female_paired_PPR_cell_df$group == "repeated"]) 
qqnorm(wide_female_paired_PPR_cell_df$diff[wide_female_paired_PPR_cell_df$group == "repeated"])
qqline(wide_female_paired_PPR_cell_df$diff[wide_female_paired_PPR_cell_df$group == "repeated"])


# running the t-tests
# naive 
t.test(wide_female_paired_PPR_cell_df$HFS[wide_female_paired_PPR_cell_df$group == "naive"],
            wide_female_paired_PPR_cell_df$Baseline[wide_female_paired_PPR_cell_df$group == "naive"],
            paired = TRUE)

# acute
t.test(wide_female_paired_PPR_cell_df$HFS[wide_female_paired_PPR_cell_df$group == "acute"],
       wide_female_paired_PPR_cell_df$Baseline[wide_female_paired_PPR_cell_df$group == "acute"],
       paired = TRUE)

# AM251 
t.test(wide_female_paired_PPR_cell_df$HFS[wide_female_paired_PPR_cell_df$group == "AM251"],
       wide_female_paired_PPR_cell_df$Baseline[wide_female_paired_PPR_cell_df$group == "AM251"],
       paired = TRUE)

# repeated 
t.test(wide_female_paired_PPR_cell_df$HFS[wide_female_paired_PPR_cell_df$group == "repeated"],
       wide_female_paired_PPR_cell_df$Baseline[wide_female_paired_PPR_cell_df$group == "repeated"],
       paired = TRUE)
```

```{r}
naive_female_PPR_plot_data <- wide_female_paired_PPR_cell_df %>%
  filter(group == "naive") %>%
  pivot_longer(cols = c(Baseline, HFS),
               names_to = "state",
               values_to = "mean_PPR_cell")

# plot
naive_female_PPR_plot <- ggplot(naive_female_PPR_plot_data, aes(x = state, y = mean_PPR_cell, group = letter)) +
  
# individual cells
  geom_point(size = 1, colour = "lightgrey") +
  geom_line(colour = "lightgrey", alpha = 0.9) +
  
# mean point
  stat_summary(aes(group = 1), fun.data = mean_se, geom = "line", colour = "#ecc479", linewidth = 1.2) +
  stat_summary(aes(group = 1), fun.data = mean_se, geom = "point", colour = "#ecc479", size = 2.5) +
  
# significance bracket
  geom_signif(
    comparisons = list(c("Baseline", "HFS")),
    map_signif_level = TRUE,
    annotations = "ns", 
    y_position = max(naive_female_PPR_plot_data$mean_PPR_cell) * 1.05,
    tip_length = 0.02,
    textsize = 5
  ) +
  
# y-axis
  scale_y_continuous(limits = c(0, max(naive_female_PPR_plot_data$mean_PPR_cell) * 1.2)) +
  
# theme
  patchclampplotteR_theme() +
  labs(x = NULL, y = "PPR", title = NULL) +
  theme(legend.position = "none")

naive_female_PPR_plot

# ggsave(naive_female_PPR_plot, path = here("Figures"), file = "naive_female_PPR_plot.png", width = 7, height = 5, units = "in", dpi = 300)
```

```{r}
acute_female_PPR_plot_data <- wide_female_paired_PPR_cell_df %>%
  filter(group == "acute") %>%
  pivot_longer(cols = c(Baseline, HFS),
               names_to = "state",
               values_to = "mean_PPR_cell")

# plot
acute_female_PPR_plot <- ggplot(acute_female_PPR_plot_data, aes(x = state, y = mean_PPR_cell, group = letter)) +
  
# individual cells
  geom_point(size = 1, colour = "lightgrey") +
  geom_line(colour = "lightgrey", alpha = 0.9) +
  
# mean point
  stat_summary(aes(group = 1), fun.data = mean_se, geom = "line", colour = "#eb647e", linewidth = 1.2) +
  stat_summary(aes(group = 1), fun.data = mean_se, geom = "point", colour = "#eb647e", size = 2.5) +
  
# significance bracket
  geom_signif(
    comparisons = list(c("Baseline", "HFS")),
    map_signif_level = TRUE,
    annotations = "*", 
    y_position = max(acute_female_PPR_plot_data$mean_PPR_cell) * 1.05,
    tip_length = 0.02,
    textsize = 7
  ) +
  
# y-axis
  scale_y_continuous(limits = c(0, max(acute_female_PPR_plot_data$mean_PPR_cell) * 1.2)) +
  
# theme
  patchclampplotteR_theme() +
  labs(x = NULL, y = "PPR", title = NULL) +
  theme(legend.position = "none")

acute_female_PPR_plot

# ggsave(acute_female_PPR_plot, path = here("Figures"), file = "acute_female_PPR_plot.png", width = 7, height = 5, units = "in", dpi = 300)
```

```{r}
am251_female_PPR_plot_data <- wide_female_paired_PPR_cell_df %>%
  filter(group == "AM251") %>%
  pivot_longer(cols = c(Baseline, HFS),
               names_to = "state",
               values_to = "mean_PPR_cell")

# plot
am251_female_PPR_plot <- ggplot(am251_female_PPR_plot_data, aes(x = state, y = mean_PPR_cell, group = letter)) +
  
# individual cells
  geom_point(size = 1, colour = "lightgrey") +
  geom_line(colour = "lightgrey", alpha = 0.9) +
  
# mean point
  stat_summary(aes(group = 1), fun.data = mean_se, geom = "line", colour = "#C11C84", linewidth = 1.2) +
  stat_summary(aes(group = 1), fun.data = mean_se, geom = "point", colour = "#C11C84", size = 2.5) +
  
# significance bracket
  geom_signif(
    comparisons = list(c("Baseline", "HFS")),
    map_signif_level = TRUE,
    annotations = "ns", 
    y_position = max(am251_female_PPR_plot_data$mean_PPR_cell) * 1.05,
    tip_length = 0.02,
    textsize = 5
  ) +
  
# y-axis
  scale_y_continuous(limits = c(0, max(am251_female_PPR_plot_data$mean_PPR_cell) * 1.2)) +
  
# theme
  patchclampplotteR_theme() +
  labs(x = NULL, y = "PPR", title = NULL) +
  theme(legend.position = "none")

am251_female_PPR_plot

# ggsave(am251_female_PPR_plot, path = here("Figures"), file = "am251_female_PPR_plot.png", width = 7, height = 5, units = "in", dpi = 300)
```

```{r}
repeated_female_PPR_plot_data <- wide_female_paired_PPR_cell_df %>%
  filter(group == "repeated") %>%
  pivot_longer(cols = c(Baseline, HFS),
               names_to = "state",
               values_to = "mean_PPR_cell")

# plot
repeated_female_PPR_plot <- ggplot(repeated_female_PPR_plot_data, aes(x = state, y = mean_PPR_cell, group = letter)) +
  
# individual cells
  geom_point(size = 1, colour = "lightgrey") +
  geom_line(colour = "lightgrey", alpha = 0.9) +
  
# mean point
  stat_summary(aes(group = 1), fun.data = mean_se, geom = "line", colour = "#005b96", linewidth = 1.2) +
  stat_summary(aes(group = 1), fun.data = mean_se, geom = "point", colour = "#005b96", size = 2.5) +
  
# significance bracket
  geom_signif(
    comparisons = list(c("Baseline", "HFS")),
    map_signif_level = TRUE,
    annotations = "ns", 
    y_position = max(repeated_female_PPR_plot_data$mean_PPR_cell) * 1.05,
    tip_length = 0.02,
    textsize = 5
  ) +
  
# y-axis
  scale_y_continuous(limits = c(0, max(repeated_female_PPR_plot_data$mean_PPR_cell) * 1.2)) +
  
# theme
  patchclampplotteR_theme() +
  labs(x = NULL, y = "PPR", title = NULL) +
  theme(legend.position = "none")

repeated_female_PPR_plot

# ggsave(repeated_female_PPR_plot, path = here("Figures"), file = "repeated_female_PPR_plot.png", width = 7, height = 5, units = "in", dpi = 300)
```

female vs male acute PPR HFS
```{r eval=FALSE}
plot_PPR_data_single_treatment(
  data = PPR_df,
  plot_treatment = "Control",
  plot_category = 2,
  baseline_label = "Baseline",
  post_hormone_label = "HFS",
  included_sexes = "both",
  facet_by_sex = "yes",
  left_sex = "Female",
  test_type = "t.test",
  large_axis_text = "no",
  treatment_colour_theme = my_theme_colours,
  theme_options = my_theme_options,
  save_plot_png = "no"
)

# sig increase in the PPR after HFS
# higher PPR means lower probability of release
```

female vs male naive PPR HFS
```{r eval=FALSE}
plot_PPR_data_single_treatment(
  data = PPR_df,
  plot_treatment = "Control",
  plot_category = 1,
  baseline_label = "Baseline",
  post_hormone_label = "HFS",
  included_sexes = "both",
  facet_by_sex = "yes",
  left_sex = "Female",
  test_type = "t.test",
  large_axis_text = "no",
  treatment_colour_theme = my_theme_colours,
  theme_options = my_theme_options,
  save_plot_png = "no"
)
```

female vs male repeated PPR HFS
```{r eval=FALSE}
plot_PPR_data_single_treatment(
  data = PPR_df,
  plot_treatment = "Control",
  plot_category = 3,
  baseline_label = "Baseline",
  post_hormone_label = "HFS",
  included_sexes = "both",
  facet_by_sex = "yes",
  left_sex = "Female",
  test_type = "t.test",
  large_axis_text = "no",
  treatment_colour_theme = my_theme_colours,
  theme_options = my_theme_options,
  save_plot_png = "no"
)
```


### change in PPR female plot
```{r}
#1 group labels
  group_labels <- c(
    "naive" = "Naive",
    "acute" = "Acute",
    "AM251" = "Acute with AM251",
    "repeated" = "Repeated",
    "cort" = "Naive with Corticosterone")


# baseline only cells  
female_baseline_only_PPR_df <- female_baseline_PPR_df %>%
  filter(!(letter %in% female_paired_PPR_df$letter)) %>%  # only letters NOT in paired df
  mutate(state = "Baseline") %>%
  mutate(group = group)

#2 plot
female_PPR_plot <- female_paired_PPR_df %>%
  ggplot(aes(x = state, y = mean_PPR_cell)) + 

# baseline-only cells
  geom_point(data = female_baseline_only_PPR_df,
             aes(x = state, y = mean_PPR_cell),
             shape = 16, size = 1.5, colour = "lightgrey") +
  
# paired individual cells  
  geom_point(aes(shape = sex),size = 1, colour = "lightgrey") + 
  geom_line(aes(group = letter), colour = "lightgrey", alpha = 0.9) + 
  
# group mean + SE
  stat_summary(aes(group = 1, colour = group),
               fun.data = mean_se,
               geom = "line",
               linewidth = 1.2) +
  stat_summary(aes(group = 1,shape = sex,colour = group),
    fun.data = mean_se,
    geom = "point",
    size = 2.5
  ) +  
 
# colours and shapes
  scale_colour_manual(values = c(
    "naive" = "#f5e0b3", # or "darkgrey"
    "acute" = "#f19cac",
    "AM251" = "#FFADFF",
    "repeated" = "#6497b1",
    "cort" = "#93c47d"
  )) +
scale_shape_manual(values = c("Female" = 16, "Male" = 17)) +
  
# facet by group in order
  facet_wrap(~ group, labeller = as_labeller(group_labels), nrow = 1) + # nrow = 1 makes it all on one line
  # want to change order but whatever
  
# add significance brackets
  geom_signif(
    comparisons = list(c("Baseline", "HFS")),
    test = "t.test",
    test.args = list(paired = TRUE),
    map_signif_level = function(p)
        if (p <= 0.0001) {
          return("****")
        } else {
          if (p <= 0.001) {
            return("***")
          } else {
            if (p <= 0.01) {
              return("**")
            } else {
              if (p <= 0.05) {
                return("*")
              } else {
                if (p < 0.1 & p > 0.05) {
                  return(signif(p, 3))
                } else {
                  return("ns")
                }
              }
            }
          }
        }
, # or TRUE for stars, # FALSE for values
    vjust = -0.3,
    textsize = 5,
    size = 0.5,
    margin_top = 0.1,
    extend_line = 0.03
  ) +
  
# expand y-axis so the brackets don't overlap with labels
  scale_y_continuous(expand = expansion(mult = c(0.2, .2))) +
  
# theme and titles
  patchclampplotteR_theme() +
  labs(x = NULL, y = "PPR", title = NULL) +
  theme(legend.position = "none")  # remove legend

female_PPR_plot

# ggsave(female_PPR_plot, path = here("Figures"), file = "female_PPR_plot.png", width = 7, height = 5, units = "in", dpi = 300)
```


### PPR with ALL SEXES AND TREATMENTS
```{r eval=FALSE}
#1 facet labels
  facet_labels <- c(
    "1.Control.Female" = "Female Naive",
    "1.Control.Male" = "Male Naive",
    "2.Control.Female" = "Female Acute",
    "2.Control.Male" = "Male Acute",
    "2.AM251.Female" = "Acute with AM251",
    "3.Control.Female" = "Female Repeated",
    "3.Control.Male" = "Male Repeated")

#2 making the data frame for individual cells
PPR_plot_df <- PPR_df %>%
  filter(state %in% c("Baseline", "Post-modification")) %>% 
  mutate(
    state = ifelse(state == "Post-modification", "HFS", state)) %>% # rename to HFS
 mutate(facet_group = factor(interaction(category, treatment, sex),
                              levels = names(facet_labels))) %>%
  group_by(letter, state, category, treatment, sex, facet_group) %>%
  summarize(mean_PPR_cell = mean(PPR, na.rm = TRUE), .groups = "drop")  
   
#3 plot
PPR_plot <- PPR_plot_df %>%
  ggplot(aes(x = state, y = mean_PPR_cell)) + 

# individual  cells  
  geom_point(aes(shape = sex),size = 1, colour = "lightgrey") + 
  geom_line(aes(group = letter), colour = "lightgrey", alpha = 0.9) + 
  
# group mean
  stat_summary(aes(group = 1, colour = interaction(category, treatment)),
               fun.data = mean_se,
               geom = "line",
               linewidth = 1.2) +
  
  stat_summary(aes(group = 1,shape = sex,colour = interaction(category, treatment)),
    fun.data = mean_se,
    geom = "point",
    size = 2.5
  ) +  
 
# colours and shapes
  scale_colour_manual(values = c(
    "1.Control" = "#f5e0b3", # or "darkgrey"
    "2.Control" = "#f19cac",
    "2.AM251" = "#FFADFF",
    "3.Control" = "#6497b1"
  )) +
scale_shape_manual(values = c("Female" = 16, "Male" = 17)) +
  
# facet with labels and order
  facet_wrap(~ facet_group, labeller = as_labeller(facet_labels), nrow = 2) +
  
# add significance brackets
  geom_signif(
    comparisons = list(c("Baseline", "HFS")),
    test = "t.test",
    test.args = list(paired = TRUE),
    map_signif_level = function(p)
        if (p <= 0.0001) {
          return("****")
        } else {
          if (p <= 0.001) {
            return("***")
          } else {
            if (p <= 0.01) {
              return("**")
            } else {
              if (p <= 0.05) {
                return("*")
              } else {
                if (p < 0.1 & p > 0.05) {
                  return(signif(p, 3))
                } else {
                  return("ns")
                }
              }
            }
          }
        }
, # or TRUE for stars, # FALSE for values
    vjust = -0.3,
    textsize = 5,
    size = 0.5,
    margin_top = 0.1,
    extend_line = 0.03
  ) +
  
# expand y-axis so the brackets don't overlap with labels
  scale_y_continuous(expand = expansion(mult = c(0.2, .2))) +
  
# theme and titles
  patchclampplotteR_theme() +
  labs(x = NULL, y = "PPR", title = NULL) +
  theme(legend.position = "none")  # remove legend

PPR_plot
```

### thesis baseline naive and acute only
```{r}
# specific group order
group_order <- c("naive", "acute")

# colours for groups
light_group_colors <- c(
  "naive" = "#f5e0b3",
  "acute" = "#f19cac"
)

group_colors <- c(
  "naive" = "#ecc479",
  "acute" = "#eb647e"
)


# plot baseline PPR for female groups
female_acute_baseline_group_PPR_plot <- female_baseline_PPR_df %>%
  filter(group %in% group_order) %>%
  mutate(group = factor(group, levels = group_order)) %>%
  ggplot(aes(x = group, y = mean_PPR_cell)) +

# boxes
  geom_boxplot(aes(fill = group), alpha = 0.6,
               outlier.shape = NA, width = 0.5, show.legend = FALSE,
               color = "black") +

# individual cells as dots (sina plot)
  geom_sina(aes(color = group), max_width = 0.2,
            shape = 16, size = 2, show.legend = FALSE) +

# axis labels
  labs(x = NULL, y = "Baseline Paired Pulse Ratio") +

# group color mapping for boxplot and dots
  scale_fill_manual(values = light_group_colors) +
  scale_color_manual(values = group_colors) +
  
# significance bracket
  geom_signif(
    comparisons = list(c("naive", "acute")),
    map_signif_level = TRUE,
    annotations = "ns", 
    y_position = max(female_baseline_PPR_df$mean_PPR_cell)*1.05,
    tip_length = 0.02,
    textsize = 5
  ) +

  # x-axis labels
  scale_x_discrete(labels = c("naive" = "Naive", 
                              "acute" = "Acute")) +
  # y-axis
    scale_y_continuous(limits = c(0, 3), expand = expansion(mult = c(0, 0.05))) +

  patchclampplotteR_theme() +
  theme(legend.position = "none") 

  
female_acute_baseline_group_PPR_plot

# ggsave(female_acute_baseline_group_PPR_plot, path = here("Figures"), file = "female_acute_baseline_group_PPR_plot.png", width = 7, height = 5, units = "in", dpi = 300)
```

### PPR baseline visualization
```{r}
# specific group order
group_order <- c("naive", "acute", "AM251", "repeated", "cort")

# colours for groups
light_group_colors <- c(
  "naive" = "#f5e0b3",
  "acute" = "#f19cac",
  "AM251" = "#FFADFF",
  "repeated" = "#6497b1",
  "cort" = "#93c47d"
)

group_colors <- c(
  "naive" = "#ecc479",
  "acute" = "#eb647e",
  "AM251" = "#c11c84",
  "repeated" = "#005b96",
  "cort" = "#6aa84f"
)


# plot baseline PPR for female groups
female_baseline_group_PPR_plot <- female_baseline_PPR_df %>%
  mutate(group = factor(group, levels = group_order)) %>%
  ggplot(aes(x = group, y = mean_PPR_cell)) +

# boxes
  geom_boxplot(aes(fill = group), alpha = 0.6,
               outlier.shape = NA, width = 0.5, show.legend = FALSE,
               color = "black") +

# individual cells as dots (sina plot)
  geom_sina(aes(color = group), max_width = 0.2,
            shape = 16, size = 2, show.legend = FALSE) +

# axis labels
  labs(x = NULL, y = "Baseline Paired Pulse Ratio") +

# group color mapping for boxplot and dots
  scale_fill_manual(values = light_group_colors) +
  scale_color_manual(values = group_colors) +

  # x-axis labels
  scale_x_discrete(labels = c("naive" = "Naive", 
                              "acute" = "Acute", 
                              "AM251" = "Acute with AM251", 
                              "repeated" = "Repeated",
                              "cort" = "Naive with Corticosterone")) +
  # y-axis
    scale_y_continuous(limits = c(0, 3), expand = expansion(mult = c(0, 0.05))) +

  patchclampplotteR_theme() +
  theme(legend.position = "none") 

  
female_baseline_group_PPR_plot

# ggsave(female_baseline_control_PPR_plot, path = here("Figures"), file = "female_baseline_control_PPR_plot.png", width = 7, height = 5, units = "in", dpi = 300)
```
#### anova
```{r}
# HoV
leveneTest(mean_PPR_cell ~ group, data = female_baseline_PPR_df)
# passed

# anova
female_baseline_PPR_anova <- aov(mean_PPR_cell ~ group, data = female_baseline_PPR_df)
summary(female_baseline_PPR_anova)
# not significant

# assumption of normality
female_baseline_PPR_anova_resid <- residuals(female_baseline_PPR_anova)
shapiro.test(female_baseline_PPR_anova_resid)
qqnorm(female_baseline_PPR_anova_resid)
qqline(female_baseline_PPR_anova_resid, col = "red")
# passed
```


### PPR HFS visualization
```{r}
# specific group order
group_order <- c("naive", "acute", "AM251", "repeated", "cort")

# colours for groups
light_group_colors <- c(
  "naive" = "#f5e0b3",
  "acute" = "#f19cac",
  "AM251" = "#FFADFF",
  "repeated" = "#6497b1",
  "cort" = "#93c47d"
)

group_colors <- c(
  "naive" = "#ecc479",
  "acute" = "#eb647e",
  "AM251" = "#c11c84",
  "repeated" = "#005b96",
  "cort" = "#6aa84f"
)


# plot baseline PPR for female groups
female_HFS_group_PPR_plot <- female_HFS_PPR_df %>%
  mutate(group = factor(group, levels = group_order)) %>%
  ggplot(aes(x = group, y = mean_PPR_cell)) +

# boxes
  geom_boxplot(aes(fill = group), alpha = 0.6,
               outlier.shape = NA, width = 0.5, show.legend = FALSE,
               color = "black") +

# individual cells as dots (sina plot)
  geom_sina(aes(color = group), max_width = 0.2,
            shape = 16, size = 2, show.legend = FALSE) +

# axis labels
  labs(x = NULL, y = "Final Paired Pulse Ratio") +

# group color mapping for boxplot and dots
  scale_fill_manual(values = light_group_colors) +
  scale_color_manual(values = group_colors) +

  # x-axis labels
  scale_x_discrete(labels = c("naive" = "Naive", 
                              "acute" = "Acute", 
                              "AM251" = "Acute with AM251", 
                              "repeated" = "Repeated",
                              "cort" = "Naive with Corticosterone")) +
  # y-axis
    scale_y_continuous(limits = c(0, 3), expand = expansion(mult = c(0, 0.05))) +

  patchclampplotteR_theme() +
  theme(legend.position = "none") 

  
female_HFS_group_PPR_plot

# ggsave(female_baseline_control_PPR_plot, path = here("Figures"), file = "female_baseline_control_PPR_plot.png", width = 7, height = 5, units = "in", dpi = 300)
```
#### anova
```{r}
# HoV
leveneTest(mean_PPR_cell ~ group, data = female_HFS_PPR_df)
# passed

# anova
female_HFS_PPR_anova <- aov(mean_PPR_cell ~ group, data = female_HFS_PPR_df)
summary(female_HFS_PPR_anova)
# not significant

# assumption of normality
female_HFS_PPR_anova_resid <- residuals(female_HFS_PPR_anova)
shapiro.test(female_HFS_PPR_anova_resid)
qqnorm(female_HFS_PPR_anova_resid)
qqline(female_HFS_PPR_anova_resid, col = "red")
# passed
```



## AP Frequency
AP Frequencies for Multiple Treatments
```{r}
plot_AP_frequencies_multiple_treatments(
  data = AP_count_data,
  include_all_treatments = "no",
  list_of_treatments = c("Control", "AM251"),
  plot_category = 2,
  included_sexes = "female",
  treatment_colour_theme = my_theme_colours
)
```

#### Mine 
```{r}
# data prep: adding group column
AP_freq_df <- AP_count_data %>%
  mutate(group = case_when(
    sex == "Female" & category == 1 & treatment == "Control" ~ "naive",
    sex == "Female" & category == 2 & treatment == "Control" ~ "acute",
    sex == "Female" & category == 2 & treatment == "AM251" ~ "AM251",
    sex == "Female" & category == 3 & treatment == "Control" ~ "repeated",
    sex == "Female" & category == 1 & treatment == "Cort" ~ "cort",
  )) %>%
  mutate(group = factor(group, levels = c("naive", "acute", "AM251", "repeated", "cort")))

# letter and state need to be factors
AP_freq_df$state <- factor(AP_freq_df$state)
AP_freq_df$letter <- factor(AP_freq_df$letter)
AP_freq_df$sweep <- factor(AP_freq_df$sweep)

# baseline only
female_baseline_AP_freq_df <- AP_freq_df %>%
  filter(state == "Baseline")
```

```{r}
# eyeball interaction plot

library(sciplot)
AP_freq_df$state <- factor(AP_freq_df$state, levels=c("Baseline", "HFS")) # telling it what order
lineplot.CI(x.factor=state, response=AP_frequency, group=group, xlab="State", ylab="AP Frequency (Hz)", data=AP_freq_df) 
```

```{r}
library(nlme)
# starting it off with imposed compound symmetry (assumes sphericity)
AP_freq_model.cs = lme(AP_frequency ~ group*state, data = AP_freq_df, random = ~1|letter, correlation = corCompSymm(form = ~1|letter)) 
anova(AP_freq_model.cs) 


df_female_AP_freq_naive <- AP_freq_df %>% filter(group == "naive")
df_female_AP_freq_acute <- AP_freq_df %>% filter(group == "acute")
df_female_AP_freq_AM251 <- AP_freq_df %>% filter(group == "AM251")
df_female_AP_freq_repeated <- AP_freq_df %>% filter(group == "repeated")

# naive
naive_AP_freq_model.cs <- lme(
  AP_frequency ~ state,
  random = ~1 | letter,
  data = df_female_AP_freq_naive,
  correlation = corCompSymm(form = ~1|letter)
)
anova(naive_AP_freq_model.cs)
# no effect of state on naive AP frequency

# acute
acute_AP_freq_model.cs <- lme(
  AP_frequency ~ state,
  random = ~1 | letter,
  data = df_female_AP_freq_acute,
  correlation = corCompSymm(form = ~1|letter)
)
anova(acute_AP_freq_model.cs)
# effect of state on AP frequency

# am251
am251_AP_freq_model.cs <- lme(
  AP_frequency ~ state,
  random = ~1 | letter,
  data = df_female_AP_freq_AM251,
  correlation = corCompSymm(form = ~1|letter)
)
anova(am251_AP_freq_model.cs)
# no effect of state on AP frequency

# repeated
repeated_AP_freq_model.cs <- lme(
  AP_frequency ~ state,
  random = ~1 | letter,
  data = df_female_AP_freq_repeated,
  correlation = corCompSymm(form = ~1|letter)
)
anova(repeated_AP_freq_model.cs)
# no effect of state on AP frequency
```
```{r, fig.width = 12, fig.height = 10}
library(sjPlot) 
plot_grid(plot_model(AP_freq_model.cs, type = "diag")) 
# going with it because log was also horrible, sqrt, negative binomial still had significant deviation
```

### Christelinda's
```{r eval=FALSE}
plot_AP_frequencies_single_treatment(
  data = AP_count_data, # 
  plot_treatment = "Control",
  plot_category = 2, # Acute with only picro
  included_sexes = "female",
  baseline_label = "Baseline",
  hormone_added = "HFS",
  significance_display_method = "p-values", # could be "p-values" or "stars"
  treatment_colour_theme = my_theme_colours,
  large_axis_text = "no",
  test_type = "wilcox.test", # need to test assumptions
  theme_options = my_theme_options,
  save_plot_png = "no"
)
```
```{r eval=FALSE}
plot_AP_frequencies_single_treatment(
  data = AP_count_data, 
  plot_treatment = "AM251",
  plot_category = 2,
  included_sexes = "female",
  baseline_label = "Baseline",
  hormone_added = "HFS",
  significance_display_method = "p-values", # could be "p-values" or "stars"
  treatment_colour_theme = my_theme_colours,
  large_axis_text = "no",
  test_type = "wilcox.test", # need to test assumptions, can be "wilcox.test", "t.test", or "none"
  theme_options = my_theme_options,
  save_plot_png = "no"
)
```
```{r eval=FALSE}
plot_AP_frequencies_single_treatment(
  data = AP_count_data, 
  plot_treatment = "Control",
  plot_category = 3,
  included_sexes = "female",
  baseline_label = "Baseline",
  hormone_added = "HFS",
  significance_display_method = "p-values", # could be "p-values" or "stars"
  treatment_colour_theme = my_theme_colours,
  large_axis_text = "no",
  test_type = "wilcox.test", # need to test assumptions, can be "wilcox.test", "t.test", or "none"
  theme_options = my_theme_options,
  save_plot_png = "no"
)
```
```{r eval=FALSE}
plot_AP_frequencies_single_treatment(
  data = AP_count_data, # 
  plot_treatment = "Cort",
  plot_category = 1, 
  included_sexes = "female",
  baseline_label = "Baseline",
  hormone_added = "HFS",
  significance_display_method = "p-values", # could be "p-values" or "stars"
  treatment_colour_theme = my_theme_colours,
  large_axis_text = "no",
  test_type = "wilcox.test", # need to test assumptions
  theme_options = my_theme_options,
  save_plot_png = "no"
)
```
```{r eval=FALSE}
plot_AP_frequencies_single_treatment(
  data = AP_count_data,  
  plot_treatment = "Control",
  plot_category = 1, 
  included_sexes = "female",
  baseline_label = "Baseline",
  hormone_added = "HFS",
  significance_display_method = "stars", # could be "p-values" or "stars"
  treatment_colour_theme = my_theme_colours,
  large_axis_text = "no",
  test_type = "wilcox.test", # need to test assumptions
  theme_options = my_theme_options,
  save_plot_png = "yes"
)
```




## AP Amplitude
### Mine

#### Naive Females 
```{r}
# data
naive_females <- c("RMN3", "RMN4", "RMN5") # all fire some APs
naive_female_AP_data <- subset(AP_data, letter %in% naive_females)


naive_female_baseline_AP_data <- subset(naive_female_AP_data, state == "Baseline")$peak_amplitude
naive_female_HFS_AP_data <- subset(naive_female_AP_data, state == "HFS")$peak_amplitude

naive_female_AP_data_diff <- naive_female_baseline_AP_data-naive_female_HFS_AP_data


# normality
qqnorm(naive_female_AP_data_diff) 
qqline(naive_female_AP_data_diff) 
shapiro.test(naive_female_AP_data_diff) # normality test of difference variable
# normal (when the cells with 0 amplitude are removed)

t.test(naive_female_baseline_AP_data, naive_female_HFS_AP_data, paired = TRUE)
```
```{r}
# visualize

naive_female_AP_plot <- naive_female_AP_data[, c("letter", "state", "peak_amplitude")]

# plot
naive_female_AP_plot <- naive_female_AP_data %>%
  ggplot(aes(x = state, y = peak_amplitude, group = letter)) +
  
# individual cells
  geom_point(aes(state), size = 1, colour = "lightgrey") + # or #f19cac
  geom_line(aes(group = letter), colour = "lightgrey", alpha = 0.9) +
  
# mean point
  stat_summary(aes(group = 1),
               fun.data = mean_se,
               geom = "line",
               colour = "#ecc479",
               linewidth = 1.2) +
  
  stat_summary(aes(group = 1),
    fun.data = mean_se,
    geom = "point",
    colour = "#ecc479",
    size = 2.5
  ) + 

# bracket
  geom_signif(
    comparisons = list(c("Baseline", "HFS")),
    map_signif_level = TRUE,  
    annotations = "ns",  
    vjust = -0.3,
    textsize = 5,# 5 when ns, 7 when *s
    size = 0.5,
    margin_top = 0.1,
    extend_line = 0.03
  ) +

# y-axis
  scale_y_continuous(limits = c(0, 100)) +
  
# theme and titles
  patchclampplotteR_theme() +
  labs(x = NULL, y = "Peak Amplitude (pA)", title = NULL) +
  theme(legend.position = "none")  # remove legend

naive_female_AP_plot

# ggsave(naive_female_AP_plot, path = here("Figures"), file = "naive_female_AP_plot.png", width = 7, height = 5, units = "in", dpi = 300)
```


#### Acute Females 
```{r}
# data
acute_females <- c("RMA1", "RMA3", "RMA8", "RMA9", "RMA10") # remove RMA2, RMA4, RMA6 because they have a 0 value
acute_female_AP_data <- subset(AP_data, letter %in% acute_females)


acute_female_baseline_AP_data <- subset(acute_female_AP_data, state == "Baseline")$peak_amplitude
acute_female_HFS_AP_data <- subset(acute_female_AP_data, state == "HFS")$peak_amplitude

acute_female_AP_data_diff <- acute_female_baseline_AP_data-acute_female_HFS_AP_data


# normality
qqnorm(acute_female_AP_data_diff) 
qqline(acute_female_AP_data_diff) 
shapiro.test(acute_female_AP_data_diff) # normality test of difference variable
# normal (when the cells with 0 amplitude are removed)

t.test(acute_female_baseline_AP_data, acute_female_HFS_AP_data, paired = TRUE)
```
```{r}
# visualize

acute_female_AP_plot <- acute_female_AP_data[, c("letter", "state", "peak_amplitude")]

# plot
acute_female_AP_plot <- acute_female_AP_data %>%
  ggplot(aes(x = state, y = peak_amplitude, group = letter)) +
  
# individual cells
  geom_point(aes(state), size = 1, colour = "lightgrey") + # or #f19cac
  geom_line(aes(group = letter), colour = "lightgrey", alpha = 0.9) +
  
# mean point
  stat_summary(aes(group = 1),
               fun.data = mean_se,
               geom = "line",
               colour = "#eb647e",
               linewidth = 1.2) +
  
  stat_summary(aes(group = 1),
    fun.data = mean_se,
    geom = "point",
    colour = "#eb647e",
    size = 2.5
  ) + 

# bracket
  geom_signif(
    comparisons = list(c("Baseline", "HFS")),
    map_signif_level = TRUE,  
    annotations = "*",  
    vjust = -0.3,
    textsize = 7,
    size = 0.5,
    margin_top = 0.1,
    extend_line = 0.03
  ) +

# y-axis
  scale_y_continuous(limits = c(0, 100)) +
  
# theme and titles
  patchclampplotteR_theme() +
  labs(x = NULL, y = "Peak Amplitude (pA)", title = NULL) +
  theme(legend.position = "none")  # remove legend

acute_female_AP_plot

# ggsave(acute_female_AP_plot, path = here("Figures"), file = "acute_female_AP_plot.png", width = 7, height = 5, units = "in", dpi = 300)
```

#### AM251 Females 
```{r}
# data
AM251_females <- c("RMA2A", "RMA3A", "RMA4A", "RMA5A", "RMA6A", "RMA10A") # remove RMA1A, RMA9A because they have a 0 value
AM251_female_AP_data <- subset(AP_data, letter %in% AM251_females)


AM251_female_baseline_AP_data <- subset(AM251_female_AP_data, state == "Baseline")$peak_amplitude
AM251_female_HFS_AP_data <- subset(AM251_female_AP_data, state == "HFS")$peak_amplitude

AM251_female_AP_data_diff <- AM251_female_baseline_AP_data-AM251_female_HFS_AP_data


# normality
qqnorm(AM251_female_AP_data_diff) 
qqline(AM251_female_AP_data_diff) 
shapiro.test(AM251_female_AP_data_diff) 
# normal (when the cells with 0 amplitude are removed)

t.test(AM251_female_baseline_AP_data, AM251_female_HFS_AP_data, paired = TRUE)
```

```{r}
# visualize

AM251_female_AP_data_plot <- AM251_female_AP_data[, c("letter", "state", "peak_amplitude")]


# plot
AM251_female_AP_plot <- AM251_female_AP_data %>%
  ggplot(aes(x = state, y = peak_amplitude, group = letter)) +
  
# individual cells
  geom_point(aes(state), size = 1, colour = "lightgrey") + 
  geom_line(aes(group = letter), colour = "lightgrey", alpha = 0.9) +
  
# mean point
  stat_summary(aes(group = 1),
               fun.data = mean_se,
               geom = "line",
               colour = "#C11C84",
               linewidth = 1.2) +
  
  stat_summary(aes(group = 1),
    fun.data = mean_se,
    geom = "point",
    colour = "#C11C84",
    size = 2.5
  ) + 

# bracket
  geom_signif(
    comparisons = list(c("Baseline", "HFS")),
    map_signif_level = TRUE,  
    annotations = "ns",  
    vjust = -0.3,
    textsize = 5,
    size = 0.5,
    margin_top = 0.1,
    extend_line = 0.03
  ) +

# y-axis
  scale_y_continuous(limits = c(0, 100)) +
  
# theme and titles
  patchclampplotteR_theme() +
  labs(x = NULL, y = "Peak Amplitude (pA)", title = NULL) +
  theme(legend.position = "none")  # remove legend

AM251_female_AP_plot

# ggsave(AM251_female_AP_plot, path = here("Figures"), file = "AM251_female_AP_plot.png", width = 7, height = 5, units = "in", dpi = 300)
```

#### Repeated Females 
```{r}
# data
repeated_females <- c("RMR1", "RMR2", "RMR3", "RMR4", "RMR5", "RMR6", "RMR8", "RMR9", "RMR10") # none have 0 values
repeated_female_AP_data <- subset(AP_data, letter %in% repeated_females)


repeated_female_baseline_AP_data <- subset(repeated_female_AP_data, state == "Baseline")$peak_amplitude
repeated_female_HFS_AP_data <- subset(repeated_female_AP_data, state == "HFS")$peak_amplitude


# difference needed for PAIRED t-test
repeated_female_AP_data_diff <- repeated_female_baseline_AP_data-repeated_female_HFS_AP_data


# normality
qqnorm(repeated_female_AP_data_diff) 
qqline(repeated_female_AP_data_diff) 
shapiro.test(repeated_female_AP_data_diff) 
# normal (when the cells with 0 amplitude are removed)

t.test(repeated_female_baseline_AP_data, repeated_female_HFS_AP_data, paired = TRUE)
```

```{r}
# visualize

repeated_female_AP_data_plot <- repeated_female_AP_data[, c("letter", "state", "peak_amplitude")]

# plot
repeated_female_AP_plot <- repeated_female_AP_data %>%
  ggplot(aes(x = state, y = peak_amplitude, group = letter)) +
  
# individual cells
  geom_point(aes(state), size = 1, colour = "lightgrey") + 
  geom_line(aes(group = letter), colour = "lightgrey", alpha = 0.9) +
  
# mean point
  stat_summary(aes(group = 1),
               fun.data = mean_se,
               geom = "line",
               colour = "#005b96",
               linewidth = 1.2) +
  
  stat_summary(aes(group = 1),
    fun.data = mean_se,
    geom = "point",
    colour = "#005b96",
    size = 2.5
  ) + 

# bracket
  geom_signif(
    comparisons = list(c("Baseline", "HFS")),
    map_signif_level = TRUE,  
    annotations = "**",  
    vjust = -0.3,
    textsize = 7,
    size = 0.5,
    margin_top = 0.1,
    extend_line = 0.03
  ) +

# y-axis
  scale_y_continuous(limits = c(0, 100)) +
  
# theme and titles
  patchclampplotteR_theme() +
  labs(x = NULL, y = "Peak Amplitude (pA)", title = NULL) +
  theme(legend.position = "none")  # remove legend

repeated_female_AP_plot

# ggsave(repeated_female_AP_plot, path = here("Figures"), file = "repeated_female_AP_plot.png", width = 7, height = 5, units = "in", dpi = 300)
```

#### Cort Females 
```{r}
# data
cort_females <- c("RMC1", "RMC2", "RMC4", "RMC5", "RMC6", "RMC7") # remove RMC3 because they have a 0 value
cort_female_AP_data <- subset(AP_data, letter %in% cort_females)


cort_female_baseline_AP_data <- subset(cort_female_AP_data, state == "Baseline")$peak_amplitude
cort_female_HFS_AP_data <- subset(cort_female_AP_data, state == "HFS")$peak_amplitude

cort_female_AP_data_diff <- cort_female_baseline_AP_data-cort_female_HFS_AP_data


# normality
qqnorm(cort_female_AP_data_diff) 
qqline(cort_female_AP_data_diff) 
shapiro.test(cort_female_AP_data_diff) # normality test of difference variable
# normal (when the cells with 0 amplitude are removed)

t.test(cort_female_baseline_AP_data, cort_female_HFS_AP_data, paired = TRUE)
```

```{r}
# visualize

cort_female_AP_plot <- cort_female_AP_data[, c("letter", "state", "peak_amplitude")]

# plot
cort_female_AP_plot <- cort_female_AP_data %>%
  ggplot(aes(x = state, y = peak_amplitude, group = letter)) +
  
# individual cells
  geom_point(aes(state), size = 1, colour = "lightgrey") + # or #f19cac
  geom_line(aes(group = letter), colour = "lightgrey", alpha = 0.9) +
  
# mean point
  stat_summary(aes(group = 1),
               fun.data = mean_se,
               geom = "line",
               colour = "#6aa84f",
               linewidth = 1.2) +
  
  stat_summary(aes(group = 1),
    fun.data = mean_se,
    geom = "point",
    colour = "#6aa84f",
    size = 2.5
  ) + 

# bracket
  geom_signif(
    comparisons = list(c("Baseline", "HFS")),
    map_signif_level = TRUE,  
    annotations = "ns",  
    vjust = -0.3,
    textsize = 5,
    size = 0.5,
    margin_top = 0.1,
    extend_line = 0.03
  ) +

# y-axis
  scale_y_continuous(limits = c(0, 100)) +
  
# theme and titles
  patchclampplotteR_theme() +
  labs(x = NULL, y = "Peak Amplitude (pA)", title = NULL) +
  theme(legend.position = "none")  # remove legend

cort_female_AP_plot

# ggsave(acute_female_AP_plot, path = here("Figures"), file = "acute_female_AP_plot.png", width = 7, height = 5, units = "in", dpi = 300)
```



#### ANOVA
```{r}
# making it into one data frame
AP_amp_anova_data <- subset(AP_data, 
                     letter %in% c(acute_females,
                                   AM251_females,
                                   repeated_females,
                                   cort_females))

# treated as factors
AP_amp_anova_data$group <- factor(AP_amp_anova_data$group)
AP_amp_anova_data$state <- factor(AP_amp_anova_data$state)
AP_amp_anova_data$letter <- factor(AP_amp_anova_data$letter)
```

```{r}
# visualize

AP_amp_anova_plot <- ggplot(AP_amp_anova_data, aes(x = group, y = peak_amplitude, fill = group)) +
  geom_boxplot(alpha = 0.6, outlier.shape = NA) +
  geom_jitter(aes(color = group), width = 0.15, size = 2, alpha = 0.8) +
  facet_wrap(~ state) +
  patchclampplotteR_theme() +
  labs(y = "AP Peak Amplitude (pA)", x = NULL) +
  theme(legend.position = "none") +
  scale_fill_manual(values = c("acute" = "#f19cac",
                               "AM251" = "#ffadff",
                               "repeated" = "#6497b1",
                               "cort" = "#93c47d")) +
  
  scale_color_manual(values = c("acute" = "#eb647e", 
                                "AM251" = "#c11c84",
                                "repeated" = "#005b96",
                                "cort" = "#6aa84f")) 

AP_amp_anova_plot
```

```{r}
# HoV

leveneTest(AP_amp_anova_data$peak_amplitude, interaction(AP_amp_anova_data$state, AP_amp_anova_data$group))
# no evidence to reject the null that variances are homogeneous
```

```{r}
# running anova

AP_amp_anova <- ezANOVA(
  data = AP_amp_anova_data,
  dv = peak_amplitude,
  wid = letter,
  within = state,
  between = group,
  type = 3,
  detailed = T,
  return_aov = T
)

print(AP_amp_anova)
```

```{r}
# normality of residuals

# linear model 
AP_amp_anova_lm_model <- lm(peak_amplitude ~ group * state, data = AP_amp_anova_data)

# extract residuals
resid.AP_amp_anova <- residuals(AP_amp_anova_lm_model)

# Q-Q plot
qqnorm(resid.AP_amp_anova)
qqline(resid.AP_amp_anova)

# Shapiro-Wilk test
shapiro.test(resid.AP_amp_anova)

# log transforming actually made it worse so gonna stick with slight devition form normality cause its fine
```


### Christelinda's
```{r eval=FALSE}
plot_AP_comparison(
  AP_data,
  plot_treatment = "Control",
  plot_category = 2,
  included_sexes = "female",
  facet_by_sex = "no",
  left_sex = "Female",
  y_variable = "peak_amplitude",
  y_axis_title = "Peak Amplitude (pA)",
  theme_options = my_theme_options,
  baseline_label = "Baseline",
  test_type = "wilcox.test",
  post_hormone_label = "HFS",
  treatment_colour_theme = my_theme_colours,
  save_plot_png = "no"
)
```

AP Amplitude: Acute Females with AM251
```{r eval=FALSE}
plot_AP_comparison(
  AP_data,
  plot_treatment = "AM251",
  plot_category = 2,
  included_sexes = "female",
  facet_by_sex = "no",
  left_sex = "Female",
  y_variable = "peak_amplitude",
  y_axis_title = "Peak Amplitude (pA)",
  theme_options = my_theme_options,
  baseline_label = "Baseline",
  test_type = "wilcox.test",
  post_hormone_label = "HFS",
  treatment_colour_theme = my_theme_colours,
  save_plot_png = "no"
)
```

AP Amplitude: Repeated Females 
```{r eval=FALSE}
plot_AP_comparison(
  AP_data,
  plot_treatment = "Control",
  plot_category = 3,
  included_sexes = "female",
  facet_by_sex = "no",
  left_sex = "Female",
  y_variable = "peak_amplitude",
  y_axis_title = "Peak Amplitude (pA)",
  theme_options = my_theme_options,
  baseline_label = "Baseline",
  test_type = "wilcox.test",
  post_hormone_label = "HFS",
  treatment_colour_theme = my_theme_colours,
  save_plot_png = "no"
)
```

## Variance Analysis
Creating Variance dataset for variance analysis (category 2)
```{r}
variance_2_df <- make_variance_data(
  data = summary_eEPSC_df$summary_data,
  include_all_categories = "no",
  list_of_categories = 2,
  include_all_treatments = "yes",
  list_of_treatments = NULL,
  baseline_interval = "t0to5",
  post_hormone_interval = "t25to30",
  treatment_colour_theme = my_theme_colours,
  save_output_as_RDS = "no"
)

variance_2_df

# VARIANCE

# The strength of synaptic transmission onto a neuron depends on the number of functional vesicle release sites (N), the probability of vesicle release (Pr), and the quantal size (Q)

# 1/CV2 depends on N and Pr, but not on Q
# VMR depends on Pr and Q, but not on N
```

```{r}
variance_1_df <- make_variance_data(
  data = summary_eEPSC_df$summary_data,
  include_all_categories = "no",
  list_of_categories = 1,
  include_all_treatments = "yes",
  list_of_treatments = NULL,
  baseline_interval = "t0to5",
  post_hormone_interval = "t25to30",
  treatment_colour_theme = my_theme_colours,
  save_output_as_RDS = "no"
)

variance_1_df
```

```{r}
variance_3_df <- make_variance_data(
  data = summary_eEPSC_df$summary_data,
  include_all_categories = "no",
  list_of_categories = 3,
  include_all_treatments = "yes",
  list_of_treatments = NULL,
  baseline_interval = "t0to5",
  post_hormone_interval = "t25to30",
  treatment_colour_theme = my_theme_colours,
  save_output_as_RDS = "no"
)

variance_3_df
```


Variance Comparisons for ACUTE (Control)
```{r eval=FALSE}
cv_comparison_control_plot <- plot_variance_comparison_data(
  data = variance_2_df,
  plot_category = 2, # acute
  plot_treatment = "Control", # only picro
  variance_measure = "cv",
  included_sexes = "both",
  facet_by_sex = "yes",
  left_sex = "Female",
  baseline_interval = "t0to5",
  post_hormone_interval = "t25to30",
  post_hormone_label = "HFS",
  test_type = "wilcox.test",
  large_axis_text = "no",
  treatment_colour_theme = my_theme_colours,
  theme_options = my_theme_options,
  save_plot_png = "no"
)

vmr_comparison_control_plot <- plot_variance_comparison_data(
  data = variance_2_df,
  plot_category = 2, # acute
  plot_treatment = "Control", # only picro
  variance_measure = "VMR",
  included_sexes = "both",
  facet_by_sex = "yes",
  left_sex = "Female",
  baseline_interval = "t0to5",
  post_hormone_interval = "t25to30",
  post_hormone_label = "HFS",
  test_type = "wilcox.test",
  large_axis_text = "no",
  treatment_colour_theme = my_theme_colours,
  theme_options = my_theme_options,
  save_plot_png = "no"
)

cv_comparison_control_plot
vmr_comparison_control_plot

# With the almost significant decrease in VMR in males: 
# if it was significant, since there is no change in 1/CV2, it would be a presynaptic change in Q
```
Variance Comparisons for ACUTE (AM251)
```{r eval=FALSE}
cv_comparison_AM251_plot <- plot_variance_comparison_data(
  data = variance_2_df,
  plot_category = 2, # acute
  plot_treatment = "AM251",
  variance_measure = "cv",
  included_sexes = "female", # no male data
  facet_by_sex = "no",
  left_sex = "Female",
  baseline_interval = "t0to5",
  post_hormone_interval = "t25to30",
  post_hormone_label = "HFS",
  test_type = "wilcox.test",
  large_axis_text = "no",
  treatment_colour_theme = my_theme_colours,
  theme_options = my_theme_options,
  save_plot_png = "no"
)

vmr_comparison_AM251_plot <- plot_variance_comparison_data(
  data = variance_2_df,
  plot_category = 2, # acute
  plot_treatment = "AM251",
  variance_measure = "VMR",
  included_sexes = "female", # no male data
  facet_by_sex = "no",
  left_sex = "Female",
  baseline_interval = "t0to5",
  post_hormone_interval = "t25to30",
  post_hormone_label = "HFS",
  test_type = "wilcox.test",
  large_axis_text = "no",
  treatment_colour_theme = my_theme_colours,
  theme_options = my_theme_options,
  save_plot_png = "no"
)

cv_comparison_AM251_plot
vmr_comparison_AM251_plot

# With the almost significant decrease in VMR in males: 
# if it was significant, since there is no change in 1/CV2, it would be a presynaptic change in Q
```
Variance Comparisons for REPEATED (Control)
```{r eval=FALSE}
cv_comparison_repeated_plot <- plot_variance_comparison_data(
  data = variance_3_df,
  plot_category = 3, # repeated
  plot_treatment = "Control",
  variance_measure = "cv",
  included_sexes = "both",
  facet_by_sex = "yes",
  left_sex = "Female",
  baseline_interval = "t0to5",
  post_hormone_interval = "t25to30",
  post_hormone_label = "HFS",
  test_type = "wilcox.test",
  large_axis_text = "no",
  treatment_colour_theme = my_theme_colours,
  theme_options = my_theme_options,
  save_plot_png = "no"
)

vmr_comparison_repeated_plot <- plot_variance_comparison_data(
  data = variance_3_df,
  plot_category = 3, # repeated
  plot_treatment = "Control",
  variance_measure = "VMR",
  included_sexes = "both", 
  facet_by_sex = "yes",
  left_sex = "Female",
  baseline_interval = "t0to5",
  post_hormone_interval = "t25to30",
  post_hormone_label = "HFS",
  test_type = "wilcox.test",
  large_axis_text = "no",
  treatment_colour_theme = my_theme_colours,
  theme_options = my_theme_options,
  save_plot_png = "no"
)

cv_comparison_repeated_plot
vmr_comparison_repeated_plot

# RMR6 VMR after is the suddenly high one 

# With the significant decrease in VMR in repeated males, since there is no change in 1/CV2, it is a presynaptic change in Q
```

Variance Comparisons for NAIVE
```{r eval=FALSE}
cv_comparison_naive_plot <- plot_variance_comparison_data(
  data = variance_1_df,
  plot_category = 1, 
  plot_treatment = "Control",
  variance_measure = "cv",
  included_sexes = "both",
  facet_by_sex = "yes",
  left_sex = "Female",
  baseline_interval = "t0to5",
  post_hormone_interval = "t25to30",
  post_hormone_label = "HFS",
  test_type = "wilcox.test",
  large_axis_text = "no",
  treatment_colour_theme = my_theme_colours,
  theme_options = my_theme_options
)

vmr_comparison_naive_plot <- plot_variance_comparison_data(
  data = variance_1_df,
  plot_category = 1, 
  plot_treatment = "Control",
  variance_measure = "VMR",
  included_sexes = "both",
  facet_by_sex = "yes",
  left_sex = "Female",
  baseline_interval = "t0to5",
  post_hormone_interval = "t25to30",
  post_hormone_label = "HFS",
  test_type = "wilcox.test",
  large_axis_text = "no",
  treatment_colour_theme = my_theme_colours,
  theme_options = my_theme_options
)

cv_comparison_naive_plot
vmr_comparison_naive_plot
```

```{r eval=FALSE}
cv_comparison_cort_plot <- plot_variance_comparison_data(
  data = variance_1_df,
  plot_category = 1, 
  plot_treatment = "Cort",
  variance_measure = "cv",
  included_sexes = "both",
  facet_by_sex = "yes",
  left_sex = "Female",
  baseline_interval = "t0to5",
  post_hormone_interval = "t25to30",
  post_hormone_label = "HFS",
  test_type = "wilcox.test",
  large_axis_text = "no",
  treatment_colour_theme = my_theme_colours,
  theme_options = my_theme_options
)

vmr_comparison_cort_plot <- plot_variance_comparison_data(
  data = variance_1_df,
  plot_category = 1, 
  plot_treatment = "Cort",
  variance_measure = "VMR",
  included_sexes = "both",
  facet_by_sex = "yes",
  left_sex = "Female",
  baseline_interval = "t0to5",
  post_hormone_interval = "t25to30",
  post_hormone_label = "HFS",
  test_type = "wilcox.test",
  large_axis_text = "no",
  treatment_colour_theme = my_theme_colours,
  theme_options = my_theme_options
)

cv_comparison_cort_plot
vmr_comparison_cort_plot
```

### Thesis
```{r}
variance_df_list <- list(variance_1_df, variance_2_df, variance_3_df) 

variance_df <- bind_rows(variance_df_list) %>% ungroup()

# adding group column
variance_df <- variance_df %>%
  mutate(
    group = case_when(
      category == 1 & treatment == "Control" ~ "naive",
      category == 2 & treatment == "Control" ~ "acute",
      category == 2 & treatment == "AM251"   ~ "AM251",
      category == 3 & treatment == "Control" ~ "repeated",
       category == 1 & treatment == "Cort" ~ "cort",
    )
  )

# renaming to HFS
variance_df <- variance_df %>%
  mutate(state = recode_factor(state,
                        "Post-modification" = "HFS"))

# removing unpaired neurons (that are only baselines)
variance_df <- variance_df %>%
  group_by(group, letter) %>%
  filter(n_distinct(state) == 2) %>%  
  ungroup()

# converting to wide format
wide_variance_df <- variance_df %>%
  select(group, sex, letter, state, cv_inverse_square) %>%
  pivot_wider(names_from = state, values_from = cv_inverse_square)


# adding difference column (for cv_inverse_square) to test for normality
wide_variance_df <- wide_variance_df %>%
  mutate(diff = HFS - Baseline)

# filtering for only females
wide_female_variance_df <- wide_variance_df %>%
  filter(sex == "Female")


# testing for normality
shapiro.test(wide_female_variance_df$diff[wide_female_variance_df$group == "naive"])
qqnorm(wide_female_variance_df$diff[wide_female_variance_df$group == "naive"])
qqline(wide_female_variance_df$diff[wide_female_variance_df$group == "naive"])

shapiro.test(wide_female_variance_df$diff[wide_female_variance_df$group == "acute"])
qqnorm(wide_female_variance_df$diff[wide_female_variance_df$group == "acute"])
qqline(wide_female_variance_df$diff[wide_female_variance_df$group == "acute"])

shapiro.test(wide_female_variance_df$diff[wide_female_variance_df$group == "AM251"])
qqnorm(wide_female_variance_df$diff[wide_female_variance_df$group == "AM251"])
qqline(wide_female_variance_df$diff[wide_female_variance_df$group == "AM251"])

shapiro.test(wide_female_variance_df$diff[wide_female_variance_df$group == "repeated"]) # shaprio borderline (0.04591) but I say it looks good enough
qqnorm(wide_female_variance_df$diff[wide_female_variance_df$group == "repeated"])
qqline(wide_female_variance_df$diff[wide_female_variance_df$group == "repeated"])


# running the t-tests
# naive 
t.test(wide_female_variance_df$HFS[wide_female_variance_df$group == "naive"],
            wide_female_variance_df$Baseline[wide_female_variance_df$group == "naive"],
            paired = TRUE)

# acute
t.test(wide_female_variance_df$HFS[wide_female_variance_df$group == "acute"],
       wide_female_variance_df$Baseline[wide_female_variance_df$group == "acute"],
       paired = TRUE)

# AM251 
t.test(wide_female_variance_df$HFS[wide_female_variance_df$group == "AM251"],
       wide_female_variance_df$Baseline[wide_female_variance_df$group == "AM251"],
       paired = TRUE)

# repeated 
t.test(wide_female_variance_df$HFS[wide_female_variance_df$group == "repeated"],
       wide_female_variance_df$Baseline[wide_female_variance_df$group == "repeated"],
       paired = TRUE)
```

```{r}
naive_female_cv_plot_data <- wide_female_variance_df %>%
  filter(group == "naive") %>%
  pivot_longer(cols = c(Baseline, HFS),
               names_to = "state",
               values_to = "cv_inverse_square")

# plot
naive_female_cv_plot <- ggplot(naive_female_cv_plot_data, aes(x = state, y = cv_inverse_square, group = letter)) +
  
# individual cells
  geom_point(size = 1, colour = "lightgrey") +
  geom_line(colour = "lightgrey", alpha = 0.9) +
  
# mean point
  stat_summary(aes(group = 1), fun.data = mean_se, geom = "line", colour = "#ecc479", linewidth = 1.2) +
  stat_summary(aes(group = 1), fun.data = mean_se, geom = "point", colour = "#ecc479", size = 2.5) +
  
# significance bracket
  geom_signif(
    comparisons = list(c("Baseline", "HFS")),
    map_signif_level = TRUE,
    annotations = "ns", 
    y_position = max(naive_female_cv_plot_data$cv_inverse_square) * 1.05,
    tip_length = 0.02,
    textsize = 5
  ) +
  
# y-axis
  scale_y_continuous(limits = c(0, max(naive_female_cv_plot_data$cv_inverse_square) * 1.2)) +
  
# theme
  patchclampplotteR_theme() +
  labs(x = NULL, y = "1/CV²", title = NULL) +
  theme(legend.position = "none")

naive_female_cv_plot

# ggsave(naive_female_cv_plot, path = here("Figures"), file = "naive_female_cv_plot.png", width = 7, height = 5, units = "in", dpi = 300)
```

```{r}
acute_female_cv_plot_data <- wide_female_variance_df %>%
  filter(group == "acute") %>%
  pivot_longer(cols = c(Baseline, HFS),
               names_to = "state",
               values_to = "cv_inverse_square")

# plot
acute_female_cv_plot <- ggplot(acute_female_cv_plot_data, aes(x = state, y = cv_inverse_square, group = letter)) +
  
# individual cells
  geom_point(size = 1, colour = "lightgrey") +
  geom_line(colour = "lightgrey", alpha = 0.9) +
  
# mean point
  stat_summary(aes(group = 1), fun.data = mean_se, geom = "line", colour = "#eb647e", linewidth = 1.2) +
  stat_summary(aes(group = 1), fun.data = mean_se, geom = "point", colour = "#eb647e", size = 2.5) +
  
# significance bracket
  geom_signif(
    comparisons = list(c("Baseline", "HFS")),
    map_signif_level = TRUE,
    annotations = "ns", 
    y_position = max(acute_female_cv_plot_data$cv_inverse_square) * 1.05,
    tip_length = 0.02,
    textsize = 5
  ) +
  
# y-axis
  scale_y_continuous(limits = c(0, max(acute_female_cv_plot_data$cv_inverse_square) * 1.2)) +
  
# theme
  patchclampplotteR_theme() +
  labs(x = NULL, y = "1/CV²", title = NULL) +
  theme(legend.position = "none")

acute_female_cv_plot

# ggsave(acute_female_cv_plot, path = here("Figures"), file = "acute_female_cv_plot.png", width = 7, height = 5, units = "in", dpi = 300)
```

```{r}
am251_female_cv_plot_data <- wide_female_variance_df %>%
    filter(group == "AM251") %>%
  pivot_longer(cols = c(Baseline, HFS),
               names_to = "state",
               values_to = "cv_inverse_square")

# plot
am251_female_cv_plot <- ggplot(am251_female_cv_plot_data, aes(x = state, y = cv_inverse_square, group = letter)) +
  
# individual cells
  geom_point(size = 1, colour = "lightgrey") +
  geom_line(colour = "lightgrey", alpha = 0.9) +
  
# mean point
  stat_summary(aes(group = 1), fun.data = mean_se, geom = "line", colour = "#C11C84", linewidth = 1.2) +
  stat_summary(aes(group = 1), fun.data = mean_se, geom = "point", colour = "#C11C84", size = 2.5) +
  
# significance bracket
  geom_signif(
    comparisons = list(c("Baseline", "HFS")),
    map_signif_level = TRUE,
    annotations = "ns", 
    y_position = max(am251_female_cv_plot_data$cv_inverse_square) * 1.05,
    tip_length = 0.02,
    textsize = 5
  ) +
  
# y-axis
  scale_y_continuous(limits = c(0, max(am251_female_cv_plot_data$cv_inverse_square) * 1.2)) +
  
# theme
  patchclampplotteR_theme() +
  labs(x = NULL, y = "1/CV²", title = NULL) +
  theme(legend.position = "none")

am251_female_cv_plot

# ggsave(am251_female_cv_plot, path = here("Figures"), file = "am251_female_cv_plot.png", width = 7, height = 5, units = "in", dpi = 300)
```

```{r}
repeated_female_cv_plot_data <- wide_female_variance_df %>%
    filter(group == "AM251") %>%
  pivot_longer(cols = c(Baseline, HFS),
               names_to = "state",
               values_to = "cv_inverse_square")

# plot
repeated_female_cv_plot <- ggplot(repeated_female_cv_plot_data, aes(x = state, y = cv_inverse_square, group = letter)) +
  
# individual cells
  geom_point(size = 1, colour = "lightgrey") +
  geom_line(colour = "lightgrey", alpha = 0.9) +
  
# mean point
  stat_summary(aes(group = 1), fun.data = mean_se, geom = "line", colour = "#005b96", linewidth = 1.2) +
  stat_summary(aes(group = 1), fun.data = mean_se, geom = "point", colour = "#005b96", size = 2.5) +
  
# significance bracket
  geom_signif(
    comparisons = list(c("Baseline", "HFS")),
    map_signif_level = TRUE,
    annotations = "ns", 
    y_position = max(repeated_female_cv_plot_data$cv_inverse_square) * 1.05,
    tip_length = 0.02,
    textsize = 5
  ) +
  
# y-axis
  scale_y_continuous(limits = c(0, max(repeated_female_cv_plot_data$cv_inverse_square) * 1.2)) +
  
# theme
  patchclampplotteR_theme() +
  labs(x = NULL, y = "1/CV²", title = NULL) +
  theme(legend.position = "none")

repeated_female_cv_plot

# ggsave(repeated_female_cv_plot, path = here("Figures"), file = "repeated_female_cv_plot.png", width = 7, height = 5, units = "in", dpi = 300)
```




## ANOVA for Baseline eEPSC
```{r}
# data frame
female_amp_df <- summary_eEPSC_df$percent_change_data %>%
  filter(sex == "Female" & category %in% c(1,2,3) & treatment %in% c("Control","AM251")) %>% 
  mutate(cat_treat = factor(
    interaction(category, treatment),
    levels = c("1.Control", "2.Control", "2.AM251", "3.Control")
  ))

female_amp_df
```

```{r}
# log transform amplitude data
female_amp_df$log_t0to5 <- log(female_amp_df$t0to5)
female_amp_df$log_t25to30 <- log(female_amp_df$t25to30)
```


```{r}
# assumptions

library(car)
leveneTest(t0to5 ~ cat_treat, data = female_amp_df)
# normal variances are homogeneous

leveneTest(log_t0to5 ~ cat_treat, data = female_amp_df)
# log variances are homogeneous
```



```{r}
# one-way ANOVA
female_baseline_amp_anova <- aov(t0to5 ~ cat_treat, data = female_amp_df)
summary(female_baseline_amp_anova)

# log one-way ANOVA
log_female_baseline_amp_anova <- aov(log_t0to5 ~ cat_treat, data = female_amp_df)
summary(log_female_baseline_amp_anova)
```

```{r}
# normal residuals
female_baseline_amp_anova_residuals <- residuals(female_baseline_amp_anova)

# check normality of residuals
shapiro.test(female_baseline_amp_anova_residuals)
# not normal

hist(female_baseline_amp_anova_residuals, breaks = 10, main = "Residuals Histogram")

qqnorm(female_baseline_amp_anova_residuals)
qqline(female_baseline_amp_anova_residuals, col = "red")



# log residuals
log_female_baseline_amp_anova_residuals <- residuals(female_baseline_amp_anova)

# check normality of residuals
shapiro.test(log_female_baseline_amp_anova_residuals)
# not any better

hist(log_female_baseline_amp_anova_residuals, breaks = 10, main = "Residuals Histogram")

qqnorm(log_female_baseline_amp_anova_residuals)
qqline(log_female_baseline_amp_anova_residuals, col = "red")
```

```{r}
# non-parametric Kruskal-Wallis (on original untransformed data)

kruskal.test(t0to5 ~ cat_treat, data = female_amp_df)
```

## ANOVA for post HFS eEPSC

```{r}
# assumptions

leveneTest(t25to30 ~ cat_treat, data = female_amp_df)
# variances are homogeneous

leveneTest(log_t25to30 ~ cat_treat, data = female_amp_df)
# variances are homogeneous
```

```{r}
# one-way ANOVA
female_HFS_amp_anova <- aov(t25to30 ~ cat_treat, data = female_amp_df)
summary(female_HFS_amp_anova)

# log
log_female_HFS_amp_anova <- aov(log_t25to30 ~ cat_treat, data = female_amp_df)
summary(log_female_HFS_amp_anova)
```

```{r}
# residuals
female_HFS_amp_anova_residuals <- residuals(female_HFS_amp_anova)

# check normality of residuals
shapiro.test(female_HFS_amp_anova_residuals)
# not normal

hist(female_HFS_amp_anova_residuals, breaks = 10, main = "Residuals Histogram")

qqnorm(female_HFS_amp_anova_residuals)
qqline(female_HFS_amp_anova_residuals, col = "red")



# log transformed
log_female_HFS_amp_anova_residuals <- residuals(log_female_HFS_amp_anova)

# check normality of residuals
shapiro.test(log_female_HFS_amp_anova_residuals)
# normal

hist(log_female_HFS_amp_anova_residuals, breaks = 10, main = "Residuals Histogram")

qqnorm(log_female_HFS_amp_anova_residuals)
qqline(log_female_HFS_amp_anova_residuals, col = "red")
```


## Repeated Measures
```{r}
# convert to long
df_female_long <- summary_eEPSC_df$percent_change_data %>% filter(sex=="Female") %>%
  pivot_longer(
    cols = c(t0to5, t5to10, t10to15, t15to20, t20to25, t25to30),  # ONLY the time columns
    names_to = "time",         # new column for time window
    values_to = "time_value"   # new column for the corresponding value of that time window
  ) %>% mutate(
    time = factor(time, levels = c("t0to5","t5to10","t10to15","t15to20","t20to25","t25to30")),
group = case_when(
      sex == "Female" & category == 1 & treatment == "Control" ~ "naive",
      sex == "Female" & category == 2 & treatment == "Control" ~ "acute",
      sex == "Female" & category == 2 & treatment == "AM251"   ~ "AM251",
      sex == "Female" & category == 3 & treatment == "Control" ~ "repeated",
      sex == "Female" & category == 1 & treatment == "Cort" ~ "cort"
      ),
    group = factor(group, levels = c("naive", "acute", "AM251", "repeated", "cort"))
  ) %>% ungroup() %>% as.data.frame() %>% droplevels() %>%
  filter(!is.na(group))

df_female_long <- df_female_long %>% filter(! letter %in% c("RMA100A", "RMR100", "RMR101", "RMR102", "RMR103", "RMR104", "RMR105", "RMR106", "RMR107")) # need to filter out neurons that are ONLY baselines (they are not repeated)
```

means and variances.
```{r}
library(tidyverse)
df_female_long %>%
  group_by(group, time) %>%
  summarise(N = n(), mean=mean(time_value), var=var(time_value))
# unlikely to have homogeneity of variances 
```

```{r}
# eyeball interaction plot

library(sciplot)
df_female_long$time <- factor(df_female_long$time, levels=c("t0to5", "t5to10", "t10to15", "t15to20", "t20to25", "t25to30")) # telling it what order
lineplot.CI(x.factor=time, response=time_value, group=group, xlab="Time Interval", ylab="eEPSC Amplitude (pA)", data=df_female_long) 

# looks like an interaction for sure
```

```{r}
library(nlme)
# don't need letter/time because there are not multiple measurements (subsamples) for each letter (neuron) at each time interval

# starting it off with imposed compound symmetry (assumes sphericity)
project_model.cs = lme(time_value ~ group*time, data = df_female_long, random = ~1|letter, correlation = corCompSymm(form = ~1|letter)) 
anova(project_model.cs) 
```


```{r, fig.width = 12, fig.height = 10}
library(sjPlot) 
plot_grid(plot_model(project_model.cs, type = "diag")) 
# residuals don't look very normal
# variance has a fan pattern
# not passing assumptions
```

```{r}
# actually testing for sphericity
library(afex) 
project_repmesanov <- aov_ez(
  id = "letter",  
  dv = "time_value",
  data = df_female_long,
  between = c("group"),
  within = c("time"),
  type = "III")  # type III because I probably have an interaction
summary(project_repmesanov)
anova(project_repmesanov)

# FAILS SPHERICITY (Mauchly Test p-value was less than 0.05) -> want linear mixed model -> compound symmetry variance structure not appropriate
```

```{r}
# failed sphericity -> can't use the model with compound symmetry imposed -> but still want to use a linear mixed model

# still don't need letter/time because there are not multiple measurements (sub samples) for each letter (neuron) at each time interval


# log transform
df_female_long$log_time_value <- log(df_female_long$time_value)


# log model with imposed compound symmetry
log_project_model.cs = lme(log_time_value ~ group*time, data = df_female_long, random = ~1|letter, correlation = corCompSymm(form = ~1|letter)) 
anova(log_project_model.cs) 


# does the log model with imposed compound symmetry pass assumptions of sphericity
library(afex) 
log_project_repmesanov <- aov_ez(
  id = "letter",  
  dv = "log_time_value",
  data = df_female_long,
  between = c("group"),
  within = c("time"),
  type = "III")  # type III because I probably have an interaction
summary(log_project_repmesanov)
anova(log_project_repmesanov)

# FAILS SPHERICITY (Mauchly Test p-value was less than 0.05... tiny bit better than before but still bad) -> compound symmetry variance structure not appropriate
```


```{r}
# don't need letter/time because each letter was not measured multiple times at each time interval (because I already pruned them)

# check for autocorrelation
acf(resid(log_project_model.cs))
# looks autocorrelated (bigger to smaller trend) -> try ar1 (autoregressive)

log_project_model.ar1 = lme(log_time_value ~ group*time, data = df_female_long, random = ~1|letter, correlation=corAR1(form= ~1|letter))
anova(log_project_model.ar1)
anova(log_project_model.cs, log_project_model.ar1)

# (autoregressive) ar1 structure is a better fit (lower AIC)
# significant effect of time (p < 0.0001) and of group*time interaction (p = 0.0133)
# INTERACTION -> CANNOT DIRECTLY INTERPRET MAIN EFFECTS
```

```{r, fig.width = 12, fig.height = 10}
# does this ar1 log model pass assumptions for a linear mixed model?

plot_grid(plot_model(log_project_model.ar1, type = "diag")) 

# want a p-value
log_project_model.ar1.resid=resid(log_project_model.ar1)
shapiro.test(log_project_model.ar1.resid) 
```

INTERACTION -> CANNOT DIRECTLY INTERPRET MAIN EFFECTS
more interested in the effect of time WITHIN groups
remove the between-subjects factor (group/treatment)

```{r}
library(emmeans)
library(nlme) 

# randomized block analysis for each group level


# subset by group
df_female_summary_naive <- df_female_long %>% filter(group == "naive")
df_female_summary_acute <- df_female_long %>% filter(group == "acute")
df_female_summary_AM251 <- df_female_long %>% filter(group == "AM251")
df_female_summary_repeated <- df_female_long %>% filter(group == "repeated")
df_female_summary_cort <- df_female_long %>% filter(group == "cort")
```

```{r}
# naive
ar1.project_naive.fit <- lme(
  log_time_value ~ time,
  random = ~1 | letter,
  data = df_female_summary_naive,
  correlation = corAR1(form= ~1|letter)
)
anova(ar1.project_naive.fit) # not significant (p = 0.093) -> don't need post hoc
```

```{r}
# acute
ar1.project_acute.fit <- lme(
  log_time_value ~ time,
  random = ~1 | letter,
  data = df_female_summary_acute,
  correlation = corAR1(form= ~1|letter)
)
anova(ar1.project_acute.fit) # significant effect of time (p = 1e-0.4) -> need post hoc


# acute subset
acute_t0to5_t5to10 <- subset(df_female_summary_acute, time=="t0to5" | time=="t5to10")
acute_t0to5_t10to15 <- subset(df_female_summary_acute, time=="t0to5" | time=="t10to15")
acute_t0to5_t15to20 <- subset(df_female_summary_acute, time=="t0to5" | time=="t15to20")
acute_t0to5_t20to25 <- subset(df_female_summary_acute, time=="t0to5" | time=="t20to25")
acute_t0to5_t25to30 <- subset(df_female_summary_acute, time=="t0to5" | time=="t25to30")

# p-values evaluated against p = 0.01 to account for multiple (5) comparisons

# t0to5 vs t5to10 = not significant (0.3919511)
acute_repmesanov.t0to5_t5to10 <- aov_ez(id = "letter", dv = "time_value", data = acute_t0to5_t5to10, within = "time",
  type = "III") # type III is default for when there is only one factor (time)
summary(acute_repmesanov.t0to5_t5to10)

# t0to5 vs t10to15 = not significant (0.2490239)
acute_repmesanov.t0to5_t10to15 <- aov_ez(id = "letter", dv = "time_value", data = acute_t0to5_t10to15, within = "time",
  type = "III")  
summary(acute_repmesanov.t0to5_t10to15)

# t0to5 vs t15to20 = not significant (0.0198726) evaluating against alpha 0.01 to account for multiple comparisons
acute_repmesanov.t0to5_t15to20 <- aov_ez(id = "letter", dv = "time_value", data = acute_t0to5_t15to20, within = "time",
  type = "III")  
summary(acute_repmesanov.t0to5_t15to20)

# t0to5 vs t20to25 = significant (0.0066564)
acute_repmesanov.t0to5_t20to25 <- aov_ez(id = "letter", dv = "time_value", data = acute_t0to5_t20to25, within = "time",
  type = "III")  
summary(acute_repmesanov.t0to5_t20to25)

# t0to5 vs t25to30 = significant (0.00618)
acute_repmesanov.t0to5_t25to30 <- aov_ez(id = "letter", dv = "time_value", data = acute_t0to5_t25to30, within = "time",
  type = "III")  
summary(acute_repmesanov.t0to5_t25to30)
```

```{r}
# AM251
ar1.project_AM251.fit <- lme(
  log_time_value ~ time,
  random = ~1 | letter,
  data = df_female_summary_AM251,
  correlation = corAR1(form= ~1|letter)
)
anova(ar1.project_AM251.fit) # significant effect of time (p = 0.0279) -> need post hoc


# am251 subset
AM251_t0to5_t5to10 <- subset(df_female_summary_AM251, time=="t0to5" | time=="t5to10")
AM251_t0to5_t10to15 <- subset(df_female_summary_AM251, time=="t0to5" | time=="t10to15")
AM251_t0to5_t15to20 <- subset(df_female_summary_AM251, time=="t0to5" | time=="t15to20")
AM251_t0to5_t20to25 <- subset(df_female_summary_AM251, time=="t0to5" | time=="t20to25")
AM251_t0to5_t25to30 <- subset(df_female_summary_AM251, time=="t0to5" | time=="t25to30")

# p-values evaluated against p = 0.01 to account for multiple (5) comparisons

# t0to5 vs t5to10 = not significant (0.430472)
AM251_repmesanov.t0to5_t5to10 <- aov_ez(id = "letter", dv = "time_value", data = AM251_t0to5_t5to10, within = "time",
  type = "III") # type III is default for when there is only one factor (time)
summary(AM251_repmesanov.t0to5_t5to10)

# t0to5 vs t10to15 = not significant (0.495999)
AM251_repmesanov.t0to5_t10to15 <- aov_ez(id = "letter", dv = "time_value", data = AM251_t0to5_t10to15, within = "time",
  type = "III")  
summary(AM251_repmesanov.t0to5_t10to15)

# t0to5 vs t15to20 = not significant (0.310160)
AM251_repmesanov.t0to5_t15to20 <- aov_ez(id = "letter", dv = "time_value", data = AM251_t0to5_t15to20, within = "time",
  type = "III")  
summary(AM251_repmesanov.t0to5_t15to20)

# t0to5 vs t20to25 = not significant (0.15574)
AM251_repmesanov.t0to5_t20to25 <- aov_ez(id = "letter", dv = "time_value", data = AM251_t0to5_t20to25, within = "time",
  type = "III")  
summary(AM251_repmesanov.t0to5_t20to25)

# t0to5 vs t25to30 = not significant (0.031281)
AM251_repmesanov.t0to5_t25to30 <- aov_ez(id = "letter", dv = "time_value", data = AM251_t0to5_t25to30, within = "time",
  type = "III")  
summary(AM251_repmesanov.t0to5_t25to30)
```


```{r}
# repeated
ar1.project_repeated.fit <- lme(
  log_time_value ~ time,
  random = ~1 | letter,
  data = df_female_summary_repeated,
  correlation = corAR1(form= ~1|letter)
)
anova(ar1.project_repeated.fit) # significant effect of time (p = 0.0169) -> need post hoc


# repeated subset
repeated_t0to5_t5to10 <- subset(df_female_summary_repeated, time=="t0to5" | time=="t5to10")
repeated_t0to5_t10to15 <- subset(df_female_summary_repeated, time=="t0to5" | time=="t10to15")
repeated_t0to5_t15to20 <- subset(df_female_summary_repeated, time=="t0to5" | time=="t15to20")
repeated_t0to5_t20to25 <- subset(df_female_summary_repeated, time=="t0to5" | time=="t20to25")
repeated_t0to5_t25to30 <- subset(df_female_summary_repeated, time=="t0to5" | time=="t25to30")

# p-values evaluated against p = 0.01 to account for multiple (5) comparisons

# t0to5 vs t5to10 = not significant (0.342114)
repeated_repmesanov.t0to5_t5to10 <- aov_ez(id = "letter", dv = "time_value", data = repeated_t0to5_t5to10, within = "time",
  type = "III") # type III is default for when there is only one factor (time)
summary(repeated_repmesanov.t0to5_t5to10)

# t0to5 vs t10to15 = not significant (0.200030)
repeated_repmesanov.t0to5_t10to15 <- aov_ez(id = "letter", dv = "time_value", data = repeated_t0to5_t10to15, within = "time",
  type = "III")  
summary(repeated_repmesanov.t0to5_t10to15)

# t0to5 vs t15to20 = not significant (0.095749)
repeated_repmesanov.t0to5_t15to20 <- aov_ez(id = "letter", dv = "time_value", data = repeated_t0to5_t15to20, within = "time",
  type = "III")  
summary(repeated_repmesanov.t0to5_t15to20)

# t0to5 vs t20to25 = not significant (0.128527)
repeated_repmesanov.t0to5_t20to25 <- aov_ez(id = "letter", dv = "time_value", data = repeated_t0to5_t20to25, within = "time",
  type = "III")  
summary(repeated_repmesanov.t0to5_t20to25)

# t0to5 vs t25to30 = not significant (0.190323)
repeated_repmesanov.t0to5_t25to30 <- aov_ez(id = "letter", dv = "time_value", data = repeated_t0to5_t25to30, within = "time",
  type = "III")  
summary(repeated_repmesanov.t0to5_t25to30)
```

```{r}
# cort
ar1.project_cort.fit <- lme(
  log_time_value ~ time,
  random = ~1 | letter,
  data = df_female_summary_cort,
  correlation = corAR1(form= ~1|letter)
)
anova(ar1.project_cort.fit) # significant effect of time (p = 0.1603) -> need post hoc
```

p-values evaluated against p = 0.01 to account for multiple (5) comparisons
bonferroni correction
0.05/5 = 0.01 (corrected alpha level)

## t-test between naive and acute baseline eEPSC
```{r}
# adding group column
female_amp_df <- female_amp_df %>%
  mutate(
    group = case_when(
      category == 1 & treatment == "Control" ~ "naive",
    category == 2 & treatment == "Control" ~ "acute",
    category == 2 & treatment == "AM251" ~ "AM251",
    category == 3 & treatment == "Control" ~ "repeated",
    category == 1 & treatment == "Cort" ~ "cort" ))

# already has cell means (t0to5)

# normality
shapiro.test(female_amp_df$t0to5[female_amp_df$group == "naive"])
qqnorm(female_amp_df$t0to5[female_amp_df$group == "naive"])
qqline(female_amp_df$t0to5[female_amp_df$group == "naive"]) # passes

shapiro.test(female_amp_df$t0to5[female_amp_df$group == "acute"])
qqnorm(female_amp_df$t0to5[female_amp_df$group == "acute"])
qqline(female_amp_df$t0to5[female_amp_df$group == "acute"]) # passes

# HoV
leveneTest(t0to5 ~ group, data = female_amp_df) # passes

# running the t-test
t.test(female_amp_df$t0to5[female_amp_df$group == "naive"],
            female_amp_df$t0to5[female_amp_df$group == "acute"],
            paired = FALSE,
       var.equal = TRUE)
# significantly different (p = 0.03426)
```

## t-test between naive and acute baseline PPR
```{r}
# female filter
female_PPR_cell_df <- PPR_cell_df %>% filter(sex == "Female")

# normality
shapiro.test(female_PPR_cell_df$mean_PPR_cell[female_PPR_cell_df$group == "naive"])
qqnorm(female_PPR_cell_df$mean_PPR_cell[female_PPR_cell_df$group == "naive"])
qqline(female_PPR_cell_df$mean_PPR_cell[female_PPR_cell_df$group == "naive"]) # passes

shapiro.test(female_PPR_cell_df$mean_PPR_cell[female_PPR_cell_df$group == "acute"])
qqnorm(female_PPR_cell_df$mean_PPR_cell[female_PPR_cell_df$group == "acute"])
qqline(female_PPR_cell_df$mean_PPR_cell[female_PPR_cell_df$group == "acute"]) # passes

# HoV
leveneTest(mean_PPR_cell ~ group, data = female_PPR_cell_df) # passes

# running the t-test
t.test(female_PPR_cell_df$mean_PPR_cell[female_PPR_cell_df$group == "naive"],
            female_PPR_cell_df$mean_PPR_cell[female_PPR_cell_df$group == "acute"],
            paired = FALSE,
       var.equal = TRUE)
# NOT significantly different (p = 0.09049)
```

## other baseline parameters
```{r}
baseline_parameters <- read.csv("Data/baseline_parameters.csv")
```
```{r}
# Cm
# normality
shapiro.test(baseline_parameters$Cm[baseline_parameters$group == "naive"])
qqnorm(baseline_parameters$Cm[baseline_parameters$group == "naive"])
qqline(baseline_parameters$Cm[baseline_parameters$group == "naive"]) # passes

shapiro.test(baseline_parameters$Cm[baseline_parameters$group == "acute"])
qqnorm(baseline_parameters$Cm[baseline_parameters$group == "acute"])
qqline(baseline_parameters$Cm[baseline_parameters$group == "acute"]) # passes

# HoV
leveneTest(Cm ~ group, data = baseline_parameters) # passes

# t-test
t.test(baseline_parameters$Cm[baseline_parameters$group == "naive"],
            baseline_parameters$Cm[baseline_parameters$group == "acute"],
            paired = FALSE,
       var.equal = TRUE) # not different (p = 0.6262)

# Vm
# normality
shapiro.test(baseline_parameters$Vm[baseline_parameters$group == "naive"])
qqnorm(baseline_parameters$Vm[baseline_parameters$group == "naive"])
qqline(baseline_parameters$Vm[baseline_parameters$group == "naive"]) # passes

shapiro.test(baseline_parameters$Vm[baseline_parameters$group == "acute"])
qqnorm(baseline_parameters$Vm[baseline_parameters$group == "acute"])
qqline(baseline_parameters$Vm[baseline_parameters$group == "acute"]) # passes

# HoV
leveneTest(Vm ~ group, data = baseline_parameters) # passes

# t-test
t.test(baseline_parameters$Vm[baseline_parameters$group == "naive"],
           baseline_parameters$Vm[baseline_parameters$group == "acute"],
            paired = FALSE,
       var.equal = TRUE) # not different (p = 0.08435)
```
Cm Plot
```{r}
# data

female_acute_baseline_Cm_plot <- baseline_parameters %>%
  mutate(group = factor(group, levels = c("naive", "acute"))) %>%

ggplot(aes(x = group, y = Cm)) +


patchclampplotteR_theme() +
  
# axis labels
  labs(x = NULL, y = "Baseline Membrane Capacitance (pF)") +
  patchclampplotteR_theme() +
  
# the boxes
  geom_boxplot(aes(fill = group), 
               alpha = 0.6, 
               color = "black", # get rid of if want the dark colour to be the outline
# outlier.shape = NA stops the box plot from plotting outliers. BUT because the sina plot is a different layer, all outliers are still shown as dots from that.
               outlier.shape = NA, 
               width = 0.5, 
               show.legend = FALSE)  +
  
  # the dots/scatter plot
  geom_sina(aes(x = group, color = group), 
            max_width = 0.2, 
            shape = 16, 
            size = 2, 
            show.legend = FALSE) +
  
  # significance bracket
  geom_signif(
    comparisons = list(c("naive", "acute")),
    map_signif_level = TRUE,
    annotations = "ns", 
    y_position = max(baseline_parameters$Cm) * 1.05,
    tip_length = 0.02,
    textsize = 5
  ) +

  # colours
  scale_fill_manual(values = c("naive" = "#f5e0b3",
                               "acute" = "#f19cac")) +
  
  scale_color_manual(values = c("naive" = "#ecc479", 
                                "acute" = "#eb647e")) +
  
  # x-axis labels  
scale_x_discrete(labels = c("naive" = "Naive",
                            "acute" = "Acute")) +
  

  scale_y_continuous(expand = expansion(mult = c(0.2, .2))) +

  guides(fill = "none", color = "none")

female_acute_baseline_Cm_plot

# ggsave(female_acute_baseline_Cm_plot, path = here("Figures"), file = "female_acute_baseline_Cm_plot.png", width = 7, height = 5, units = "in", dpi = 300)
```

Vm Plot
```{r}
# data

female_acute_baseline_Vm_plot <- baseline_parameters %>%
  mutate(group = factor(group, levels = c("naive", "acute"))) %>%

ggplot(aes(x = group, y = Vm)) +


patchclampplotteR_theme() +
  
# axis labels
  labs(x = NULL, y = "Resting Membrane Potential (mV)") +
  patchclampplotteR_theme() +
  
# the boxes
  geom_boxplot(aes(fill = group), 
               alpha = 0.6, 
               color = "black", # get rid of if want the dark colour to be the outline
# outlier.shape = NA stops the box plot from plotting outliers. BUT because the sina plot is a different layer, all outliers are still shown as dots from that.
               outlier.shape = NA, 
               width = 0.5, 
               show.legend = FALSE)  +
  
  # the dots/scatter plot
  geom_sina(aes(x = group, color = group), 
            max_width = 0.2, 
            shape = 16, 
            size = 2, 
            show.legend = FALSE) +
  
  # significance bracket
  geom_signif(
    comparisons = list(c("naive", "acute")),
    map_signif_level = TRUE,
    annotations = "ns", 
    y_position = max(baseline_parameters$Vm) * 0.05,
    tip_length = 0.02,
    textsize = 5
  ) +

  # colours
  scale_fill_manual(values = c("naive" = "#f5e0b3",
                               "acute" = "#f19cac")) +
  
  scale_color_manual(values = c("naive" = "#ecc479", 
                                "acute" = "#eb647e")) +
  
  # x-axis labels  
scale_x_discrete(labels = c("naive" = "Naive",
                            "acute" = "Acute")) +
  

  scale_y_continuous(expand = expansion(mult = c(0.2, .2))) +

  guides(fill = "none", color = "none")

female_acute_baseline_Vm_plot

# ggsave(female_acute_baseline_Vm_plot, path = here("Figures"), file = "female_acute_baseline_Vm_plot.png", width = 7, height = 5, units = "in", dpi = 300)
```

```{r}
project_group_colours <- c(
  "cort" = "#ecc479",
  "acute" = "#eb647e"
)

project_group_fill_colours <- c(
  "cort" = "#f5e0b3",
  "acute" = "#f19cac"
)

AP_freq_df$sweep <- as.factor(AP_freq_df$sweep)

# filter to only cort (naive) and acute and "Baseline" state
# and summarize the data by calculating the average AP_frequency per group and sweep
baseline_acute_AP_freq_df <- AP_freq_df %>%
  filter(state == "Baseline" & group %in% c("cort", "acute")) %>%
  group_by(group, sweep) %>%
  summarise(
    mean_AP_frequency = mean(AP_frequency, na.rm = TRUE),
    se_AP_freq = sd(AP_frequency, na.rm = TRUE) / sqrt(n()),  # Standard Error
    .groups = "drop"
  )

# create error bar colour column (same logic as your other plot)
baseline_acute_AP_freq_df$errorbar_colour <- 
  project_group_fill_colours[as.character(baseline_acute_AP_freq_df$group)]

# correct order in the plot
baseline_acute_AP_freq_df <- baseline_acute_AP_freq_df %>%
  mutate(group = factor(group, levels = c("cort", "acute")))

# plot
baseline_acute_AP_freq_plot <- ggplot(baseline_acute_AP_freq_df, aes(x = sweep, y = mean_AP_frequency, group = group)) +
  patchclampplotteR_theme() + 
  
# axis labels
  labs(x = "Sweep", y = "Action Potential Frequency (Hz)") +
  
# line plot to show the trend of mean AP frequency per sweep for each group
  geom_line(aes(color = group), linewidth = 1.2) +

# points on the lines for each sweep
  geom_point(aes(color = group), size = 2) +

# error bars for SE
  geom_errorbar(
    aes(
      ymin = mean_AP_frequency - se_AP_freq,
      ymax = mean_AP_frequency + se_AP_freq,
      color = baseline_acute_AP_freq_df$errorbar_colour
    ),
    width = 0.2,
    linewidth = 0.85
  ) +
  
# colours
  scale_color_manual(values = project_group_colours) +

  
# significance
  geom_signif(
    comparisons = list(c("cort", "acute")),
    map_signif_level = TRUE,
    annotations = "ns",  
    y_position = max(baseline_acute_AP_freq_df$mean_AP_frequency) * 0.1,
    tip_length = 0.02,
    textsize = 5
  ) +
  
  
# y-axis scaling and limits
  scale_y_continuous(expand = expansion(mult = c(0.2, 0.2))) +
  
# hide legends for fill and color
  guides(fill = "none", color = "none")

# Print the plot
baseline_acute_AP_freq_plot

# Optionally save the plot
# ggsave(AP_freq_plot, path = here("Figures"), filename = "AP_freq_plot.png", width = 7, height = 5, units = "in", dpi = 300)
```
stats on the baseline AP freq:
```{r eval=FALSE}
baseline_acute_AP_freq_df # data frame is already in long format

# eyeball interaction plot
baseline_acute_AP_freq_df$sweep <- factor(baseline_acute_AP_freq_df$sweep, levels=c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10")) # telling it what order
lineplot.CI(x.factor=sweep, response=mean_AP_frequency, group=group, xlab="Sweep", ylab="AP Frequency (Hz)", data=baseline_acute_AP_freq_df) # maybe interaction

# to keep the random factor of letter in the df
baseline_acute_AP_freq_stats_df <- AP_freq_df %>%
  filter(state == "Baseline" & group %in% c("cort", "acute")) 
baseline_acute_AP_freq_stats_df


# starting it off with imposed compound symmetry (assumes sphericity)
baseline_acute_AP_freq_stats.cs = lme(AP_frequency ~ group*sweep, data = baseline_acute_AP_freq_stats_df, random = ~1|letter, correlation = corCompSymm(form = ~1|letter)) 

plot_grid(plot_model(baseline_acute_AP_freq_stats.cs, type = "diag")) # good enough

acf(resid(baseline_acute_AP_freq_stats.cs)) # looks autocorrelated

# trying with autoregressive (ar1) structure
baseline_acute_AP_freq_stats.ar1 = lme(AP_frequency ~ group*sweep, data = baseline_acute_AP_freq_stats_df, random = ~1|letter, correlation=corAR1(form= ~1|letter))

# which model is better
anova(baseline_acute_AP_freq_stats.cs, baseline_acute_AP_freq_stats.ar1)
# autoregressive structure is a better fit

# actually running
anova(baseline_acute_AP_freq_stats.ar1) 
# effect of sweep, and effect of interaction
# biologically, of course the higher sweep has more AP... so I want to see the difference between groups -> do one way anova for the effect of group at each sweep

# subset
sweep_1 <- baseline_acute_AP_freq_stats_df %>% filter(sweep %in% "1")
sweep_1
sweep_2 <- baseline_acute_AP_freq_stats_df %>% filter(sweep %in% "2")
sweep_3 <- baseline_acute_AP_freq_stats_df %>% filter(sweep %in% "3")
sweep_4 <- baseline_acute_AP_freq_stats_df %>% filter(sweep %in% "4")
sweep_5 <- baseline_acute_AP_freq_stats_df %>% filter(sweep %in% "5")
sweep_6 <- baseline_acute_AP_freq_stats_df %>% filter(sweep %in% "6")
sweep_7 <- baseline_acute_AP_freq_stats_df %>% filter(sweep %in% "7")
sweep_8 <- baseline_acute_AP_freq_stats_df %>% filter(sweep %in% "8")
sweep_9 <- baseline_acute_AP_freq_stats_df %>% filter(sweep %in% "9")
sweep_10 <- baseline_acute_AP_freq_stats_df %>% filter(sweep %in% "10")

# HoV for t-tests
leveneTest(AP_frequency ~ group, data = baseline_acute_AP_freq_stats_df) # passes

# p-values evaluated against p = 0.001 to account for multiple (10) comparisons

t.test(sweep_1$AP_frequency[sweep_1$AP_frequency$letter %in% c("RMC1", "RMC2", "RMC3", "RMC4", "RMC5", "RMC6", "RMC7")],
       sweep_1$AP_frequency[sweep_1$AP_frequency$letter %in% c("RMA1", "RMA2", "RMA3", "RMA4", "RMA6", "RMA8", "RMA9", "RMA10")],
       paired = FALSE,
       var.equal = TRUE)
```
# Spontaneous Currents
```{r eval=FALSE}
# FOR FIRST TIME ONLY
first_time_df <- add_new_cells(
  new_raw_data_csv = "Data/new_raw_sEPSC.csv",
  cell_characteristics_csv = "Data/Cell-Characteristics.csv",
  old_raw_data_csv = "Data/raw_sEPSC_df.csv",
  data_type = "sEPSC",
  software = "MiniAnalysis",
  bin_width = 5,
  write_new_csv = "yes",
  new_file_name = "Data/raw_sEPSC_df.csv",
  decimal_places = 2,
)
```
To Append New Data onto the EXISTING SHEET (raw_sEPSC_df.csv) after first time
```{r eval=FALSE}
# will not run if there is nothing new in "new_raw_sEPSC.csv" so if you put new data directly into "raw_sEPSC_df.csv", it won't run
add_new_cells(
  new_raw_data_csv = "Data/new_raw_sEPSC.csv", # should ONLY have the new data you want
  cell_characteristics_csv = "Data/Cell-Characteristics.csv",
  old_raw_data_csv = "Data/raw_sEPSC_df.csv",
  data_type = "sEPSC",
  software = "MiniAnalysis",
  write_new_csv = "yes",
  new_file_name = "Data/raw_sEPSC_df.csv", # will overwrite the current version of this file
  decimal_places = 2
)

# once successful, go delete the data from "new_raw_eEPSC.csv" so that you don't get a duplication error the next time you are adding data to the raw_eEPSC_df.
```

```{r}
raw_sEPSC_df <- read.csv("Data/raw_sEPSC_df.csv")
```


Normalizing Data:
```{r}
normalized_raw_sEPSC_df <- make_normalized_EPSC_data(
  filename = "Data/raw_sEPSC_df.csv",
  current_type = "sEPSC",
  min_time_value = 0,
  max_time_value = 30,
  interval_length = 5,
  baseline_length = 5,
  negative_transform_currents = "yes" # because the raw amplitudes are negative
)
```

Pruning:
```{r}
pruned_sEPSC_df <- make_pruned_EPSC_data(
  data = normalized_raw_sEPSC_df,
  current_type = "sEPSC",
  software = "MiniAnalysis",
  min_time_value = 0,
  max_time_value = 30,
  baseline_length = 5,
  interval_length = 1,
  decimal_places = 2
)
```

Summary Data:
```{r}
summary_sEPSC_df <- make_summary_EPSC_data(
  data = pruned_sEPSC_df$individual_cells, 
  current_type = "sEPSC",
  save_output_as_RDS = "no",
  baseline_interval = "t0to5",
  ending_interval = "t25to30"
)
```

```{r}
# adding group column

summary_sEPSC_df$percent_change_amplitude <- summary_sEPSC_df$percent_change_amplitude %>%
  mutate(group = case_when(
    category == 1 & treatment == "Control" ~ "naive",
    category == 2 & treatment == "Control" ~ "acute",
    category == 2 & treatment == "AM251"   ~ "AM251",
    category == 3 & treatment == "Control" ~ "repeated",
    category == 1 & treatment == "Cort"    ~ "cort"
  )) %>%
  mutate(group = factor(group, levels = c("naive", "acute", "AM251", "repeated", "cort")))

summary_sEPSC_df$percent_change_frequency <- summary_sEPSC_df$percent_change_frequency %>%
  mutate(group = case_when(
    category == 1 & treatment == "Control" ~ "naive",
    category == 2 & treatment == "Control" ~ "acute",
    category == 2 & treatment == "AM251"   ~ "AM251",
    category == 3 & treatment == "Control" ~ "repeated",
    category == 1 & treatment == "Cort"    ~ "cort"
  )) %>%
  mutate(group = factor(group, levels = c("naive", "acute", "AM251", "repeated", "cort")))

summary_sEPSC_df$summary_data <- summary_sEPSC_df$summary_data %>%
  mutate(group = case_when(
    category == 1 & treatment == "Control" ~ "naive",
    category == 2 & treatment == "Control" ~ "acute",
    category == 2 & treatment == "AM251"   ~ "AM251",
    category == 3 & treatment == "Control" ~ "repeated",
    category == 1 & treatment == "Cort"    ~ "cort"
  )) %>%
  mutate(group = factor(group, levels = c("naive", "acute", "AM251", "repeated", "cort")))

summary_sEPSC_df$mean_SE_amplitude <- summary_sEPSC_df$mean_SE_amplitude %>%
  mutate(group = case_when(
    category == 1 & treatment == "Control" ~ "naive",
    category == 2 & treatment == "Control" ~ "acute",
    category == 2 & treatment == "AM251"   ~ "AM251",
    category == 3 & treatment == "Control" ~ "repeated",
    category == 1 & treatment == "Cort"    ~ "cort"
  )) %>%
  mutate(group = factor(group, levels = c("naive", "acute", "AM251", "repeated", "cort")))

summary_sEPSC_df$mean_SE_frequency <- summary_sEPSC_df$mean_SE_frequency %>%
  mutate(group = case_when(
    category == 1 & treatment == "Control" ~ "naive",
    category == 2 & treatment == "Control" ~ "acute",
    category == 2 & treatment == "AM251"   ~ "AM251",
    category == 3 & treatment == "Control" ~ "repeated",
    category == 1 & treatment == "Cort"    ~ "cort"
  )) %>%
  mutate(group = factor(group, levels = c("naive", "acute", "AM251", "repeated", "cort")))


# add difference column
summary_sEPSC_df$percent_change_amplitude <- summary_sEPSC_df$percent_change_amplitude %>%
  mutate(diff = t25to30 - t0to5)

# add difference column
summary_sEPSC_df$percent_change_frequency <- summary_sEPSC_df$percent_change_frequency %>%
  mutate(diff = t25to30 - t0to5)
```



## Amplitude t-test
```{r}
# normality

shapiro.test(summary_sEPSC_df$percent_change_amplitude$t0to5[summary_sEPSC_df$percent_change_amplitude$group == "naive"]) # p = 0.1554
shapiro.test(summary_sEPSC_df$percent_change_amplitude$t25to30[summary_sEPSC_df$percent_change_amplitude$group == "naive"]) # p = 0.5708

shapiro.test(summary_sEPSC_df$percent_change_amplitude$t0to5[summary_sEPSC_df$percent_change_amplitude$group == "acute"]) # p = 0.8667
shapiro.test(summary_sEPSC_df$percent_change_amplitude$t25to30[summary_sEPSC_df$percent_change_amplitude$group == "acute"]) # p = 0.8609


# HoV
leveneTest(t0to5 ~ group, data = summary_sEPSC_df$percent_change_amplitude) # p = 0.6267
leveneTest(t25to30 ~ group, data = summary_sEPSC_df$percent_change_amplitude) # p = 0.6974

# running the t-test
t.test(summary_sEPSC_df$percent_change_amplitude$t0to5[summary_sEPSC_df$percent_change_amplitude$group == "naive"], summary_sEPSC_df$percent_change_amplitude$t0to5[summary_sEPSC_df$percent_change_amplitude$group == "acute"], paired = FALSE, var.equal = TRUE) # sEPSC amplitude does not significantly differ at baseline between naive and acute (p = 0.8456)

t.test(summary_sEPSC_df$percent_change_amplitude$t25to30[summary_sEPSC_df$percent_change_amplitude$group == "naive"], summary_sEPSC_df$percent_change_amplitude$t25to30[summary_sEPSC_df$percent_change_amplitude$group == "acute"], paired = FALSE, var.equal = TRUE) # sEPSC amplitude does not significantly differ at baseline between naive and acute (p = 0.8892)
```

## Frequency t-test
```{r}
# normality

shapiro.test(summary_sEPSC_df$percent_change_frequency$t0to5[summary_sEPSC_df$percent_change_frequency$group == "naive"]) # p = 0.2688
shapiro.test(summary_sEPSC_df$percent_change_frequency$t25to30[summary_sEPSC_df$percent_change_frequency$group == "naive"]) # p = 0.01193
qqnorm(summary_sEPSC_df$percent_change_frequency$t25to30[summary_sEPSC_df$percent_change_frequency$group == "naive"])
qqline(summary_sEPSC_df$percent_change_frequency$t25to30[summary_sEPSC_df$percent_change_frequency$group == "naive"]) # not THAT bad, gonna take it (still not significant with a very high p-value when I do a wilcoxon)

shapiro.test(summary_sEPSC_df$percent_change_frequency$t0to5[summary_sEPSC_df$percent_change_frequency$group == "acute"]) # p = 0.3519
shapiro.test(summary_sEPSC_df$percent_change_frequency$t25to30[summary_sEPSC_df$percent_change_frequency$group == "acute"]) # p = 0.3697


# HoV
leveneTest(t0to5 ~ group, data = summary_sEPSC_df$percent_change_frequency) # p = 0.8587
leveneTest(t25to30 ~ group, data = summary_sEPSC_df$percent_change_frequency) # p = 0.616

# running the t-test
t.test(summary_sEPSC_df$percent_change_frequency$t0to5[summary_sEPSC_df$percent_change_frequency$group == "naive"], summary_sEPSC_df$percent_change_frequency$t0to5[summary_sEPSC_df$percent_change_frequency$group == "acute"], paired = FALSE, var.equal = TRUE) # sEPSC amplitude does not significantly differ at baseline between naive and acute (p = 0.711)

t.test(summary_sEPSC_df$percent_change_frequency$t25to30[summary_sEPSC_df$percent_change_frequency$group == "naive"], summary_sEPSC_df$percent_change_frequency$t25to30[summary_sEPSC_df$percent_change_frequency$group == "acute"], paired = FALSE, var.equal = TRUE) # sEPSC amplitude does not significantly differ at baseline between naive and acute (p = 0.5186)
```

## Amplitude plots
```{r}
sEPSC_amp_baseline_plot <- summary_sEPSC_df$percent_change_amplitude %>%
  filter(group %in% c("naive", "acute")) %>%
  mutate(group = factor(group, levels = c("naive", "acute"))) %>%
  
  ggplot(aes(x = group, y = t0to5)) +
  
  # boxplot
  geom_boxplot(aes(fill = group),
               alpha = 0.6, 
               color = "black",
               outlier.shape = NA,
               width = 0.5,
               show.legend = FALSE) +
  
  # sina 
  geom_sina(aes(color = group),
            max_width = 0.2,
            shape = 16,
            size = 2,
            show.legend = FALSE) +
  
  # significance bracket
  geom_signif(
    comparisons = list(c("naive", "acute")),
    map_signif_level = TRUE,
    annotations = "ns",  
    y_position = max(summary_sEPSC_df$percent_change_amplitude$t0to5) * 1.05,
    tip_length = 0.02,
    textsize = 5 # 5 when ns, 7 when *
  ) +
  
  # colours
  scale_fill_manual(values = c("naive" = "#f5e0b3", "acute" = "#f19cac")) +
  scale_color_manual(values = c("naive" = "#ecc479", "acute" = "#eb647e")) +
  
  # axes labels
  labs(x = NULL, y = "Baseline sEPSC Amplitude (pA)") +
  scale_x_discrete(labels = c("naive" = "Naive", "acute" = "Acute")) +
  
  scale_y_continuous(expand = expansion(mult = c(0.2, 0.2))) +
  
  patchclampplotteR_theme()

sEPSC_amp_baseline_plot
```
```{r}
sEPSC_amp_HFS_plot <- summary_sEPSC_df$percent_change_amplitude %>%
  filter(group %in% c("naive", "acute")) %>%
  mutate(group = factor(group, levels = c("naive", "acute"))) %>%
  
  ggplot(aes(x = group, y = t25to30)) +
  
  # boxplot
  geom_boxplot(aes(fill = group),
               alpha = 0.6, 
               color = "black",
               outlier.shape = NA,
               width = 0.5,
               show.legend = FALSE) +
  
  # sina 
  geom_sina(aes(color = group),
            max_width = 0.2,
            shape = 16,
            size = 2,
            show.legend = FALSE) +
  
  # significance bracket
  geom_signif(
    comparisons = list(c("naive", "acute")),
    map_signif_level = TRUE,
    annotations = "ns",  
    y_position = max(summary_sEPSC_df$percent_change_amplitude$t25to30) * 1.05,
    tip_length = 0.02,
    textsize = 5 # 5 when ns, 7 when *
  ) +
  
  # colours
  scale_fill_manual(values = c("naive" = "#f5e0b3", "acute" = "#f19cac")) +
  scale_color_manual(values = c("naive" = "#ecc479", "acute" = "#eb647e")) +
  
  # axes labels
  labs(x = NULL, y = "Final sEPSC Amplitude (pA)") +
  scale_x_discrete(labels = c("naive" = "Naive", "acute" = "Acute")) +
  
  scale_y_continuous(expand = expansion(mult = c(0.2, 0.2))) +
  
  patchclampplotteR_theme()

sEPSC_amp_HFS_plot
```

## Frequency plots
```{r}
sEPSC_freq_baseline_plot <- summary_sEPSC_df$percent_change_frequency %>%
  filter(group %in% c("naive", "acute")) %>%
  mutate(group = factor(group, levels = c("naive", "acute"))) %>%
  
  ggplot(aes(x = group, y = t0to5)) +
  
  # boxplot
  geom_boxplot(aes(fill = group),
               alpha = 0.6, 
               color = "black",
               outlier.shape = NA,
               width = 0.5,
               show.legend = FALSE) +
  
  # sina 
  geom_sina(aes(color = group),
            max_width = 0.2,
            shape = 16,
            size = 2,
            show.legend = FALSE) +
  
  # significance bracket
  geom_signif(
    comparisons = list(c("naive", "acute")),
    map_signif_level = TRUE,
    annotations = "ns",  
    y_position = max(summary_sEPSC_df$percent_change_frequency$t0to5) * 1.05,
    tip_length = 0.02,
    textsize = 5 # 5 when ns, 7 when *
  ) +
  
  # colours
  scale_fill_manual(values = c("naive" = "#f5e0b3", "acute" = "#f19cac")) +
  scale_color_manual(values = c("naive" = "#ecc479", "acute" = "#eb647e")) +
  
  # axes labels
  labs(x = NULL, y = "Baseline sEPSC Frequency (Hz)") +
  scale_x_discrete(labels = c("naive" = "Naive", "acute" = "Acute")) +
  
  scale_y_continuous(expand = expansion(mult = c(0.2, 0.2))) +
  
  patchclampplotteR_theme()

sEPSC_freq_baseline_plot
```

```{r}
sEPSC_freq_HFS_plot <- summary_sEPSC_df$percent_change_frequency %>%
  filter(group %in% c("naive", "acute")) %>%
  mutate(group = factor(group, levels = c("naive", "acute"))) %>%
  
  ggplot(aes(x = group, y = t25to30)) +
  
  # boxplot
  geom_boxplot(aes(fill = group),
               alpha = 0.6, 
               color = "black",
               outlier.shape = NA,
               width = 0.5,
               show.legend = FALSE) +
  
  # sina 
  geom_sina(aes(color = group),
            max_width = 0.2,
            shape = 16,
            size = 2,
            show.legend = FALSE) +
  
  # significance bracket
  geom_signif(
    comparisons = list(c("naive", "acute")),
    map_signif_level = TRUE,
    annotations = "ns",  
    y_position = max(summary_sEPSC_df$percent_change_frequency$t25to30) * 1.05,
    tip_length = 0.02,
    textsize = 5 # 5 when ns, 7 when *
  ) +
  
  # colours
  scale_fill_manual(values = c("naive" = "#f5e0b3", "acute" = "#f19cac")) +
  scale_color_manual(values = c("naive" = "#ecc479", "acute" = "#eb647e")) +
  
  # axes labels
  labs(x = NULL, y = "Final sEPSC Frequency (Hz)") +
  scale_x_discrete(labels = c("naive" = "Naive", "acute" = "Acute")) +
  
  scale_y_continuous(expand = expansion(mult = c(0.2, 0.2))) +
  
  patchclampplotteR_theme()

sEPSC_freq_HFS_plot
```
