---
title: "honours"
output: html_document
date: "2025-05-07"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r eval=FALSE}
pak::pak("christelinda-laureijs/patchclampplotteR")
```
## Libraries
libraries I might need
```{r}
library(patchclampplotteR)
library(dplyr)
library(ggplot2)
library(ggsignif)
library(ggtext)
library(ggforce)
library(ggpubr)
library(here)
library(car)
library(ez)
library(lme4)
library(lmerTest)
library(tidyr)
```

## Importing Data
Importing Cell Characteristics
```{r}
cell_characteristics <- import_cell_characteristics_df("Data/Cell-Characteristics.csv")

cell_characteristics
```

Importing Sheet with Raw Evoked Current Data
```{r}
eEPSC_data <- read.csv("Data/new_raw_eEPSC.csv")

eEPSC_data
```

### Raw eEPSC
To Append New Data onto the EXISTING SHEET (raw_eEPSC_df.csv) after first time
```{r eval=FALSE}
# will not run if there is nothing new in "new_raw_eEPSC.csv" so if you put new data directly into "raw_eEPSC_df.csv", it won't run
add_new_cells(
  new_raw_data_csv = "Data/new_raw_eEPSC.csv", # should ONLY have the new data you want
  cell_characteristics_csv = "Data/Cell-Characteristics.csv",
  old_raw_data_csv = "Data/raw_eEPSC_df.csv",
  data_type = "eEPSC",
  write_new_csv = "yes",
  new_file_name = "Data/raw_eEPSC_df.csv", # will overwrite the current version of this file
  decimal_places = 2
)

# once successful, go delete the data from "new_raw_eEPSC.csv" so that you don't get a duplication error the next time you are adding data to the raw_eEPSC_df.
```

Look at the data frame
```{r}
raw_eEPSC_df <- read.csv(here("Data/raw_eEPSC_df.csv")) # puts it in the environment
```

### AP Count
Importing NEW Action Potential Count Data
```{r eval=FALSE}
add_new_cells(
  new_raw_data_csv = "Data/new_AP_count.csv", # should ONLY have the new data you want
  cell_characteristics_csv = "Data/Cell-Characteristics.csv",
  old_raw_data_csv = "Data/AP_count_data.csv", # current data
  data_type = "AP_count",
  write_new_csv = "yes",
  new_file_name = "Data/AP_count_data.csv", # will add to this and overwrite the current version of this file
  decimal_places = 2,
  injection_start_time = 265.4,
  length_of_current_injection = 0.5
)
```
```{r}
AP_count_data <- read.csv(here("Data/AP_count_data.csv"))
```

### AP Parameters
Importing NEW Action Potential Parameter Data
```{r eval=FALSE}
add_new_cells(
  new_raw_data_csv = "Data/new_AP_parameters.csv", # should ONLY have the new data you want,
  cell_characteristics_csv = "Data/Cell-Characteristics.csv",
  old_raw_data_csv = "Data/AP_parameters.csv", # current data
  data_type = "AP_parameter",
  write_new_csv = "yes",
  new_file_name = "Data/AP_parameters.csv", # will add to this and overwrite the current version of this file (same as current data)
  decimal_places = 2,
  injection_start_time = 265.4,
  length_of_current_injection = 0.5
)
```
```{r}
AP_data <- read.csv(here("Data/AP_parameters.csv"))
```

```{r}
# adding group column
AP_data <- AP_data %>%
  mutate(group = case_when(
    category == 1 & treatment == "Control" ~ "naive",
    category == 2 & treatment == "Control" ~ "acute",
    category == 2 & treatment == "AM251" ~ "AM251",
    category == 3 & treatment == "Control" ~ "repeated",
    category == 1 & treatment == "Cort" ~ "cort",
  )) %>%
  mutate(group = factor(group, levels = c("naive", "acute", "AM251", "repeated", "cort")))
```


## Theme and Colour Options
defining my colour theme
```{r}
my_theme_colours <- data.frame(
  category = c(1, 2, 3, 2, 1),
    treatment = c("Control", "Control", "Control", "AM251", "Cort"),
  display_names = c("Naive", "Acute", "Repeated", "Acute with AM251", "Naive with Corticosterone"),
  colours = c("#ecc479", "#eb647e", "#005b96", "#C11C84", "#6aa84f"),
  very_pale_colours = c("#f5e0b3", "#f19cac", "#6497b1", "#FFADFF","#93c47d")
)
```

editing my theme options
```{r}
library(tibble)

my_theme_options <- read.csv("Data/my_custom_theme_options.csv") %>%
  remove_rownames() %>%
  column_to_rownames(var = "option")
```

## How many cells, and how long are they?
```{r}
# acute
raw_eEPSC_df %>%
  filter(category == 2) %>%
  filter(time == 0) %>%
  group_by(treatment) %>%
  count(sex) %>%
  arrange(treatment, sex)
```
```{r}
# naive
raw_eEPSC_df %>%
  filter(category == 1) %>%
  filter(time == 0) %>%
  group_by(treatment) %>%
  count(sex) %>%
  arrange(treatment, sex)
```
```{r}
# repeated
raw_eEPSC_df %>%
  filter(category == 3) %>%
  filter(time == 0) %>%
  group_by(treatment) %>%
  count(sex) %>%
  arrange(treatment, sex)
```

Length of Cells
```{r}
raw_eEPSC_df %>%
  group_by(letter) %>%
  summarize(max_time = max(time))
```

## Raw Plots per Cell
Normalizing Data:
```{r}
normalized_raw_eEPSC_df <- make_normalized_EPSC_data(
  filename = "Data/raw_eEPSC_df.csv",
  current_type = "eEPSC",
  min_time_value = 0,
  max_time_value = 30,
  interval_length = 5,
  baseline_length = 5,
  negative_transform_currents = "yes" # because the raw amplitudes are negative
)
```

Raw ACUTE Plots for each cell:
```{r eval=FALSE}
raw_eEPSC_acute_plots <- plot_raw_current_data(
 data = normalized_raw_eEPSC_df, # why are RMA3 and RMA4 not showing up (May 2025)
 # no longer filtering bad cells RMA5 and RMA7 (2025/6/16)
  plot_treatment = "Control", # RMA3 and RMA4 were not showing up because they had "control" instead of "Control" and "female" instead of "Female" (May 2025)
  plot_category = 2, # 2 is acute restraint, 1 is naive
  current_type = "eEPSC",
  y_variable = "P1",
  pruned = "no",
  hormone_added = "HFS",
  hormone_or_HFS_start_time = 5,
  theme_options = my_theme_options,
  treatment_colour_theme = my_theme_colours
)

 raw_eEPSC_acute_plots
```
Raw ACUTE Plots for each cell with AM251:
```{r eval=FALSE}
raw_eEPSC_acute_plots_AM251 <- plot_raw_current_data(
 data = normalized_raw_eEPSC_df,
  plot_treatment = "AM251",
  plot_category = 2, # 2 is acute restraint, 1 is naive
  current_type = "eEPSC",
  y_variable = "P1",
  pruned = "no",
  hormone_added = "HFS",
  hormone_or_HFS_start_time = 5,
  theme_options = my_theme_options,
  treatment_colour_theme = my_theme_colours
)

 raw_eEPSC_acute_plots_AM251

```

Raw Naive Plots for each cell:
```{r eval=FALSE}
raw_eEPSC_naive_plots <- plot_raw_current_data(
 data = normalized_raw_eEPSC_df,
  plot_treatment = "Control",
  plot_category = 1,
  current_type = "eEPSC",
  y_variable = "P1",
  pruned = "no",
  hormone_added = "HFS",
  hormone_or_HFS_start_time = 5,
  theme_options = my_theme_options,
  treatment_colour_theme = my_theme_colours
)

 raw_eEPSC_naive_plots

# remove the title ("Recording LS10") and subtitle ("Treatment: Control Sex: Female")
# LS10_plot <- raw_eEPSC_naive_plots$LS10 + theme(plot.subtitle = element_blank(), plot.title = element_blank())

# LS10_plot

#fixing the y-axis
# LS10_final_plot <- LS10_plot + ylim(0,550)

# LS10_final_plot

# saving as png to figure folder
#ggsave(LS10_final_plot, path = here("Figures"), file = "LS10_final_plot.png", width = 7, height = 5, units = "in", dpi = 300)
```

Raw REPEATED Plots for each cell:
```{r}
raw_eEPSC_repeated_plots <- plot_raw_current_data(
 data = normalized_raw_eEPSC_df, # why are RMA3 and RMA4 not showing up (May 2025)
 # no longer filtering bad cells RMA5 and RMA7 (2025/6/16)
  plot_treatment = "Control", # RMA3 and RMA4 were not showing up because they had "control" instead of "Control" and "female" instead of "Female" (May 2025)
  plot_category = 3, # 3 is repeated, 2 is acute restraint, 1 is naive
  current_type = "eEPSC",
  y_variable = "P1",
  pruned = "no",
  hormone_added = "HFS",
  hormone_or_HFS_start_time = 5,
  theme_options = my_theme_options,
  treatment_colour_theme = my_theme_colours
)

 raw_eEPSC_repeated_plots
```

```{r eval=FALSE}
raw_eEPSC_cort_plots <- plot_raw_current_data(
 data = normalized_raw_eEPSC_df, 
  plot_treatment = "Cort", 
  plot_category = 1, 
  current_type = "eEPSC",
  y_variable = "P1",
  pruned = "no",
  hormone_added = "HFS",
  hormone_or_HFS_start_time = 5,
  theme_options = my_theme_options,
  treatment_colour_theme = my_theme_colours
)

 raw_eEPSC_cort_plots
```


## Pruned Plots per Cell
Prune full cells from the normalized raw data: FOR FULL CELLS ONLY
```{r}
# pruning averages data per minute

pruned_eEPSC_df <- make_pruned_EPSC_data(
  data = normalized_raw_eEPSC_df,
  current_type = "eEPSC",
  min_time_value = 0, 
  max_time_value = 30,
  baseline_length = 5, 
  interval_length = 1
)

pruned_eEPSC_df$individual_cells
```

```{r}
# all cells
all_pruned_eEPSC_df <- make_pruned_EPSC_data(
  data = normalized_raw_eEPSC_df,
  current_type = "eEPSC",
  min_time_value = 0,
  max_time_value = 30,
  baseline_length = 5,
  interval_length = 1
)

all_pruned_eEPSC_df$individual_cells
```


Plot Pruned NAIVE Data
```{r eval=FALSE}
pruned_eEPSC_naive_plots <- plot_raw_current_data(
  data = pruned_eEPSC_df$individual_cells,
  plot_treatment = "Control",
  plot_category = 1,
  current_type = "eEPSC",
  y_variable = "mean_P1",
  pruned = "yes",
  hormone_added = "HFS",
  hormone_or_HFS_start_time = 5,
  theme_options = my_theme_options,
  treatment_colour_theme = my_theme_colours
)

pruned_eEPSC_naive_plots
```
Plot Pruned ACUTE Data
```{r eval=FALSE}
pruned_eEPSC_acute_plots <- plot_raw_current_data(
  data = pruned_eEPSC_df$individual_cells,
  plot_treatment = "Control",
  plot_category = 2,
  current_type = "eEPSC",
  y_variable = "mean_P1",
  pruned = "yes",
  hormone_added = "HFS",
  hormone_or_HFS_start_time = 5,
  theme_options = my_theme_options,
  treatment_colour_theme = my_theme_colours
)

pruned_eEPSC_acute_plots
```


Plot Pruned ACUTE Data with AM251
```{r eval=FALSE}
pruned_eEPSC_acute_plots_AM251 <- plot_raw_current_data(
  data = pruned_eEPSC_df$individual_cells,
  plot_treatment = "AM251",
  plot_category = 2,
  current_type = "eEPSC",
  y_variable = "mean_P1",
  pruned = "yes",
  hormone_added = "HFS",
  hormone_or_HFS_start_time = 5,
  theme_options = my_theme_options,
  treatment_colour_theme = my_theme_colours
)

pruned_eEPSC_acute_plots_AM251
```
Plot Pruned REPEATED Data
```{r eval=FALSE}
pruned_eEPSC_repeated_plots <- plot_raw_current_data(
  data = pruned_eEPSC_df$individual_cells,
  plot_treatment = "Control",
  plot_category = 3,
  current_type = "eEPSC",
  y_variable = "mean_P1",
  pruned = "yes",
  hormone_added = "HFS",
  hormone_or_HFS_start_time = 5,
  theme_options = my_theme_options,
  treatment_colour_theme = my_theme_colours
)

pruned_eEPSC_repeated_plots

# MR11, MR12, maybe MR7 baselines might be questionable
```

```{r eval=FALSE}
pruned_eEPSC_cort_plots <- plot_raw_current_data(
  data = pruned_eEPSC_df$individual_cells,
  plot_treatment = "Cort",
  plot_category = 1,
  current_type = "eEPSC",
  y_variable = "mean_P1",
  pruned = "yes",
  hormone_added = "HFS",
  hormone_or_HFS_start_time = 5,
  theme_options = my_theme_options,
  treatment_colour_theme = my_theme_colours
)

pruned_eEPSC_cort_plots
```


## Summary Plots
Summary DATA
```{r}
summary_eEPSC_df <- make_summary_EPSC_data(
  data = normalized_raw_eEPSC_df, # not pruned
  current_type = "eEPSC",
  save_output_as_RDS = "no",
  baseline_interval = "t0to5",
  ending_interval = "t25to30"
)
summary_eEPSC_df # what I will use in my summary data stuff and plots from now on

# gives percent change, mean, and SE

# Summary Plots (use PRUNED data, for visual ease, but t-tests are done with the SUMMARY data)

# Category 1 is naive, 2 is acute
```


Summary Plots (use PRUNED data, for visual ease)
### summary plots
Naive FEMALE Summary: (only FULL)
```{r}
naive_summary_plot <- plot_summary_current_data(
  data = pruned_eEPSC_df$all_cells,
  plot_category = 1,
  plot_treatment = "Control",
  current_type = "eEPSC",
  y_variable = "amplitude",
  hormone_added = "HFS",
  hormone_or_HFS_start_time = 5,
  included_sexes = "female",
  include_representative_trace = "no",
  representative_trace_filename = import_ext_data("Control-trace.png"),
  y_axis_limit = 230,
  # signif_stars = "yes",
  geom_signif_text_size = 8,
  t_test_df = NULL,
  large_axis_text = "no",
  legend_position = "inside",
  shade_intervals = "no",
  treatment_colour_theme = my_theme_colours,
  theme_options = my_theme_options,
  save_plot_png = "no"
) #+ theme(legend.position = "none")

naive_summary_plot

# saving as png to figure folder
# ggsave(naive_summary_plot, path = here("Figures"), file = "naive_summary_plot.png", width = 7, height = 5, units = "in", dpi = 300)
```

Naive MALE Summary:
```{r}
male_naive_summary_plot <- plot_summary_current_data(
  data = pruned_eEPSC_df$all_cells,
  plot_category = 1,
  plot_treatment = "Control",
  current_type = "eEPSC",
  y_variable = "amplitude",
  hormone_added = "HFS",
  hormone_or_HFS_start_time = 5,
  included_sexes = "male",
  include_representative_trace = "no",
  representative_trace_filename = import_ext_data("Control-trace.png"),
  y_axis_limit = 230,
  # signif_stars = "yes",
  geom_signif_text_size = 8,
  t_test_df = NULL,
  large_axis_text = "no",
  legend_position = "inside",
  shade_intervals = "no",
  treatment_colour_theme = my_theme_colours,
  theme_options = my_theme_options,
  save_plot_png = "no"
) #+ theme(legend.position = "none")

male_naive_summary_plot

# ggsave(male_naive_summary_plot, path = here("Figures"), file = "male_naive_summary_plot.png", width = 7, height = 5, units = "in", dpi = 300)
```

Acute FEMALE Summary: (only FULL)
```{r}
acute_summary_plot <- plot_summary_current_data(
  data = pruned_eEPSC_df$all_cells, 
  plot_category = 2,
  plot_treatment = "Control",
  current_type = "eEPSC",
  y_variable = "amplitude",
  hormone_added = "HFS",
  hormone_or_HFS_start_time = 5,
  included_sexes = "female",
  include_representative_trace = "no",
  representative_trace_filename = "Figures/Representative-Traces/acute_trace.png",
  y_axis_limit = 230,
  # signif_stars = "yes",
  geom_signif_text_size = 8,
  t_test_df = NULL, 
  large_axis_text = "no",
  legend_position = "inside",
  shade_intervals = "no",
  treatment_colour_theme = my_theme_colours,
  theme_options = my_theme_options,
  save_plot_png = "no"
) # + theme(legend.position = "none") # keeping this hashed out keeps the n = # label in

acute_summary_plot

# saving as png to figure folder
# ggsave(acute_summary_plot, path = here("Figures"), file = "acute_summary_plot.png", width = 7, height = 5, units = "in", dpi = 300)
```

FEMALE TREATMENT 1 COMBINED (only FULL)
```{r}
female_treatment1_plot <- pruned_eEPSC_df$all_cells %>%
  filter(sex == "Female" & category %in% c(1,2) & treatment == "Control") %>%
  ggplot(aes(x = time, y = mean_P1_all_cells, ymin = mean_P1_all_cells - se_P1_all_cells, ymax = mean_P1_all_cells + se_P1_all_cells, colour = category)) +
  geom_pointrange(size = 0.9, shape = 16) +
  ylim(0,230) +
  labs(x = "Time (min)", y = "eEPSC Amplitude (% Baseline)", colour = NULL) + # NULL for legend heading
  geom_hline(yintercept = 100, linetype = "dashed") +
  scale_colour_manual(values = c("lightgrey", "#f19cac"), labels = c("Naive, n = 10", "Acute, n = 8")) + 
  
  # add HFS text
  annotate(
        geom = "text",
        x = 5,
        y = 220,
        label = "HFS",
        size = 4,
        hjust = 0.5
      ) +
  
  # add arrow
   annotate(
        geom = "segment",
        x = 5,
        y = 210,
        xend = 5,
        yend = 190,
        arrow = grid::arrow(type = "closed", length = grid::unit(0.02, "npc"))
      ) +
  patchclampplotteR_theme() +
  theme(
    legend.position = "inside",
    legend.position.inside = c(0.025, 0.05),
    legend.justification = c(0, 0)
  )

female_treatment1_plot

# ggsave(female_treatment1_plot, path = here("Figures"), file = "female_treatment1_plot.png", width = 7, height = 5, units = "in", dpi = 300)
```

```{r}
female_stress_plot <- pruned_eEPSC_df$all_cells %>%
  filter(sex == "Female" & category %in% c(1,2,3) & treatment %in% c("Control","AM251")) %>%
  ggplot(aes(x = time, 
             y = mean_P1_all_cells, 
             ymin = mean_P1_all_cells - se_P1_all_cells, 
             ymax = mean_P1_all_cells + se_P1_all_cells, 
             colour = interaction(category, treatment))) +
  
  geom_pointrange(size = 0.9, shape = 16) +
  ylim(0,230) +
  labs(x = "Time (min)", y = "eEPSC Amplitude (% Baseline)", colour = NULL) + # NULL for legend heading
  geom_hline(yintercept = 100, linetype = "dashed") +
 
   scale_colour_manual(
    values = c(
      "1.Control" = "#f5e0b3",
      "2.Control" = "#f19cac",
      "2.AM251"   = "#FFADFF",
      "3.Control" = "#6497b1"
    ),
    breaks = c(
      "1.Control",
      "2.Control",
      "2.AM251",
      "3.Control"
    ),
    labels = c(
      "1.Control" = "Naive, n = 10",
      "2.Control" = "Acute, n = 8",
      "2.AM251"   = "Acute with AM251, n = 10",
      "3.Control" = "Repeated, n = 9"
    )
  ) +
  
  # add HFS text
  annotate(
        geom = "text",
        x = 5,
        y = 220,
        label = "HFS",
        size = 4,
        hjust = 0.5
      ) +
  
  # add arrow
   annotate(
        geom = "segment",
        x = 5,
        y = 210,
        xend = 5,
        yend = 190,
        arrow = grid::arrow(type = "closed", length = grid::unit(0.02, "npc"))
      ) +
  patchclampplotteR_theme() +
  
  theme(
    legend.position = "right",
    #legend.position.inside = c(0.025, 0.05),
    #legend.justification = c(0, 0)
  )

female_stress_plot

# ggsave(female_stress_plot, path = here("Figures"), file = "female_stress_plot.png", width = 9, height = 5, units = "in", dpi = 300)
```


MALE TREATMENT 1 COMBINED
```{r}
male_treatment1_plot <- pruned_eEPSC_df$all_cells %>%
  filter(sex == "Male" & category %in% c(1,2) & treatment == "Control") %>%
  
  ggplot(aes(x = time, y = mean_P1_all_cells, ymin = mean_P1_all_cells - se_P1_all_cells, ymax = mean_P1_all_cells + se_P1_all_cells, colour = category)) +
  geom_pointrange(size = 0.9, shape = 17) +
  ylim(0,230) +
  labs(x = "Time (min)", y = "eEPSC Amplitude (% Baseline)", colour = NULL) + # NULL for legend heading
  geom_hline(yintercept = 100, linetype = "dashed") +
  scale_colour_manual(values = c("lightgrey", "#f19cac"), labels = c("Naive, n = 13", "Acute, n = 8")) +
  
 # add HFS text
  annotate(
        geom = "text",
        x = 5,
        y = 220,
        label = "HFS",
        size = 4,
        hjust = 0.5
      ) +
  
  # add arrow  
  annotate(
        geom = "segment",
        x = 5,
        y = 210,
        xend = 5,
        yend = 190,
        arrow = grid::arrow(type = "closed", length = grid::unit(0.02, "npc"))
      ) +
  
  patchclampplotteR_theme() +
  theme(
    legend.position = "inside",
    legend.position.inside = c(0.025, 0.05),
    legend.justification = c(0, 0)
  )

male_treatment1_plot

# ggsave(male_treatment1_plot, path = here("Figures"), file = "male_treatment1_plot.png", width = 7, height = 5, units = "in", dpi = 300)
```


Acute FEMALE Summary with AM251: (only FULL)
```{r eval = FALSE}
# Christelinda's package
am251_acute_summary_plot <- plot_summary_current_data(
  data = pruned_eEPSC_df$all_cells, 
  plot_category = 2,
  plot_treatment = "AM251",
  current_type = "eEPSC",
  y_variable = "amplitude",
  hormone_added = "HFS",
  hormone_or_HFS_start_time = 5,
  included_sexes = "female",
  include_representative_trace = "no",
  representative_trace_filename = import_ext_data("Control-trace.png"),
  y_axis_limit = 230,
  # signif_stars = "yes",
  geom_signif_text_size = 8,
  t_test_df = NULL, 
  large_axis_text = "no",
  legend_position = "inside",
  shade_intervals = "no",
  treatment_colour_theme = my_theme_colours,
  theme_options = my_theme_options,
  save_plot_png = "no"
) #+ theme(legend.position = "none") keeping this hashed out keeps the n = # label in

am251_acute_summary_plot

# ggsave(am251_acute_summary_plot, path = here("Figures"), file = "am251_acute_summary_plot.png", width = 7, height = 5, units = "in", dpi = 300)
```
```{r}
female_am251_summary_plot <- pruned_eEPSC_df$all_cells %>%
  filter(sex == "Female",
         category == 2,
         treatment == "AM251") %>%
  ggplot(aes(x = time,
             y = mean_P1_all_cells,
             ymin = mean_P1_all_cells - se_P1_all_cells,
             ymax = mean_P1_all_cells + se_P1_all_cells,
             colour = "AM251")) +
  
  geom_pointrange(size = 0.9, shape = 16) +
  ylim(0, 230) +
  labs(x = "Time (min)", y = "eEPSC Amplitude (% Baseline)", colour = NULL) +
  geom_hline(yintercept = 100, linetype = "dashed") +
  
  scale_colour_manual(
    values = c("AM251" = "#FFADFF"),
    labels = c("AM251" = "Acute with AM251, n = 10")
  ) +
  
  annotate(
    geom = "text",
    x = 5,
    y = 220,
    label = "HFS",
    size = 4,
    hjust = 0.5
  ) +
  
  annotate(
    geom = "segment",
    x = 5,
    y = 210,
    xend = 5,
    yend = 190,
    arrow = grid::arrow(type = "closed", length = grid::unit(0.02, "npc"))
  ) +
  
  patchclampplotteR_theme() +
  theme(
    legend.position = "inside",
    legend.position.inside = c(0.025, 0.05),
    legend.justification = c(0, 0)
  )

female_am251_summary_plot

# ggsave(female_am251_summary_plot, path = here("Figures"), file = "female_am251_summary_plot.png", width = 7, height = 5, units = "in", dpi = 300)
```


REPEATED FEMALE Summary: (only FULL)
```{r eval = FALSE}
# Christelinda's package
repeated_summary_plot <- plot_summary_current_data(
  data = pruned_eEPSC_df$all_cells, 
  plot_category = 3,
  plot_treatment = "Control",
  current_type = "eEPSC",
  y_variable = "amplitude",
  hormone_added = "HFS",
  hormone_or_HFS_start_time = 5,
  included_sexes = "female",
  include_representative_trace = "no",
  representative_trace_filename = import_ext_data("Control-trace.png"),
  y_axis_limit = 230,
  # signif_stars = "yes",
  geom_signif_text_size = 8,
  t_test_df = NULL, 
  large_axis_text = "no",
  legend_position = "inside",
  shade_intervals = "no",
  treatment_colour_theme = my_theme_colours,
  theme_options = my_theme_options,
  save_plot_png = "no"
) #+ theme(legend.position = "none") keeping this hashed out keeps the n = # label in

repeated_summary_plot

# ggsave(repeated_summary_plot, path = here("Figures"), file = "repeated_summary_plot.png", width = 7, height = 5, units = "in", dpi = 300)
```
```{r}
female_repeated_summary_plot <- pruned_eEPSC_df$all_cells %>%
  filter(sex == "Female",
         category == 3,
         treatment == "Control") %>%
  ggplot(aes(x = time,
             y = mean_P1_all_cells,
             ymin = mean_P1_all_cells - se_P1_all_cells,
             ymax = mean_P1_all_cells + se_P1_all_cells,
             colour = "repeated")) +
  
  geom_pointrange(size = 0.9, shape = 16) +
  ylim(0, 230) +
  labs(x = "Time (min)", y = "eEPSC Amplitude (% Baseline)", colour = NULL) +
  geom_hline(yintercept = 100, linetype = "dashed") +
  
  scale_colour_manual(
    values = c("repeated" = "#6497b1"),
    labels = c("repeated" = "Repeated, n = 9")
  ) +
  
  annotate(
    geom = "text",
    x = 5,
    y = 220,
    label = "HFS",
    size = 4,
    hjust = 0.5
  ) +
  
  annotate(
    geom = "segment",
    x = 5,
    y = 210,
    xend = 5,
    yend = 190,
    arrow = grid::arrow(type = "closed", length = grid::unit(0.02, "npc"))
  ) +
  
  patchclampplotteR_theme() +
  theme(
    legend.position = "inside",
    legend.position.inside = c(0.025, 0.05),
    legend.justification = c(0, 0)
  )

female_repeated_summary_plot

# ggsave(female_repeated_summary_plot, path = here("Figures"), file = "female_repeated_summary_plot.png", width = 7, height = 5, units = "in", dpi = 300)
```


REPEATED MALE Summary:
```{r}
male_repeated_summary_plot <- plot_summary_current_data(
  data = pruned_eEPSC_df$all_cells, 
  plot_category = 3,
  plot_treatment = "Control",
  current_type = "eEPSC",
  y_variable = "amplitude",
  hormone_added = "HFS",
  hormone_or_HFS_start_time = 5,
  included_sexes = "male",
  include_representative_trace = "no",
  representative_trace_filename = import_ext_data("Control-trace.png"),
  y_axis_limit = 230,
  # signif_stars = "yes",
  geom_signif_text_size = 8,
  t_test_df = NULL, 
  large_axis_text = "no",
  legend_position = "inside",
  shade_intervals = "no",
  treatment_colour_theme = my_theme_colours,
  theme_options = my_theme_options,
  save_plot_png = "no"
) #+ theme(legend.position = "none") keeping this hashed out keeps the n = # label in

male_repeated_summary_plot

# ggsave(male_repeated_summary_plot, path = here("Figures"), file = "male_repeated_summary_plot.png", width = 7, height = 5, units = "in", dpi = 300)

```


Acute MALE Summary:
```{r}
male_acute_summary_plot <- plot_summary_current_data(
  data = pruned_eEPSC_df$all_cells, 
  plot_category = 2,
  plot_treatment = "Control",
  current_type = "eEPSC",
  y_variable = "amplitude",
  hormone_added = "HFS",
  hormone_or_HFS_start_time = 5,
  included_sexes = "male",
  include_representative_trace = "no",
  representative_trace_filename = import_ext_data("Control-trace.png"),
  y_axis_limit = 230,
  # signif_stars = "yes",
  geom_signif_text_size = 8,
  t_test_df = NULL, 
  large_axis_text = "no",
  legend_position = "inside",
  shade_intervals = "no",
  treatment_colour_theme = my_theme_colours,
  theme_options = my_theme_options,
  save_plot_png = "no"
) #+ theme(legend.position = "none") keeping this hashed out keeps the n = # label in

male_acute_summary_plot

# ggsave(male_acute_summary_plot, path = here("Figures"), file = "male_acute_summary_plot.png", width = 7, height = 5, units = "in", dpi = 300)
```

CORT FEMALE Summary:
```{r}
female_cort_summary_plot <- pruned_eEPSC_df$all_cells %>%
  filter(sex == "Female" & category %in% c(1) & treatment == "Cort") %>%
  ggplot(aes(x = time, y = mean_P1_all_cells, ymin = mean_P1_all_cells - se_P1_all_cells, ymax = mean_P1_all_cells + se_P1_all_cells, colour = category)) +
  geom_pointrange(size = 0.9, shape = 16) +
  ylim(0,230) +
  labs(x = "Time (min)", y = "eEPSC Amplitude (% Baseline)", colour = NULL) + # NULL for legend heading
  geom_hline(yintercept = 100, linetype = "dashed") +
  scale_colour_manual(values = c("#93c47d"), labels = c("Naive with Corticosterone, n = 7")) + 
  
  # add HFS text
  annotate(
        geom = "text",
        x = 5,
        y = 220,
        label = "HFS",
        size = 4,
        hjust = 0.5
      ) +
  
  # add arrow
   annotate(
        geom = "segment",
        x = 5,
        y = 210,
        xend = 5,
        yend = 190,
        arrow = grid::arrow(type = "closed", length = grid::unit(0.02, "npc"))
      ) +
  patchclampplotteR_theme() +
  theme(
    legend.position = "inside",
    legend.position.inside = c(0.025, 0.05),
    legend.justification = c(0, 0)
  )

female_cort_summary_plot

# ggsave(female_cort_summary_plot, path = here("Figures"), file = "female_cort_summary_plot.png", width = 7, height = 5, units = "in", dpi = 300)
```


### overall summary percent change mean and SE for eEPSC
summary data has both full and baseline only cells
```{r}
female_percentchange_eEPSC_summary <- summary_eEPSC_df$percent_change_data %>%
  filter(sex == "Female" & category %in% c(1, 2, 3) & treatment %in% c("Control", "AM251", "Cort")) %>%
  mutate(cat_treat = factor(
    interaction(category, treatment),
    levels = c("1.Control", "2.Control", "2.AM251", "3.Control", "1.Cort")
  )) %>%
  group_by(cat_treat) %>%  
  summarise(
    n = n(),
    mean_percentchange = mean(percent_change, na.rm = TRUE),
    sd_percentchange = sd(percent_change, na.rm = TRUE), 
    se_percentchange = sd_percentchange / sqrt(n), 
    .groups = "drop"  
  )
female_percentchange_eEPSC_summary
```

### eEPSC mean and SE 
```{r}
# baseline
female_baseline_eEPSC_summary <- summary_eEPSC_df$percent_change_data %>%
  filter(sex == "Female" & category %in% c(1, 2, 3) & treatment %in% c("Control", "AM251", "Cort")) %>%
  mutate(cat_treat = factor(
    interaction(category, treatment),
    levels = c("1.Control", "2.Control", "2.AM251", "3.Control", "1.Cort")
  )) %>%
  group_by(cat_treat) %>%  
  summarise(
    n = n(),
    mean_amplitude = mean(t0to5, na.rm = TRUE),
    sd_amplitude = sd(t0to5, na.rm = TRUE), 
    se_amplitude = sd_amplitude / sqrt(n), 
    .groups = "drop"  
  )
female_baseline_eEPSC_summary

# post HFS
female_HFS_eEPSC_summary <- summary_eEPSC_df$percent_change_data %>%
  filter(sex == "Female" & category %in% c(1, 2, 3) & treatment %in% c("Control", "AM251", "Cort") & !(letter %in% c("RMA100A", "RMR100", "RMR101", "RMR102", "RMR103", "RMR104", "RMR105", "RMR106", "RMR107"))) %>% # excluding baseline onlys
  mutate(cat_treat = factor(
    interaction(category, treatment),
    levels = c("1.Control", "2.Control", "2.AM251", "3.Control", "1.Cort")
  )) %>%
  group_by(cat_treat) %>%  
  summarise(
    n = n(),
    mean_amplitude = mean(t25to30, na.rm = TRUE),
    sd_amplitude = sd(t25to30, na.rm = TRUE), 
    se_amplitude = sd_amplitude / sqrt(n), 
    .groups = "drop"  
  )
female_HFS_eEPSC_summary
```

## Baseline eEPSC
```{r}
# data
female_baseline_amp_plot <- summary_eEPSC_df$percent_change_data %>%
  filter(sex == "Female" & category %in% c(1,2, 3) & treatment %in% c("Control","AM251", "Cort")) %>% 
  mutate(cat_treat = factor(
    interaction(category, treatment),
    levels = c("1.Control", "2.Control", "2.AM251", "3.Control", "1.Cort")
  )) %>%
  
  ggplot(aes(x = cat_treat, y = t0to5)) +
  
  patchclampplotteR_theme() +
  
# axis labels
  labs(x = NULL, y = "Baseline eEPSC Amplitude (pA)") +
  patchclampplotteR_theme() +
  
# the boxes
  geom_boxplot(aes(fill = interaction(category, treatment), color = interaction(category, treatment)), 
               alpha = 0.6, 
               color = "black", # get rid of if want the dark colour to be the outline
# outlier.shape = NA stops the box plot from plotting outliers. BUT because the sina plot is a different layer, all outliers are still shown as dots from that.
               outlier.shape = NA, 
               width = 0.5, 
               show.legend = FALSE)  +
  
  # the dots/scatter plot
  geom_sina(aes(x = interaction(category, treatment), color = interaction(category, treatment)), 
            max_width = 0.2, 
            shape = 16, 
            size = 2, 
            show.legend = FALSE) +

  # colours
  scale_fill_manual(values = c("1.Control" = "#f5e0b3",
                               "2.Control" = "#f19cac",
                               "2.AM251" = "#ffadff",
                               "3.Control" = "#6497b1",
                               "1.Cort" = "#93c47d")) +
  
  scale_color_manual(values = c("1.Control" = "#ecc479", 
                                "2.Control" = "#eb647e", 
                                "2.AM251" = "#c11c84",
                                "3.Control" = "#005b96",
                                "1.Cort" = "#6aa84f")) +
  
  # x-axis labels  
scale_x_discrete(labels = c("Naive", "Acute", "Acute with AM251", "Repeated", "Naive with Corticosterone")) +
  
# x-axis subtitles  
  #annotate("text", x = 1, y = -0.2, label = "n = 10", size = 4, hjust = 0.4) + 
  #annotate("text", x = 2, y = -0.2, label = "n = 8", size = 4, hjust = 0.5) + 
  #annotate("text", x = 3, y = -0.2, label = "n = 10", size = 4, hjust = 0.5) +
  
  scale_y_continuous(expand = expansion(mult = c(0.2, .2))) +

  guides(fill = "none", color = "none")

female_baseline_amp_plot

# ggsave(female_baseline_amp_plot, path = here("Figures"), file = "female_baseline_amp_plot.png", width = 7, height = 5, units = "in", dpi = 300)

```



eEPSC amplitude after the HFS (25-30 min)
## post HFS eEPSC (final)
```{r eval=FALSE}}
# data
female_HFS_amp_plot <- summary_eEPSC_df$percent_change_data %>%
  filter(sex == "Female" & category %in% c(1,2, 3) & treatment %in% c("Control","AM251", "Cort") & !(letter %in% c("RMA100A", "RMR100", "RMR101", "RMR102", "RMR103", "RMR104", "RMR105", "RMR106", "RMR107"))) %>% # excluding baseline onlys %>% 
  mutate(cat_treat = factor(
    interaction(category, treatment),
    levels = c("1.Control", "2.Control", "2.AM251", "3.Control", "1.Cort")
  )) %>%
  
  ggplot(aes(x = cat_treat, y = t25to30)) +
  
  patchclampplotteR_theme() +
  
# axis labels
  labs(x = NULL, y = "FINAL eEPSC Amplitude (pA)") +
  patchclampplotteR_theme() +
  
# the boxes
  geom_boxplot(aes(fill = interaction(category, treatment), color = interaction(category, treatment)), 
               alpha = 0.6, 
               color = "black", # get rid of if want the dark colour to be the outline
# outlier.shape = NA stops the box plot from plotting outliers. BUT because the sina plot is a different layer, all outliers are still shown as dots from that.
               outlier.shape = NA, 
               width = 0.5, 
               show.legend = FALSE)  +
  
  # the dots/scatter plot
  geom_sina(aes(x = interaction(category, treatment), color = interaction(category, treatment)), 
            max_width = 0.2, 
            shape = 16, 
            size = 2, 
            show.legend = FALSE) +
  
  # mean as a point
  #stat_summary(fun = mean, geom = "point", 
               #shape = 16, size = 4, color = "black") +
  
  # colours
  scale_fill_manual(values = c("1.Control" = "#f5e0b3",
                               "2.Control" = "#f19cac",
                               "2.AM251" = "#ffadff",
                               "3.Control" = "#6497b1",
                               "1.Cort" = "#93c47d")) +
  
  scale_color_manual(values = c("1.Control" = "#ecc479", 
                                "2.Control" = "#eb647e", 
                                "2.AM251" = "#c11c84",
                                "3.Control" = "#005b96",
                                "1.Cort" = "#6aa84f")) +
  
  # x-axis labels  
scale_x_discrete(labels = c("Naive", "Acute", "Acute with AM251", "Repeated", "Naive with Corticosterone")) +
  
# x-axis subtitles  
  #annotate("text", x = 1, y = -0.2, label = "n = 10", size = 4, hjust = 0.4) + 
  #annotate("text", x = 2, y = -0.2, label = "n = 8", size = 4, hjust = 0.5) + 
  #annotate("text", x = 3, y = -0.2, label = "n = 10", size = 4, hjust = 0.5) +

  
  scale_y_continuous(expand = expansion(mult = c(0.2, .2))) +

  guides(fill = "none", color = "none")

female_HFS_amp_plot
```

## PPR
Make PPR Dataset
includes full cells and baseline only
```{r}
PPR_df <- make_PPR_data(
  data = normalized_raw_eEPSC_df,
  include_all_treatments = "yes",
  list_of_treatments = "yes",
  PPR_min = 0,
  PPR_max = 5,
  baseline_interval = "t0to5",
  treatment_colour_theme = my_theme_colours
)
PPR_df

# adding group colulmn
PPR_df <- PPR_df %>%
  mutate(group = case_when(
    category == 1 & treatment == "Control" ~ "naive",
    category == 2 & treatment == "Control" ~ "acute",
    category == 2 & treatment == "AM251" ~ "AM251",
    category == 3 & treatment == "Control" ~ "repeated",
    category == 1 & treatment == "Cort" ~ "cort"
  )) 
```

```{r}
# cell means
PPR_cell_df <- PPR_df %>%
  group_by(letter, group, state, sex) %>%
  summarise(mean_PPR_cell = mean(PPR, na.rm = TRUE), .groups = "drop")


# BASELINE
# filtering sex and state
female_baseline_PPR_df <- PPR_cell_df %>%
  filter(sex == "Female", state == "Baseline") 

# getting the mean and se...
female_baseline_PPR_summary_df <- female_baseline_PPR_df %>%
  group_by(group) %>%
  summarise(
    n = n(),
    mean_PPR = mean(mean_PPR_cell, na.rm = TRUE),
    sd_PPR = sd(mean_PPR_cell, na.rm = TRUE),
    se_PPR = sd_PPR / sqrt(n),
    .groups = "drop"
  )
female_baseline_PPR_summary_df

# HFS
# filtering and adding group column
female_HFS_PPR_df <- PPR_cell_df %>%
  filter(sex == "Female", state == "Post-modification") 

# getting the mean and se...
female_HFS_PPR_summary_df <- female_HFS_PPR_df %>%
  group_by(group) %>%
  summarise(
    n = n(),
    mean_PPR = mean(mean_PPR_cell, na.rm = TRUE),
    sd_PPR = sd(mean_PPR_cell, na.rm = TRUE),
    se_PPR = sd_PPR / sqrt(n),
    .groups = "drop"
  )
female_HFS_PPR_summary_df


# only paired letters (for change over time)
female_paired_PPR_df <- PPR_cell_df %>%
  filter(sex == "Female", state %in% c("Baseline", "Post-modification")) %>%
  group_by(letter, group) %>%
  filter(n_distinct(state) == 2) %>%  # only keep letters with both states
  ungroup()
# rename to HFS
female_paired_PPR_df <- female_paired_PPR_df %>%
  mutate(state = ifelse(state == "Post-modification", "HFS", state))
```


female vs male acute PPR HFS
```{r eval=FALSE}
plot_PPR_data_single_treatment(
  data = PPR_df,
  plot_treatment = "Control",
  plot_category = 2,
  baseline_label = "Baseline",
  post_hormone_label = "HFS",
  included_sexes = "both",
  facet_by_sex = "yes",
  left_sex = "Female",
  test_type = "t.test",
  large_axis_text = "no",
  treatment_colour_theme = my_theme_colours,
  theme_options = my_theme_options,
  save_plot_png = "no"
)

# sig increase in the PPR after HFS
# higher PPR means lower probability of release
```

female vs male naive PPR HFS
```{r eval=FALSE}
plot_PPR_data_single_treatment(
  data = PPR_df,
  plot_treatment = "Control",
  plot_category = 1,
  baseline_label = "Baseline",
  post_hormone_label = "HFS",
  included_sexes = "both",
  facet_by_sex = "yes",
  left_sex = "Female",
  test_type = "t.test",
  large_axis_text = "no",
  treatment_colour_theme = my_theme_colours,
  theme_options = my_theme_options,
  save_plot_png = "no"
)
```

female vs male repeated PPR HFS
```{r eval=FALSE}
plot_PPR_data_single_treatment(
  data = PPR_df,
  plot_treatment = "Control",
  plot_category = 3,
  baseline_label = "Baseline",
  post_hormone_label = "HFS",
  included_sexes = "both",
  facet_by_sex = "yes",
  left_sex = "Female",
  test_type = "t.test",
  large_axis_text = "no",
  treatment_colour_theme = my_theme_colours,
  theme_options = my_theme_options,
  save_plot_png = "no"
)
```


### change in PPR female plot
```{r}
#1 group labels
  group_labels <- c(
    "naive" = "Naive",
    "acute" = "Acute",
    "AM251" = "Acute with AM251",
    "repeated" = "Repeated",
    "cort" = "Naive with Corticosterone")


# baseline only cells  
female_baseline_only_PPR_df <- female_baseline_PPR_df %>%
  filter(!(letter %in% female_paired_PPR_df$letter)) %>%  # only letters NOT in paired df
  mutate(state = "Baseline") %>%
  mutate(group = group)

#2 plot
female_PPR_plot <- female_paired_PPR_df %>%
  ggplot(aes(x = state, y = mean_PPR_cell)) + 

# baseline-only cells
  geom_point(data = female_baseline_only_PPR_df,
             aes(x = state, y = mean_PPR_cell),
             shape = 16, size = 1.5, colour = "lightgrey") +
  
# paired individual cells  
  geom_point(aes(shape = sex),size = 1, colour = "lightgrey") + 
  geom_line(aes(group = letter), colour = "lightgrey", alpha = 0.9) + 
  
# group mean + SE
  stat_summary(aes(group = 1, colour = group),
               fun.data = mean_se,
               geom = "line",
               linewidth = 1.2) +
  stat_summary(aes(group = 1,shape = sex,colour = group),
    fun.data = mean_se,
    geom = "point",
    size = 2.5
  ) +  
 
# colours and shapes
  scale_colour_manual(values = c(
    "naive" = "#f5e0b3", # or "darkgrey"
    "acute" = "#f19cac",
    "AM251" = "#FFADFF",
    "repeated" = "#6497b1",
    "cort" = "#93c47d"
  )) +
scale_shape_manual(values = c("Female" = 16, "Male" = 17)) +
  
# facet by group in order
  facet_wrap(~ group, labeller = as_labeller(group_labels), nrow = 1) + # nrow = 1 makes it all on one line
  # want to change order but whatever
  
# add significance brackets
  geom_signif(
    comparisons = list(c("Baseline", "HFS")),
    test = "t.test",
    test.args = list(paired = TRUE),
    map_signif_level = function(p)
        if (p <= 0.0001) {
          return("****")
        } else {
          if (p <= 0.001) {
            return("***")
          } else {
            if (p <= 0.01) {
              return("**")
            } else {
              if (p <= 0.05) {
                return("*")
              } else {
                if (p < 0.1 & p > 0.05) {
                  return(signif(p, 3))
                } else {
                  return("ns")
                }
              }
            }
          }
        }
, # or TRUE for stars, # FALSE for values
    vjust = -0.3,
    textsize = 5,
    size = 0.5,
    margin_top = 0.1,
    extend_line = 0.03
  ) +
  
# expand y-axis so the brackets don't overlap with labels
  scale_y_continuous(expand = expansion(mult = c(0.2, .2))) +
  
# theme and titles
  patchclampplotteR_theme() +
  labs(x = NULL, y = "PPR", title = NULL) +
  theme(legend.position = "none")  # remove legend

female_PPR_plot

# ggsave(female_PPR_plot, path = here("Figures"), file = "female_PPR_plot.png", width = 7, height = 5, units = "in", dpi = 300)
```

### PPR female plot
```{r eval=FALSE}
#1 facet labels
  facet_labels <- c(
    "1.Control.Female" = "Naive",
    "2.Control.Female" = "Acute",
    "2.AM251.Female" = "Acute with AM251",
    "1.Cort.Female" = "Naive with Corticosterone")

#2 making the data frame for individual cells
female_acute_PPR_plot_df <- PPR_df %>%
  filter(state %in% c("Baseline", "Post-modification")) %>% 
  filter(sex == "Female") %>% 
  filter(category %in% c(1,2,3)) %>% # excluding category 3 (repeated), could use category %in% c(1,2) or exclude using filter(category != 3)
  mutate(
    state = ifelse(state == "Post-modification", "HFS", state)) %>% # rename to HFS
 mutate(facet_group = factor(interaction(category, treatment, sex),
                              levels = names(facet_labels))) %>%
  group_by(letter, state, category, treatment, sex, facet_group) %>%
  summarize(mean_PPR_cell = mean(PPR, na.rm = TRUE), .groups = "drop")  
   
#3 plot
female_acute_PPR_plot <- female_acute_PPR_plot_df %>%
  ggplot(aes(x = state, y = mean_PPR_cell)) + 

# individual  cells  
  geom_point(aes(shape = sex),size = 1, colour = "lightgrey") + 
  geom_line(aes(group = letter), colour = "lightgrey", alpha = 0.9) + 
  
# group mean
  stat_summary(aes(group = 1, colour = interaction(category, treatment)),
               fun.data = mean_se,
               geom = "line",
               linewidth = 1.2) +
  
  stat_summary(aes(group = 1,shape = sex,colour = interaction(category, treatment)),
    fun.data = mean_se,
    geom = "point",
    size = 2.5
  ) +   
 
# colours and shapes
  scale_colour_manual(values = c(
    "1.Control" = "#f5e0b3", # or "darkgrey"
    "2.Control" = "#f19cac",
    "2.AM251" = "#FFADFF",
    "3.Control" = "#6497b1",
    "1.Cort" = "#93c47d"
  )) +
scale_shape_manual(values = c("Female" = 16, "Male" = 17)) +
  
# facet with labels and order
  facet_wrap(~ facet_group, labeller = as_labeller(facet_labels), nrow = 1) + # nrow = 1 makes it all on one line
  
# add significance brackets
  geom_signif(
    comparisons = list(c("Baseline", "HFS")),
    test = "t.test",
    test.args = list(paired = TRUE),
    map_signif_level = function(p)
        if (p <= 0.0001) {
          return("****")
        } else {
          if (p <= 0.001) {
            return("***")
          } else {
            if (p <= 0.01) {
              return("**")
            } else {
              if (p <= 0.05) {
                return("*")
              } else {
                if (p < 0.1 & p > 0.05) {
                  return(signif(p, 3))
                } else {
                  return("ns")
                }
              }
            }
          }
        }
, # or TRUE for stars, # FALSE for values
    vjust = -0.3,
    textsize = 5,
    size = 0.5,
    margin_top = 0.1,
    extend_line = 0.03
  ) +
  
# expand y-axis so the brackets don't overlap with labels
  scale_y_continuous(expand = expansion(mult = c(0.2, .2))) +
  
# theme and titles
  patchclampplotteR_theme() +
  labs(x = NULL, y = "PPR", title = NULL) +
  theme(legend.position = "none")  # remove legend

female_acute_PPR_plot

#ggsave(female_acute_PPR_plot, path = here("Figures"), file = "female_acute_PPR_plot.png", width = 7, height = 5, units = "in", dpi = 300)
```

### PPR with ALL SEXES AND TREATMENTS
```{r eval=FALSE}
#1 facet labels
  facet_labels <- c(
    "1.Control.Female" = "Female Naive",
    "1.Control.Male" = "Male Naive",
    "2.Control.Female" = "Female Acute",
    "2.Control.Male" = "Male Acute",
    "2.AM251.Female" = "Acute with AM251",
    "3.Control.Female" = "Female Repeated",
    "3.Control.Male" = "Male Repeated")

#2 making the data frame for individual cells
PPR_plot_df <- PPR_df %>%
  filter(state %in% c("Baseline", "Post-modification")) %>% 
  mutate(
    state = ifelse(state == "Post-modification", "HFS", state)) %>% # rename to HFS
 mutate(facet_group = factor(interaction(category, treatment, sex),
                              levels = names(facet_labels))) %>%
  group_by(letter, state, category, treatment, sex, facet_group) %>%
  summarize(mean_PPR_cell = mean(PPR, na.rm = TRUE), .groups = "drop")  
   
#3 plot
PPR_plot <- PPR_plot_df %>%
  ggplot(aes(x = state, y = mean_PPR_cell)) + 

# individual  cells  
  geom_point(aes(shape = sex),size = 1, colour = "lightgrey") + 
  geom_line(aes(group = letter), colour = "lightgrey", alpha = 0.9) + 
  
# group mean
  stat_summary(aes(group = 1, colour = interaction(category, treatment)),
               fun.data = mean_se,
               geom = "line",
               linewidth = 1.2) +
  
  stat_summary(aes(group = 1,shape = sex,colour = interaction(category, treatment)),
    fun.data = mean_se,
    geom = "point",
    size = 2.5
  ) +  
 
# colours and shapes
  scale_colour_manual(values = c(
    "1.Control" = "#f5e0b3", # or "darkgrey"
    "2.Control" = "#f19cac",
    "2.AM251" = "#FFADFF",
    "3.Control" = "#6497b1"
  )) +
scale_shape_manual(values = c("Female" = 16, "Male" = 17)) +
  
# facet with labels and order
  facet_wrap(~ facet_group, labeller = as_labeller(facet_labels), nrow = 2) +
  
# add significance brackets
  geom_signif(
    comparisons = list(c("Baseline", "HFS")),
    test = "t.test",
    test.args = list(paired = TRUE),
    map_signif_level = function(p)
        if (p <= 0.0001) {
          return("****")
        } else {
          if (p <= 0.001) {
            return("***")
          } else {
            if (p <= 0.01) {
              return("**")
            } else {
              if (p <= 0.05) {
                return("*")
              } else {
                if (p < 0.1 & p > 0.05) {
                  return(signif(p, 3))
                } else {
                  return("ns")
                }
              }
            }
          }
        }
, # or TRUE for stars, # FALSE for values
    vjust = -0.3,
    textsize = 5,
    size = 0.5,
    margin_top = 0.1,
    extend_line = 0.03
  ) +
  
# expand y-axis so the brackets don't overlap with labels
  scale_y_continuous(expand = expansion(mult = c(0.2, .2))) +
  
# theme and titles
  patchclampplotteR_theme() +
  labs(x = NULL, y = "PPR", title = NULL) +
  theme(legend.position = "none")  # remove legend

PPR_plot
```

### PPR baseline visualization
```{r}
# specific group order
group_order <- c("naive", "acute", "AM251", "repeated", "cort")

# colours for groups
light_group_colors <- c(
  "naive" = "#f5e0b3",
  "acute" = "#f19cac",
  "AM251" = "#FFADFF",
  "repeated" = "#6497b1",
  "cort" = "#93c47d"
)

group_colors <- c(
  "naive" = "#ecc479",
  "acute" = "#eb647e",
  "AM251" = "#c11c84",
  "repeated" = "#005b96",
  "cort" = "#6aa84f"
)


# plot baseline PPR for female groups
female_baseline_group_PPR_plot <- female_baseline_PPR_df %>%
  mutate(group = factor(group, levels = group_order)) %>%
  ggplot(aes(x = group, y = mean_PPR_cell)) +

# boxes
  geom_boxplot(aes(fill = group), alpha = 0.6,
               outlier.shape = NA, width = 0.5, show.legend = FALSE,
               color = "black") +

# individual cells as dots (sina plot)
  geom_sina(aes(color = group), max_width = 0.2,
            shape = 16, size = 2, show.legend = FALSE) +

# axis labels
  labs(x = NULL, y = "Baseline Paired Pulse Ratio") +

# group color mapping for boxplot and dots
  scale_fill_manual(values = light_group_colors) +
  scale_color_manual(values = group_colors) +

  # x-axis labels
  scale_x_discrete(labels = c("naive" = "Naive", 
                              "acute" = "Acute", 
                              "AM251" = "Acute with AM251", 
                              "repeated" = "Repeated",
                              "cort" = "Naive with Corticosterone")) +
  # y-axis
    scale_y_continuous(limits = c(0, 3), expand = expansion(mult = c(0, 0.05))) +

  patchclampplotteR_theme() +
  theme(legend.position = "none") 

  
female_baseline_group_PPR_plot

# ggsave(female_baseline_control_PPR_plot, path = here("Figures"), file = "female_baseline_control_PPR_plot.png", width = 7, height = 5, units = "in", dpi = 300)
```
#### anova
```{r}
# HoV
leveneTest(mean_PPR_cell ~ group, data = female_baseline_PPR_df)
# passed

# anova
female_baseline_PPR_anova <- aov(mean_PPR_cell ~ group, data = female_baseline_PPR_df)
summary(female_baseline_PPR_anova)
# not significant

# assumption of normality
female_baseline_PPR_anova_resid <- residuals(female_baseline_PPR_anova)
shapiro.test(female_baseline_PPR_anova_resid)
qqnorm(female_baseline_PPR_anova_resid)
qqline(female_baseline_PPR_anova_resid, col = "red")
# passed
```


### PPR HFS visualization
```{r}
# specific group order
group_order <- c("naive", "acute", "AM251", "repeated", "cort")

# colours for groups
light_group_colors <- c(
  "naive" = "#f5e0b3",
  "acute" = "#f19cac",
  "AM251" = "#FFADFF",
  "repeated" = "#6497b1",
  "cort" = "#93c47d"
)

group_colors <- c(
  "naive" = "#ecc479",
  "acute" = "#eb647e",
  "AM251" = "#c11c84",
  "repeated" = "#005b96",
  "cort" = "#6aa84f"
)


# plot baseline PPR for female groups
female_HFS_group_PPR_plot <- female_HFS_PPR_df %>%
  mutate(group = factor(group, levels = group_order)) %>%
  ggplot(aes(x = group, y = mean_PPR_cell)) +

# boxes
  geom_boxplot(aes(fill = group), alpha = 0.6,
               outlier.shape = NA, width = 0.5, show.legend = FALSE,
               color = "black") +

# individual cells as dots (sina plot)
  geom_sina(aes(color = group), max_width = 0.2,
            shape = 16, size = 2, show.legend = FALSE) +

# axis labels
  labs(x = NULL, y = "Final Paired Pulse Ratio") +

# group color mapping for boxplot and dots
  scale_fill_manual(values = light_group_colors) +
  scale_color_manual(values = group_colors) +

  # x-axis labels
  scale_x_discrete(labels = c("naive" = "Naive", 
                              "acute" = "Acute", 
                              "AM251" = "Acute with AM251", 
                              "repeated" = "Repeated",
                              "cort" = "Naive with Corticosterone")) +
  # y-axis
    scale_y_continuous(limits = c(0, 3), expand = expansion(mult = c(0, 0.05))) +

  patchclampplotteR_theme() +
  theme(legend.position = "none") 

  
female_HFS_group_PPR_plot

# ggsave(female_baseline_control_PPR_plot, path = here("Figures"), file = "female_baseline_control_PPR_plot.png", width = 7, height = 5, units = "in", dpi = 300)
```
#### anova
```{r}
# HoV
leveneTest(mean_PPR_cell ~ group, data = female_HFS_PPR_df)
# passed

# anova
female_HFS_PPR_anova <- aov(mean_PPR_cell ~ group, data = female_HFS_PPR_df)
summary(female_HFS_PPR_anova)
# not significant

# assumption of normality
female_HFS_PPR_anova_resid <- residuals(female_HFS_PPR_anova)
shapiro.test(female_HFS_PPR_anova_resid)
qqnorm(female_HFS_PPR_anova_resid)
qqline(female_HFS_PPR_anova_resid, col = "red")
# passed
```



## AP Frequency
AP Frequencies for Multiple Treatments
```{r}
plot_AP_frequencies_multiple_treatments(
  data = AP_count_data,
  include_all_treatments = "no",
  list_of_treatments = c("Control", "AM251"),
  plot_category = 2,
  included_sexes = "female",
  treatment_colour_theme = my_theme_colours
)
```

#### Mine 
```{r}
# data prep: adding group column
AP_freq_df <- AP_count_data %>%
  mutate(group = case_when(
    sex == "Female" & category == 2 & treatment == "Control" ~ "acute",
    sex == "Female" & category == 2 & treatment == "AM251" ~ "AM251",
    sex == "Female" & category == 3 & treatment == "Control" ~ "repeated",
    sex == "Female" & category == 1 & treatment == "Cort" ~ "cort",
  )) %>%
  mutate(group = factor(group, levels = c("acute", "AM251", "repeated", "cort")))

# letter and state need to be factors
AP_freq_df$state <- factor(AP_freq_df$state)
AP_freq_df$letter <- factor(AP_freq_df$letter)
AP_freq_df$sweep <- factor(AP_freq_df$sweep)

# baseline only
female_baseline_AP_freq_df <- AP_freq_df %>%
  filter(state == "Baseline")
```

```{r}
# eyeball interaction plot

library(sciplot)
AP_freq_df$state <- factor(AP_freq_df$state, levels=c("Baseline", "HFS")) # telling it what order
lineplot.CI(x.factor=state, response=AP_frequency, group=group, xlab="State", ylab="AP Frequency (Hz)", data=AP_freq_df) 
```

```{r}
library(nlme)
# starting it off with imposed compound symmetry (assumes sphericity)
AP_freq_model.cs = lme(AP_frequency ~ group*state, data = AP_freq_df, random = ~1|letter, correlation = corCompSymm(form = ~1|letter)) 
anova(AP_freq_model.cs) 
```
```{r, fig.width = 12, fig.height = 10}
library(sjPlot) 
plot_grid(plot_model(AP_freq_model.cs, type = "diag")) 
# bad
```

```{r}
# log + 1 transform
AP_freq_df$log_AP_frequency <- log(AP_freq_df$AP_frequency + 1)

# new model
log_AP_freq_model.cs = lme(log_AP_frequency ~ group*state, data = AP_freq_df, random = ~1|letter, correlation = corCompSymm(form = ~1|letter)) 
anova(log_AP_freq_model.cs) 

# retest assumptions
plot_grid(plot_model(log_AP_freq_model.cs, type = "diag")) # looks horrible, this is technically count data so maybe want to use negative binomial
```

```{r}
# negative binomial

library(glmmTMB)
library(lme4)
library(car)
library(DHARMa)

AP_freq_model.nb <- glmer.nb(AP_frequency ~ group*state + (1|letter), data=AP_freq_df)
Anova(AP_freq_model.nb, type="III", component="cond")
summary(AP_freq_model.nb)


AP_freq_model.res.nb <- simulateResiduals(AP_freq_model.nb, n = 1000)
plot(AP_freq_model.res.nb)
testUniformity(AP_freq_model.res.nb)
testDispersion(AP_freq_model.res.nb)
```


### Christelinda's
```{r eval=FALSE}
plot_AP_frequencies_single_treatment(
  data = AP_count_data, # 
  plot_treatment = "Control",
  plot_category = 2, # Acute with only picro
  included_sexes = "female",
  baseline_label = "Baseline",
  hormone_added = "HFS",
  significance_display_method = "p-values", # could be "p-values" or "stars"
  treatment_colour_theme = my_theme_colours,
  large_axis_text = "no",
  test_type = "wilcox.test", # need to test assumptions
  theme_options = my_theme_options,
  save_plot_png = "no"
)
```
```{r eval=FALSE}
plot_AP_frequencies_single_treatment(
  data = AP_count_data, 
  plot_treatment = "AM251",
  plot_category = 2,
  included_sexes = "female",
  baseline_label = "Baseline",
  hormone_added = "HFS",
  significance_display_method = "p-values", # could be "p-values" or "stars"
  treatment_colour_theme = my_theme_colours,
  large_axis_text = "no",
  test_type = "wilcox.test", # need to test assumptions, can be "wilcox.test", "t.test", or "none"
  theme_options = my_theme_options,
  save_plot_png = "no"
)
```
```{r eval=FALSE}
plot_AP_frequencies_single_treatment(
  data = AP_count_data, 
  plot_treatment = "Control",
  plot_category = 3,
  included_sexes = "female",
  baseline_label = "Baseline",
  hormone_added = "HFS",
  significance_display_method = "p-values", # could be "p-values" or "stars"
  treatment_colour_theme = my_theme_colours,
  large_axis_text = "no",
  test_type = "wilcox.test", # need to test assumptions, can be "wilcox.test", "t.test", or "none"
  theme_options = my_theme_options,
  save_plot_png = "no"
)
```
```{r eval=FALSE}
plot_AP_frequencies_single_treatment(
  data = AP_count_data, # 
  plot_treatment = "Cort",
  plot_category = 1, 
  included_sexes = "female",
  baseline_label = "Baseline",
  hormone_added = "HFS",
  significance_display_method = "p-values", # could be "p-values" or "stars"
  treatment_colour_theme = my_theme_colours,
  large_axis_text = "no",
  test_type = "wilcox.test", # need to test assumptions
  theme_options = my_theme_options,
  save_plot_png = "no"
)
```



## AP Amplitude
### Mine
```{r}
library(lme4)
library(lmerTest)
library(sciplot)

# can't have neurons that didn't fire any dragging it down
no_zeros_female_AP_amp <- subset(AP_data, letter %in% c("RMA1", "RMA3", "RMA8", "RMA9", "RMA10", "RMA2A", "RMA3A", "RMA4A", "RMA5A", "RMA6A", "RMA10A", "RMR1", "RMR2", "RMR3", "RMR4", "RMR5", "RMR6", "RMR8", "RMR9", "RMR10", "RMC1", "RMC2", "RMC3", "RMC4", "RMC5", "RMC6", "RMC7"))

lineplot.CI(x.factor = state, response = peak_amplitude, group = group, xlab="State", ylab="AP Amplitude (pA)", data = no_zeros_female_AP_amp) 
# looks like there will be an interaction

# starting it off with imposed compound symmetry (assumes sphericity)
no_zeros_female_AP_amp.cs = lme(peak_amplitude ~ group*state, data = no_zeros_female_AP_amp, random = ~1|letter, correlation = corCompSymm(form = ~1|letter)) 
anova(no_zeros_female_AP_amp.cs) 

```


#### Acute Females 
```{r}
# data
acute_females <- c("RMA1", "RMA3", "RMA8", "RMA9", "RMA10") # remove RMA2, RMA4, RMA6 because they have a 0 value
acute_female_AP_data <- subset(AP_data, letter %in% acute_females)


acute_female_baseline_AP_data <- subset(acute_female_AP_data, state == "Baseline")$peak_amplitude
acute_female_HFS_AP_data <- subset(acute_female_AP_data, state == "HFS")$peak_amplitude

acute_female_AP_data_diff <- acute_female_baseline_AP_data-acute_female_HFS_AP_data


# normality
qqnorm(acute_female_AP_data_diff) 
qqline(acute_female_AP_data_diff) 
shapiro.test(acute_female_AP_data_diff) # normality test of difference variable
# normal (when the cells with 0 amplitude are removed)

t.test(acute_female_baseline_AP_data, acute_female_HFS_AP_data, paired = TRUE)

acute_female_AP_t.test_pvalue <- 0.01216
```
```{r}
# visualize

acute_female_AP_plot <- acute_female_AP_data[, c("letter", "state", "peak_amplitude")]

# plot
acute_female_AP_plot <- acute_female_AP_data %>%
  ggplot(aes(x = state, y = peak_amplitude, group = letter)) +
  
# individual cells
  geom_point(aes(state), size = 1, colour = "lightgrey") + # or #f19cac
  geom_line(aes(group = letter), colour = "lightgrey", alpha = 0.9) +
  
# mean point
  stat_summary(aes(group = 1),
               fun.data = mean_se,
               geom = "line",
               colour = "#eb647e",
               linewidth = 1.2) +
  
  stat_summary(aes(group = 1),
    fun.data = mean_se,
    geom = "point",
    colour = "#eb647e",
    size = 2.5
  ) + 

# bracket
  geom_signif(
    comparisons = list(c("Baseline", "HFS")),
    map_signif_level = TRUE,  
    annotations = acute_female_AP_t.test_pvalue,  
    vjust = -0.3,
    textsize = 5,
    size = 0.5,
    margin_top = 0.1,
    extend_line = 0.03
  ) +

# y-axis
  scale_y_continuous(limits = c(0, 100)) +
  
# theme and titles
  patchclampplotteR_theme() +
  labs(x = NULL, y = "Peak Amplitude (pA)", title = NULL) +
  theme(legend.position = "none")  # remove legend

acute_female_AP_plot

# ggsave(acute_female_AP_plot, path = here("Figures"), file = "acute_female_AP_plot.png", width = 7, height = 5, units = "in", dpi = 300)
```

#### AM251 Females 
```{r}
# data
AM251_females <- c("RMA2A", "RMA3A", "RMA4A", "RMA5A", "RMA6A", "RMA10A") # remove RMA1A, RMA9A because they have a 0 value
AM251_female_AP_data <- subset(AP_data, letter %in% AM251_females)


AM251_female_baseline_AP_data <- subset(AM251_female_AP_data, state == "Baseline")$peak_amplitude
AM251_female_HFS_AP_data <- subset(AM251_female_AP_data, state == "HFS")$peak_amplitude

AM251_female_AP_data_diff <- AM251_female_baseline_AP_data-AM251_female_HFS_AP_data


# normality
qqnorm(AM251_female_AP_data_diff) 
qqline(AM251_female_AP_data_diff) 
shapiro.test(AM251_female_AP_data_diff) 
# normal (when the cells with 0 amplitude are removed)

t.test(AM251_female_baseline_AP_data, AM251_female_HFS_AP_data, paired = TRUE)

AM251_female_AP_t.test_pvalue <- 0.1024
```

```{r}
# visualize

AM251_female_AP_data_plot <- AM251_female_AP_data[, c("letter", "state", "peak_amplitude")]


# plot
AM251_female_AP_plot <- AM251_female_AP_data %>%
  ggplot(aes(x = state, y = peak_amplitude, group = letter)) +
  
# individual cells
  geom_point(aes(state), size = 1, colour = "lightgrey") + 
  geom_line(aes(group = letter), colour = "lightgrey", alpha = 0.9) +
  
# mean point
  stat_summary(aes(group = 1),
               fun.data = mean_se,
               geom = "line",
               colour = "#C11C84",
               linewidth = 1.2) +
  
  stat_summary(aes(group = 1),
    fun.data = mean_se,
    geom = "point",
    colour = "#C11C84",
    size = 2.5
  ) + 

# bracket
  geom_signif(
    comparisons = list(c("Baseline", "HFS")),
    map_signif_level = TRUE,  
    annotations = AM251_female_AP_t.test_pvalue,  
    vjust = -0.3,
    textsize = 5,
    size = 0.5,
    margin_top = 0.1,
    extend_line = 0.03
  ) +

# y-axis
  scale_y_continuous(limits = c(0, 100)) +
  
# theme and titles
  patchclampplotteR_theme() +
  labs(x = NULL, y = "Peak Amplitude (pA)", title = NULL) +
  theme(legend.position = "none")  # remove legend

AM251_female_AP_plot

# ggsave(AM251_female_AP_plot, path = here("Figures"), file = "AM251_female_AP_plot.png", width = 7, height = 5, units = "in", dpi = 300)
```

#### Repeated Females 
```{r}
# data
repeated_females <- c("RMR1", "RMR2", "RMR3", "RMR4", "RMR5", "RMR6", "RMR8", "RMR9", "RMR10") # none have 0 values
repeated_female_AP_data <- subset(AP_data, letter %in% repeated_females)


repeated_female_baseline_AP_data <- subset(repeated_female_AP_data, state == "Baseline")$peak_amplitude
repeated_female_HFS_AP_data <- subset(repeated_female_AP_data, state == "HFS")$peak_amplitude


# difference needed for PAIRED t-test
repeated_female_AP_data_diff <- repeated_female_baseline_AP_data-repeated_female_HFS_AP_data


# normality
qqnorm(repeated_female_AP_data_diff) 
qqline(repeated_female_AP_data_diff) 
shapiro.test(repeated_female_AP_data_diff) 
# normal (when the cells with 0 amplitude are removed)

t.test(repeated_female_baseline_AP_data, repeated_female_HFS_AP_data, paired = TRUE)

repeated_female_AP_t.test_pvalue <- 0.004368
```

```{r}
# visualize

repeated_female_AP_data_plot <- repeated_female_AP_data[, c("letter", "state", "peak_amplitude")]

# plot
repeated_female_AP_plot <- repeated_female_AP_data %>%
  ggplot(aes(x = state, y = peak_amplitude, group = letter)) +
  
# individual cells
  geom_point(aes(state), size = 1, colour = "lightgrey") + 
  geom_line(aes(group = letter), colour = "lightgrey", alpha = 0.9) +
  
# mean point
  stat_summary(aes(group = 1),
               fun.data = mean_se,
               geom = "line",
               colour = "#005b96",
               linewidth = 1.2) +
  
  stat_summary(aes(group = 1),
    fun.data = mean_se,
    geom = "point",
    colour = "#005b96",
    size = 2.5
  ) + 

# bracket
  geom_signif(
    comparisons = list(c("Baseline", "HFS")),
    map_signif_level = TRUE,  
    annotations = repeated_female_AP_t.test_pvalue,  
    vjust = -0.3,
    textsize = 5,
    size = 0.5,
    margin_top = 0.1,
    extend_line = 0.03
  ) +

# y-axis
  scale_y_continuous(limits = c(0, 100)) +
  
# theme and titles
  patchclampplotteR_theme() +
  labs(x = NULL, y = "Peak Amplitude (pA)", title = NULL) +
  theme(legend.position = "none")  # remove legend

repeated_female_AP_plot

# ggsave(repeated_female_AP_plot, path = here("Figures"), file = "repeated_female_AP_plot.png", width = 7, height = 5, units = "in", dpi = 300)
```

#### Cort Females 
```{r}
# data
cort_females <- c("RMC1", "RMC2", "RMC4", "RMC5", "RMC6", "RMC7") # remove RMC3 because they have a 0 value
cort_female_AP_data <- subset(AP_data, letter %in% cort_females)


cort_female_baseline_AP_data <- subset(cort_female_AP_data, state == "Baseline")$peak_amplitude
cort_female_HFS_AP_data <- subset(cort_female_AP_data, state == "HFS")$peak_amplitude

cort_female_AP_data_diff <- cort_female_baseline_AP_data-cort_female_HFS_AP_data


# normality
qqnorm(cort_female_AP_data_diff) 
qqline(cort_female_AP_data_diff) 
shapiro.test(cort_female_AP_data_diff) # normality test of difference variable
# normal (when the cells with 0 amplitude are removed)

t.test(cort_female_baseline_AP_data, cort_female_HFS_AP_data, paired = TRUE)

cort_female_AP_t.test_pvalue <- 0.1261
```

```{r}
# visualize

cort_female_AP_plot <- cort_female_AP_data[, c("letter", "state", "peak_amplitude")]

# plot
cort_female_AP_plot <- cort_female_AP_data %>%
  ggplot(aes(x = state, y = peak_amplitude, group = letter)) +
  
# individual cells
  geom_point(aes(state), size = 1, colour = "lightgrey") + # or #f19cac
  geom_line(aes(group = letter), colour = "lightgrey", alpha = 0.9) +
  
# mean point
  stat_summary(aes(group = 1),
               fun.data = mean_se,
               geom = "line",
               colour = "#6aa84f",
               linewidth = 1.2) +
  
  stat_summary(aes(group = 1),
    fun.data = mean_se,
    geom = "point",
    colour = "#6aa84f",
    size = 2.5
  ) + 

# bracket
  geom_signif(
    comparisons = list(c("Baseline", "HFS")),
    map_signif_level = TRUE,  
    annotations = cort_female_AP_t.test_pvalue,  
    vjust = -0.3,
    textsize = 5,
    size = 0.5,
    margin_top = 0.1,
    extend_line = 0.03
  ) +

# y-axis
  scale_y_continuous(limits = c(0, 100)) +
  
# theme and titles
  patchclampplotteR_theme() +
  labs(x = NULL, y = "Peak Amplitude (pA)", title = NULL) +
  theme(legend.position = "none")  # remove legend

cort_female_AP_plot

# ggsave(acute_female_AP_plot, path = here("Figures"), file = "acute_female_AP_plot.png", width = 7, height = 5, units = "in", dpi = 300)
```



#### ANOVA
```{r}
# making it into one data frame
AP_amp_anova_data <- subset(AP_data, 
                     letter %in% c(acute_females,
                                   AM251_females,
                                   repeated_females,
                                   cort_females))

# treated as factors
AP_amp_anova_data$group <- factor(AP_amp_anova_data$group)
AP_amp_anova_data$state <- factor(AP_amp_anova_data$state)
AP_amp_anova_data$letter <- factor(AP_amp_anova_data$letter)
```

```{r}
# visualize

AP_amp_anova_plot <- ggplot(AP_amp_anova_data, aes(x = group, y = peak_amplitude, fill = group)) +
  geom_boxplot(alpha = 0.6, outlier.shape = NA) +
  geom_jitter(aes(color = group), width = 0.15, size = 2, alpha = 0.8) +
  facet_wrap(~ state) +
  patchclampplotteR_theme() +
  labs(y = "AP Peak Amplitude (pA)", x = NULL) +
  theme(legend.position = "none") +
  scale_fill_manual(values = c("acute" = "#f19cac",
                               "AM251" = "#ffadff",
                               "repeated" = "#6497b1",
                               "cort" = "#93c47d")) +
  
  scale_color_manual(values = c("acute" = "#eb647e", 
                                "AM251" = "#c11c84",
                                "repeated" = "#005b96",
                                "cort" = "#6aa84f")) 

AP_amp_anova_plot
```

```{r}
# HoV

leveneTest(AP_amp_anova_data$peak_amplitude, interaction(AP_amp_anova_data$state, AP_amp_anova_data$group))
# no evidence to reject the null that variances are homogeneous
```

```{r}
# running anova

AP_amp_anova <- ezANOVA(
  data = AP_amp_anova_data,
  dv = peak_amplitude,
  wid = letter,
  within = state,
  between = group,
  type = 3,
  detailed = T,
  return_aov = T
)

print(AP_amp_anova)
```

```{r}
# normality of residuals

# linear model 
AP_amp_anova_lm_model <- lm(peak_amplitude ~ group * state, data = AP_amp_anova_data)

# extract residuals
resid.AP_amp_anova <- residuals(AP_amp_anova_lm_model)

# Q-Q plot
qqnorm(resid.AP_amp_anova)
qqline(resid.AP_amp_anova)

# Shapiro-Wilk test
shapiro.test(resid.AP_amp_anova)

# log transforming actually made it worse so gonna stick with slight devition form normality cause its fine
```


### Christelinda's
```{r eval=FALSE}
plot_AP_comparison(
  AP_data,
  plot_treatment = "Control",
  plot_category = 2,
  included_sexes = "female",
  facet_by_sex = "no",
  left_sex = "Female",
  y_variable = "peak_amplitude",
  y_axis_title = "Peak Amplitude (pA)",
  theme_options = my_theme_options,
  baseline_label = "Baseline",
  test_type = "wilcox.test",
  post_hormone_label = "HFS",
  treatment_colour_theme = my_theme_colours,
  save_plot_png = "no"
)
```

AP Amplitude: Acute Females with AM251
```{r eval=FALSE}
plot_AP_comparison(
  AP_data,
  plot_treatment = "AM251",
  plot_category = 2,
  included_sexes = "female",
  facet_by_sex = "no",
  left_sex = "Female",
  y_variable = "peak_amplitude",
  y_axis_title = "Peak Amplitude (pA)",
  theme_options = my_theme_options,
  baseline_label = "Baseline",
  test_type = "wilcox.test",
  post_hormone_label = "HFS",
  treatment_colour_theme = my_theme_colours,
  save_plot_png = "no"
)
```

AP Amplitude: Repeated Females 
```{r eval=FALSE}
plot_AP_comparison(
  AP_data,
  plot_treatment = "Control",
  plot_category = 3,
  included_sexes = "female",
  facet_by_sex = "no",
  left_sex = "Female",
  y_variable = "peak_amplitude",
  y_axis_title = "Peak Amplitude (pA)",
  theme_options = my_theme_options,
  baseline_label = "Baseline",
  test_type = "wilcox.test",
  post_hormone_label = "HFS",
  treatment_colour_theme = my_theme_colours,
  save_plot_png = "no"
)
```

## Variance Analysis
Creating Variance dataset for variance analysis (category 2)
```{r}
variance_2_df <- make_variance_data(
  data = summary_eEPSC_df$summary_data,
  df_category = 2,
  include_all_treatments = "yes",
  list_of_treatments = NULL,
  baseline_interval = "t0to5",
  post_hormone_interval = "t25to30",
  treatment_colour_theme = my_theme_colours,
  save_output_as_RDS = "no"
)

variance_2_df

# VARIANCE

# The strength of synaptic transmission onto a neuron depends on the number of functional vesicle release sites (N), the probability of vesicle release (Pr), and the quantal size (Q)

# 1/CV2 depends on N and Pr, but not on Q
# VMR depends on Pr and Q, but not on N
```

```{r}
variance_1_df <- make_variance_data(
  data = summary_eEPSC_df$summary_data,
  df_category = 1,
  include_all_treatments = "yes",
  list_of_treatments = NULL,
  baseline_interval = "t0to5",
  post_hormone_interval = "t25to30",
  treatment_colour_theme = my_theme_colours,
  save_output_as_RDS = "no"
)

variance_1_df
```

```{r}
variance_3_df <- make_variance_data(
  data = summary_eEPSC_df$summary_data,
  df_category = 3,
  include_all_treatments = "yes",
  list_of_treatments = NULL,
  baseline_interval = "t0to5",
  post_hormone_interval = "t25to30",
  treatment_colour_theme = my_theme_colours,
  save_output_as_RDS = "no"
)

variance_3_df
```


Variance Comparisons for ACUTE (Control)
```{r}
cv_comparison_control_plot <- plot_variance_comparison_data(
  data = variance_2_df,
  plot_category = 2, # acute
  plot_treatment = "Control", # only picro
  variance_measure = "cv",
  included_sexes = "both",
  facet_by_sex = "yes",
  left_sex = "Female",
  baseline_interval = "t0to5",
  post_hormone_interval = "t25to30",
  post_hormone_label = "HFS",
  test_type = "wilcox.test",
  large_axis_text = "no",
  treatment_colour_theme = my_theme_colours,
  theme_options = my_theme_options,
  save_plot_png = "no"
)

vmr_comparison_control_plot <- plot_variance_comparison_data(
  data = variance_2_df,
  plot_category = 2, # acute
  plot_treatment = "Control", # only picro
  variance_measure = "VMR",
  included_sexes = "both",
  facet_by_sex = "yes",
  left_sex = "Female",
  baseline_interval = "t0to5",
  post_hormone_interval = "t25to30",
  post_hormone_label = "HFS",
  test_type = "wilcox.test",
  large_axis_text = "no",
  treatment_colour_theme = my_theme_colours,
  theme_options = my_theme_options,
  save_plot_png = "no"
)

cv_comparison_control_plot
vmr_comparison_control_plot

# With the almost significant decrease in VMR in males: 
# if it was significant, since there is no change in 1/CV2, it would be a presynaptic change in Q
```
Variance Comparisons for ACUTE (AM251)
```{r}
cv_comparison_AM251_plot <- plot_variance_comparison_data(
  data = variance_2_df,
  plot_category = 2, # acute
  plot_treatment = "AM251",
  variance_measure = "cv",
  included_sexes = "female", # no male data
  facet_by_sex = "no",
  left_sex = "Female",
  baseline_interval = "t0to5",
  post_hormone_interval = "t25to30",
  post_hormone_label = "HFS",
  test_type = "wilcox.test",
  large_axis_text = "no",
  treatment_colour_theme = my_theme_colours,
  theme_options = my_theme_options,
  save_plot_png = "no"
)

vmr_comparison_AM251_plot <- plot_variance_comparison_data(
  data = variance_2_df,
  plot_category = 2, # acute
  plot_treatment = "AM251",
  variance_measure = "VMR",
  included_sexes = "female", # no male data
  facet_by_sex = "no",
  left_sex = "Female",
  baseline_interval = "t0to5",
  post_hormone_interval = "t25to30",
  post_hormone_label = "HFS",
  test_type = "wilcox.test",
  large_axis_text = "no",
  treatment_colour_theme = my_theme_colours,
  theme_options = my_theme_options,
  save_plot_png = "no"
)

cv_comparison_AM251_plot
vmr_comparison_AM251_plot

# With the almost significant decrease in VMR in males: 
# if it was significant, since there is no change in 1/CV2, it would be a presynaptic change in Q
```
Variance Comparisons for REPEATED (Control)
```{r}
cv_comparison_repeated_plot <- plot_variance_comparison_data(
  data = variance_3_df,
  plot_category = 3, # repeated
  plot_treatment = "Control",
  variance_measure = "cv",
  included_sexes = "both",
  facet_by_sex = "yes",
  left_sex = "Female",
  baseline_interval = "t0to5",
  post_hormone_interval = "t25to30",
  post_hormone_label = "HFS",
  test_type = "wilcox.test",
  large_axis_text = "no",
  treatment_colour_theme = my_theme_colours,
  theme_options = my_theme_options,
  save_plot_png = "no"
)

vmr_comparison_repeated_plot <- plot_variance_comparison_data(
  data = variance_3_df,
  plot_category = 3, # repeated
  plot_treatment = "Control",
  variance_measure = "VMR",
  included_sexes = "both", 
  facet_by_sex = "yes",
  left_sex = "Female",
  baseline_interval = "t0to5",
  post_hormone_interval = "t25to30",
  post_hormone_label = "HFS",
  test_type = "wilcox.test",
  large_axis_text = "no",
  treatment_colour_theme = my_theme_colours,
  theme_options = my_theme_options,
  save_plot_png = "no"
)

cv_comparison_repeated_plot
vmr_comparison_repeated_plot

# RMR6 VMR after is the suddenly high one 

# With the significant decrease in VMR in repeated males, since there is no change in 1/CV2, it is a presynaptic change in Q
```

Variance Comparisons for NAIVE
```{r}
cv_comparison_naive_plot <- plot_variance_comparison_data(
  data = variance_1_df,
  plot_category = 1, 
  plot_treatment = "Control",
  variance_measure = "cv",
  included_sexes = "both",
  facet_by_sex = "yes",
  left_sex = "Female",
  baseline_interval = "t0to5",
  post_hormone_interval = "t25to30",
  post_hormone_label = "HFS",
  test_type = "wilcox.test",
  large_axis_text = "no",
  treatment_colour_theme = my_theme_colours,
  theme_options = my_theme_options
)

vmr_comparison_naive_plot <- plot_variance_comparison_data(
  data = variance_1_df,
  plot_category = 1, 
  plot_treatment = "Control",
  variance_measure = "VMR",
  included_sexes = "both",
  facet_by_sex = "yes",
  left_sex = "Female",
  baseline_interval = "t0to5",
  post_hormone_interval = "t25to30",
  post_hormone_label = "HFS",
  test_type = "wilcox.test",
  large_axis_text = "no",
  treatment_colour_theme = my_theme_colours,
  theme_options = my_theme_options
)

cv_comparison_naive_plot
vmr_comparison_naive_plot
```

```{r}
cv_comparison_cort_plot <- plot_variance_comparison_data(
  data = variance_1_df,
  plot_category = 1, 
  plot_treatment = "Cort",
  variance_measure = "cv",
  included_sexes = "both",
  facet_by_sex = "yes",
  left_sex = "Female",
  baseline_interval = "t0to5",
  post_hormone_interval = "t25to30",
  post_hormone_label = "HFS",
  test_type = "wilcox.test",
  large_axis_text = "no",
  treatment_colour_theme = my_theme_colours,
  theme_options = my_theme_options
)

vmr_comparison_cort_plot <- plot_variance_comparison_data(
  data = variance_1_df,
  plot_category = 1, 
  plot_treatment = "Cort",
  variance_measure = "VMR",
  included_sexes = "both",
  facet_by_sex = "yes",
  left_sex = "Female",
  baseline_interval = "t0to5",
  post_hormone_interval = "t25to30",
  post_hormone_label = "HFS",
  test_type = "wilcox.test",
  large_axis_text = "no",
  treatment_colour_theme = my_theme_colours,
  theme_options = my_theme_options
)

cv_comparison_cort_plot
vmr_comparison_cort_plot
```

## ANOVA for Baseline eEPSC
```{r}
# data frame
female_amp_df <- summary_eEPSC_df$percent_change_data %>%
  filter(sex == "Female" & category %in% c(1,2,3) & treatment %in% c("Control","AM251", "Cort")) %>% 
  mutate(cat_treat = factor(
    interaction(category, treatment),
    levels = c("1.Control", "2.Control", "2.AM251", "3.Control", "1.Cort")
  ))

female_amp_df
```

```{r}
# log transform amplitude data
female_amp_df$log_t0to5 <- log(female_amp_df$t0to5)
female_amp_df$log_t25to30 <- log(female_amp_df$t25to30)
```


```{r}
# assumptions

library(car)
leveneTest(t0to5 ~ cat_treat, data = female_amp_df)
# normal variances are homogeneous

leveneTest(log_t0to5 ~ cat_treat, data = female_amp_df)
# log variances are homogeneous
```



```{r}
# one-way ANOVA
female_baseline_amp_anova <- aov(t0to5 ~ cat_treat, data = female_amp_df)
summary(female_baseline_amp_anova)

# log one-way ANOVA
log_female_baseline_amp_anova <- aov(log_t0to5 ~ cat_treat, data = female_amp_df)
summary(log_female_baseline_amp_anova)
```

```{r}
# normal residuals
female_baseline_amp_anova_residuals <- residuals(female_baseline_amp_anova)

# check normality of residuals
shapiro.test(female_baseline_amp_anova_residuals)
# not normal

hist(female_baseline_amp_anova_residuals, breaks = 10, main = "Residuals Histogram")

qqnorm(female_baseline_amp_anova_residuals)
qqline(female_baseline_amp_anova_residuals, col = "red")



# log residuals
log_female_baseline_amp_anova_residuals <- residuals(female_baseline_amp_anova)

# check normality of residuals
shapiro.test(log_female_baseline_amp_anova_residuals)
# not any better

hist(log_female_baseline_amp_anova_residuals, breaks = 10, main = "Residuals Histogram")

qqnorm(log_female_baseline_amp_anova_residuals)
qqline(log_female_baseline_amp_anova_residuals, col = "red")
```

```{r}
# non-parametric Kruskal-Wallis (on original untransformed data)

kruskal.test(t0to5 ~ cat_treat, data = female_amp_df)
```

## ANOVA for post HFS eEPSC

```{r}
# assumptions

leveneTest(t25to30 ~ cat_treat, data = female_amp_df)
# variances are homogeneous

leveneTest(log_t25to30 ~ cat_treat, data = female_amp_df)
# variances are homogeneous
```

```{r}
# one-way ANOVA
female_HFS_amp_anova <- aov(t25to30 ~ cat_treat, data = female_amp_df)
summary(female_HFS_amp_anova)

# log
log_female_HFS_amp_anova <- aov(log_t25to30 ~ cat_treat, data = female_amp_df)
summary(log_female_HFS_amp_anova)
```

```{r}
# residuals
female_HFS_amp_anova_residuals <- residuals(female_HFS_amp_anova)

# check normality of residuals
shapiro.test(female_HFS_amp_anova_residuals)
# not normal

hist(female_HFS_amp_anova_residuals, breaks = 10, main = "Residuals Histogram")

qqnorm(female_HFS_amp_anova_residuals)
qqline(female_HFS_amp_anova_residuals, col = "red")



# log transformed
log_female_HFS_amp_anova_residuals <- residuals(log_female_HFS_amp_anova)

# check normality of residuals
shapiro.test(log_female_HFS_amp_anova_residuals)
# normal

hist(log_female_HFS_amp_anova_residuals, breaks = 10, main = "Residuals Histogram")

qqnorm(log_female_HFS_amp_anova_residuals)
qqline(log_female_HFS_amp_anova_residuals, col = "red")
```


## Repeated Measures
```{r}
# convert to long
df_female_long <- summary_eEPSC_df$percent_change_data %>% filter(sex=="Female") %>%
  pivot_longer(
    cols = c(t0to5, t5to10, t10to15, t15to20, t20to25, t25to30),  # ONLY the time columns
    names_to = "time",         # new column for time window
    values_to = "time_value"   # new column for the corresponding value of that time window
  ) %>% mutate(
    time = factor(time, levels = c("t0to5","t5to10","t10to15","t15to20","t20to25","t25to30")),
group = case_when(
      sex == "Female" & category == 1 & treatment == "Control" ~ "naive",
      sex == "Female" & category == 2 & treatment == "Control" ~ "acute",
      sex == "Female" & category == 2 & treatment == "AM251"   ~ "AM251",
      sex == "Female" & category == 3 & treatment == "Control" ~ "repeated",
      sex == "Female" & category == 1 & treatment == "Cort" ~ "cort"
      ),
    group = factor(group, levels = c("naive", "acute", "AM251", "repeated", "cort"))
  ) %>% ungroup() %>% as.data.frame() %>% droplevels() %>%
  filter(!is.na(group))

df_female_long <- df_female_long %>% filter(! letter %in% c("RMA100A", "RMR100", "RMR101", "RMR102", "RMR103", "RMR104", "RMR105", "RMR106", "RMR107")) # need to filter out neurons that are ONLY baselines (they are not repeated)
```

means and variances.
```{r}
library(tidyverse)
df_female_long %>%
  group_by(group, time) %>%
  summarise(N = n(), mean=mean(time_value), var=var(time_value))
# unlikely to have homogeneity of variances 
```

```{r}
# eyeball interaction plot

library(sciplot)
df_female_long$time <- factor(df_female_long$time, levels=c("t0to5", "t5to10", "t10to15", "t15to20", "t20to25", "t25to30")) # telling it what order
lineplot.CI(x.factor=time, response=time_value, group=group, xlab="Time Interval", ylab="eEPSC Amplitude (pA)", data=df_female_long) 

# looks like an interaction for sure
```

```{r}
library(nlme)
# don't need letter/time because there are not multiple measurements (subsamples) for each letter (neuron) at each time interval

# starting it off with imposed compound symmetry (assumes sphericity)
project_model.cs = lme(time_value ~ group*time, data = df_female_long, random = ~1|letter, correlation = corCompSymm(form = ~1|letter)) 
anova(project_model.cs) 
```


```{r, fig.width = 12, fig.height = 10}
library(sjPlot) 
plot_grid(plot_model(project_model.cs, type = "diag")) 
# residuals don't look very normal
# variance has a fan pattern
# not passing assumptions
```

```{r}
# actually testing for sphericity
library(afex) 
project_repmesanov <- aov_ez(
  id = "letter",  
  dv = "time_value",
  data = df_female_long,
  between = c("group"),
  within = c("time"),
  type = "III")  # type III because I probably have an interaction
summary(project_repmesanov)
anova(project_repmesanov)

# FAILS SPHERICITY (Mauchly Test p-value was less than 0.05) -> want linear mixed model -> compound symmetry variance structure not appropriate
```

```{r}
# failed sphericity -> can't use the model with compound symmetry imposed -> but still want to use a linear mixed model

# still don't need letter/time because there are not multiple measurements (sub samples) for each letter (neuron) at each time interval


# log transform
df_female_long$log_time_value <- log(df_female_long$time_value)


# log model with imposed compound symmetry
log_project_model.cs = lme(log_time_value ~ group*time, data = df_female_long, random = ~1|letter, correlation = corCompSymm(form = ~1|letter)) 
anova(log_project_model.cs) 


# does the log model with imposed compound symmetry pass assumptions of sphericity
library(afex) 
log_project_repmesanov <- aov_ez(
  id = "letter",  
  dv = "log_time_value",
  data = df_female_long,
  between = c("group"),
  within = c("time"),
  type = "III")  # type III because I probably have an interaction
summary(log_project_repmesanov)
anova(log_project_repmesanov)

# FAILS SPHERICITY (Mauchly Test p-value was less than 0.05... tiny bit better than before but still bad) -> compound symmetry variance structure not appropriate
```


```{r}
# don't need letter/time because each letter was not measured multiple times at each time interval (because I already pruned them)

# check for autocorrelation
acf(resid(log_project_model.cs))
# looks autocorrelated (bigger to smaller trend) -> try ar1 (autoregressive)

log_project_model.ar1 = lme(log_time_value ~ group*time, data = df_female_long, random = ~1|letter, correlation=corAR1(form= ~1|letter))
anova(log_project_model.ar1)
anova(log_project_model.cs, log_project_model.ar1)

# (autoregressive) ar1 structure is a better fit (lower AIC)
# significant effect of time (p < 0.0001) and of group*time interaction (p = 0.0133)
# INTERACTION -> CANNOT DIRECTLY INTERPRET MAIN EFFECTS
```

```{r, fig.width = 12, fig.height = 10}
# does this ar1 log model pass assumptions for a linear mixed model?

plot_grid(plot_model(log_project_model.ar1, type = "diag")) 

# want a p-value
log_project_model.ar1.resid=resid(log_project_model.ar1)
shapiro.test(log_project_model.ar1.resid) 
```

INTERACTION -> CANNOT DIRECTLY INTERPRET MAIN EFFECTS
more interested in the effect of time WITHIN groups
remove the between-subjects factor (group/treatment)

```{r}
library(emmeans)
library(nlme) 

# randomized block analysis for each group level


# subset by group
df_female_summary_naive <- df_female_long %>% filter(group == "naive")
df_female_summary_acute <- df_female_long %>% filter(group == "acute")
df_female_summary_AM251 <- df_female_long %>% filter(group == "AM251")
df_female_summary_repeated <- df_female_long %>% filter(group == "repeated")
df_female_summary_cort <- df_female_long %>% filter(group == "cort")
```

```{r}
# naive
ar1.project_naive.fit <- lme(
  log_time_value ~ time,
  random = ~1 | letter,
  data = df_female_summary_naive,
  correlation = corAR1(form= ~1|letter)
)
anova(ar1.project_naive.fit) # not significant (p = 0.093) -> don't need post hoc
```

```{r}
# acute
ar1.project_acute.fit <- lme(
  log_time_value ~ time,
  random = ~1 | letter,
  data = df_female_summary_acute,
  correlation = corAR1(form= ~1|letter)
)
anova(ar1.project_acute.fit) # significant effect of time (p = 1e-0.4) -> need post hoc


# acute subset
acute_t0to5_t5to10 <- subset(df_female_summary_acute, time=="t0to5" | time=="t5to10")
acute_t0to5_t10to15 <- subset(df_female_summary_acute, time=="t0to5" | time=="t10to15")
acute_t0to5_t15to20 <- subset(df_female_summary_acute, time=="t0to5" | time=="t15to20")
acute_t0to5_t20to25 <- subset(df_female_summary_acute, time=="t0to5" | time=="t20to25")
acute_t0to5_t25to30 <- subset(df_female_summary_acute, time=="t0to5" | time=="t25to30")

# p-values evaluated against p = 0.01 to account for multiple (5) comparisons

# t0to5 vs t5to10 = not significant (0.3919511)
acute_repmesanov.t0to5_t5to10 <- aov_ez(id = "letter", dv = "time_value", data = acute_t0to5_t5to10, within = "time",
  type = "III") # type III is default for when there is only one factor (time)
summary(acute_repmesanov.t0to5_t5to10)

# t0to5 vs t10to15 = not significant (0.2490239)
acute_repmesanov.t0to5_t10to15 <- aov_ez(id = "letter", dv = "time_value", data = acute_t0to5_t10to15, within = "time",
  type = "III")  
summary(acute_repmesanov.t0to5_t10to15)

# t0to5 vs t15to20 = not significant (0.0198726) evaluating against alpha 0.01 to account for multiple comparisons
acute_repmesanov.t0to5_t15to20 <- aov_ez(id = "letter", dv = "time_value", data = acute_t0to5_t15to20, within = "time",
  type = "III")  
summary(acute_repmesanov.t0to5_t15to20)

# t0to5 vs t20to25 = significant (0.0066564)
acute_repmesanov.t0to5_t20to25 <- aov_ez(id = "letter", dv = "time_value", data = acute_t0to5_t20to25, within = "time",
  type = "III")  
summary(acute_repmesanov.t0to5_t20to25)

# t0to5 vs t25to30 = significant (0.00618)
acute_repmesanov.t0to5_t25to30 <- aov_ez(id = "letter", dv = "time_value", data = acute_t0to5_t25to30, within = "time",
  type = "III")  
summary(acute_repmesanov.t0to5_t25to30)
```

```{r}
# AM251
ar1.project_AM251.fit <- lme(
  log_time_value ~ time,
  random = ~1 | letter,
  data = df_female_summary_AM251,
  correlation = corAR1(form= ~1|letter)
)
anova(ar1.project_AM251.fit) # significant effect of time (p = 0.0279) -> need post hoc


# am251 subset
AM251_t0to5_t5to10 <- subset(df_female_summary_AM251, time=="t0to5" | time=="t5to10")
AM251_t0to5_t10to15 <- subset(df_female_summary_AM251, time=="t0to5" | time=="t10to15")
AM251_t0to5_t15to20 <- subset(df_female_summary_AM251, time=="t0to5" | time=="t15to20")
AM251_t0to5_t20to25 <- subset(df_female_summary_AM251, time=="t0to5" | time=="t20to25")
AM251_t0to5_t25to30 <- subset(df_female_summary_AM251, time=="t0to5" | time=="t25to30")

# p-values evaluated against p = 0.01 to account for multiple (5) comparisons

# t0to5 vs t5to10 = not significant (0.430472)
AM251_repmesanov.t0to5_t5to10 <- aov_ez(id = "letter", dv = "time_value", data = AM251_t0to5_t5to10, within = "time",
  type = "III") # type III is default for when there is only one factor (time)
summary(AM251_repmesanov.t0to5_t5to10)

# t0to5 vs t10to15 = not significant (0.495999)
AM251_repmesanov.t0to5_t10to15 <- aov_ez(id = "letter", dv = "time_value", data = AM251_t0to5_t10to15, within = "time",
  type = "III")  
summary(AM251_repmesanov.t0to5_t10to15)

# t0to5 vs t15to20 = not significant (0.310160)
AM251_repmesanov.t0to5_t15to20 <- aov_ez(id = "letter", dv = "time_value", data = AM251_t0to5_t15to20, within = "time",
  type = "III")  
summary(AM251_repmesanov.t0to5_t15to20)

# t0to5 vs t20to25 = not significant (0.15574)
AM251_repmesanov.t0to5_t20to25 <- aov_ez(id = "letter", dv = "time_value", data = AM251_t0to5_t20to25, within = "time",
  type = "III")  
summary(AM251_repmesanov.t0to5_t20to25)

# t0to5 vs t25to30 = not significant (0.031281)
AM251_repmesanov.t0to5_t25to30 <- aov_ez(id = "letter", dv = "time_value", data = AM251_t0to5_t25to30, within = "time",
  type = "III")  
summary(AM251_repmesanov.t0to5_t25to30)
```


```{r}
# repeated
ar1.project_repeated.fit <- lme(
  log_time_value ~ time,
  random = ~1 | letter,
  data = df_female_summary_repeated,
  correlation = corAR1(form= ~1|letter)
)
anova(ar1.project_repeated.fit) # significant effect of time (p = 0.0169) -> need post hoc


# repeated subset
repeated_t0to5_t5to10 <- subset(df_female_summary_repeated, time=="t0to5" | time=="t5to10")
repeated_t0to5_t10to15 <- subset(df_female_summary_repeated, time=="t0to5" | time=="t10to15")
repeated_t0to5_t15to20 <- subset(df_female_summary_repeated, time=="t0to5" | time=="t15to20")
repeated_t0to5_t20to25 <- subset(df_female_summary_repeated, time=="t0to5" | time=="t20to25")
repeated_t0to5_t25to30 <- subset(df_female_summary_repeated, time=="t0to5" | time=="t25to30")

# p-values evaluated against p = 0.01 to account for multiple (5) comparisons

# t0to5 vs t5to10 = not significant (0.342114)
repeated_repmesanov.t0to5_t5to10 <- aov_ez(id = "letter", dv = "time_value", data = repeated_t0to5_t5to10, within = "time",
  type = "III") # type III is default for when there is only one factor (time)
summary(repeated_repmesanov.t0to5_t5to10)

# t0to5 vs t10to15 = not significant (0.200030)
repeated_repmesanov.t0to5_t10to15 <- aov_ez(id = "letter", dv = "time_value", data = repeated_t0to5_t10to15, within = "time",
  type = "III")  
summary(repeated_repmesanov.t0to5_t10to15)

# t0to5 vs t15to20 = not significant (0.095749)
repeated_repmesanov.t0to5_t15to20 <- aov_ez(id = "letter", dv = "time_value", data = repeated_t0to5_t15to20, within = "time",
  type = "III")  
summary(repeated_repmesanov.t0to5_t15to20)

# t0to5 vs t20to25 = not significant (0.128527)
repeated_repmesanov.t0to5_t20to25 <- aov_ez(id = "letter", dv = "time_value", data = repeated_t0to5_t20to25, within = "time",
  type = "III")  
summary(repeated_repmesanov.t0to5_t20to25)

# t0to5 vs t25to30 = not significant (0.190323)
repeated_repmesanov.t0to5_t25to30 <- aov_ez(id = "letter", dv = "time_value", data = repeated_t0to5_t25to30, within = "time",
  type = "III")  
summary(repeated_repmesanov.t0to5_t25to30)
```

```{r}
# cort
ar1.project_cort.fit <- lme(
  log_time_value ~ time,
  random = ~1 | letter,
  data = df_female_summary_cort,
  correlation = corAR1(form= ~1|letter)
)
anova(ar1.project_cort.fit) # significant effect of time (p = 0.1603) -> need post hoc
```

p-values evaluated against p = 0.01 to account for multiple (5) comparisons
bonferroni correction
0.05/5 = 0.01 (corrected alpha level)